---
title: "Additional_analyses"
author: "Ana Macanovic"
date: "2025-05-06"
output: html_document
---

# SI: Results of additinal analyses (SI Appendix S6)

```{r warning = F, message = F}
source("helper_functions.R")
packages_to_load <- c("readr", "dplyr", "tidyr", 
                      "ggplot2", "cowplot", "ggpubr",
                      "tidyverse", "flextable", 
                      "officer", "psych",
                      "DescTools", "stevemisc")

fpackage_check(packages_to_load)


# For full reproducibility, load the packages with groundhog using the code below instead
# of the fpackage_check function

# library(groundhog)
# groundhog.library(packages_to_load, date = "2024-4-23")
```


Load the additional panel first:
```{r message = F, warning = F}
prof_panel_filter_additional <- read_csv("panel_datasets/additional_dataset/prof_panel_additional_anonymised.csv")
```

## Table S13

Obtained by manual checking of the data sources.

## Table S14

Get the numbers of men and women professors in the additional dataset. 
Combined with Table S5, this gives table S14.

First, get the totals for the last observation for each professor:
```{r}
prof_totals <- prof_panel_filter_additional %>%
  group_by(profile_id)%>%
  filter(year == max(year) & !is.na(overall_adj_domain))

prof_totals$inferred_gender <- as.factor(prof_totals$inferred_gender)
```

Number of profs per field and gender:
```{r}
profs_gender_field <- prof_totals %>% 
  group_by(overall_adj_domain, inferred_gender)%>%
  summarise(n = n())%>%
  pivot_wider(names_from = inferred_gender, values_from = n)

profs_gender_field$overall_adj_domain <- ordered(profs_gender_field$overall_adj_domain,
                                                levels = c( "Physical Sciences", 
                                                            "Life Sciences",
                                                            "Health Sciences",
                                                            "Social Sciences",
                                                            "Arts and Humanities"))


profs_gender_field <- profs_gender_field %>%
  arrange(overall_adj_domain)

profs_gender_field$share_w <- round(profs_gender_field$w/(profs_gender_field$m+profs_gender_field$w)*100,3)


(profs_gender_field_save <- profs_gender_field %>%
  regulartable() %>%
  set_caption("Professors per field and gender")%>%
  autofit())

word_document_name <-
    read_docx() %>%
    body_add_flextable(profs_gender_field_save) %>%
    print(target = "Results/supplement_tables/SI_Table_S14.docx")
```


## Table S15

Get the additional panel descriptive statitics.
Combined with Table S6, this gives Table S15.

Describe groups by gender:
```{r}
prof_panel_filter_descriptives <- prof_panel_filter_additional %>%
  filter(!is.na(overall_adj_domain) & year >= 2013 & year <= 2023 & years_since_first_pub >= 0)

desc_by_gender <- describeBy(prof_panel_filter_descriptives[c("years_since_first_pub", "news_all", "alt_online_all", "alt_twitter",
                                                              "count_pubs", "share_first_au", "cited_by", "avg_sjr",
                                                              "count_pubs_total", "share_first_au_total", "cited_by_total_all",
                                                              "avg_sjr_total", "coa_tot_cited_by",  "coa_tot_cited_by_total", 
                                                              "coa_online_combi_total", "coa_online_combi",
                                                              "news_all_total", "alt_online_all_total",
                                                              "alt_twitter_total")], prof_panel_filter_descriptives$inferred_gender, mat = TRUE) 
```

Select columns of interest and tidy this up:
```{r}
desc_by_gender$variable <- rownames(desc_by_gender)
desc_by_gender$variable <- str_sub(desc_by_gender$variable, end = -2)

desc_by_gender_tidy <- desc_by_gender %>%
  dplyr::select(group1, variable, n, mean, sd, median, min, max)%>%
  pivot_wider(names_from = group1,
              values_from = c(n, mean, sd, median, min, max))%>%
 mutate_if(is.numeric, round, 3)
  
```

Test the means:
```{r}
cols <- c("years_since_first_pub", "news_all", "alt_online_all", "alt_twitter",
          "count_pubs", "share_first_au", "cited_by", "avg_sjr",
          "count_pubs_total", "share_first_au_total", "cited_by_total_all",
          "avg_sjr_total", "coa_tot_cited_by",  "coa_tot_cited_by_total", 
          "coa_online_combi_total", "coa_online_combi",
          "news_all_total", "alt_online_all_total",
          "alt_twitter_total")

p_values <- c()

for (col in cols){
  
  men_values <- prof_panel_filter_additional[which(prof_panel_filter_additional$inferred_gender == "m"), col]
  women_values <- prof_panel_filter_additional[which(prof_panel_filter_additional$inferred_gender == "w"), col]
  p_values <- c(p_values, round(t.test(men_values,women_values, data=data, paired=FALSE)$p.value, 5))
}

p_val_differences <- data.frame(variable = cols, 
                                p_value = p_values)
```


Merge the two tables:
```{r}
desc_by_gender_tidy <- merge(desc_by_gender_tidy,
                             p_val_differences,
                             by = "variable")

desc_by_gender_tidy$stars <- ifelse(desc_by_gender_tidy$p_value <= 0.001, "***",
                             ifelse(desc_by_gender_tidy$p_value <= 0.001, "**",
                                    ifelse(desc_by_gender_tidy$p_value <= 0.05, "*",
                                           ifelse(desc_by_gender_tidy$p_value <= 0.1, ".", ""))))

# order the factors
desc_by_gender_tidy$variable <- factor(desc_by_gender_tidy$variable,
                                       levels = c("news_all",
                                                  "news_all_total",
                                                  "alt_online_all",
                                                  "alt_online_all_total",
                                                  "alt_twitter",
                                                  "alt_twitter_total",
                                                  "count_pubs",
                                                  "count_pubs_total",
                                                  "share_first_au",
                                                  "share_first_au_total", 
                                                  "cited_by",
                                                  "cited_by_total_all",
                                                  "avg_sjr",
                                                  "avg_sjr_total",  
                                                  "coa_tot_cited_by",
                                                  "coa_tot_cited_by_total", 
                                                  "coa_online_combi",
                                                  "coa_online_combi_total",
                                                  "years_since_first_pub"))


# select the variables
desc_by_gender_tidy <- desc_by_gender_tidy %>%
  arrange(variable)%>%
  dplyr::select(variable, n_m, n_w, mean_m, mean_w, stars, sd_m, sd_w, median_m, median_w, min_m, min_w, max_m, max_w)

(desc_by_gender_tidy_save <- desc_by_gender_tidy %>%
  regulartable() %>%
  set_caption("Descriptive statistics")%>%
  autofit())

word_document_name <-
    read_docx() %>%
    body_add_flextable(desc_by_gender_tidy_save) %>%
    print(target = "Results/supplement_tables/SI_Table_S15.docx")
```
## Fig S12

Within-field comparison:
```{r}
fields <- c("Physical Sciences",
            "Life Sciences",
            "Health Sciences",
            "Social Sciences",
            "Arts and Humanities")
field_comparisons <- data.frame(matrix(NA, ncol = 5, nrow = length(fields)))

for (i in 1:length(fields)){
  field <- fields[i]
  data <- filter(prof_totals, 
                 overall_adj_domain == field)
  field_comparisons[i, 1] <- field
  field_comparisons[i, 2] <- nrow(data)
  field_comparisons[i, 3] <- round(t.test(news_all_total ~ inferred_gender, data=data, paired=FALSE)$p.value, 5)
  field_comparisons[i, 4] <- round(t.test(alt_online_all_total ~ inferred_gender, data=data, paired=FALSE)$p.value, 5)
  field_comparisons[i, 5] <- round(t.test(alt_twitter_total ~ inferred_gender, data=data, paired=FALSE)$p.value, 5)
}

colnames(field_comparisons) <- c("field", "profs",
                                 "total", "online_total", "twitter_total")
field_comparisons$comparison <-  "ttest"


mean_values_field <- prof_totals %>%
  filter(!is.na(overall_adj_domain))%>%
  group_by(inferred_gender, overall_adj_domain)%>%
  summarise(total = mean(news_all_total, na.rm = TRUE),
            online_total = mean(alt_online_all_total, na.rm = TRUE),
            twitter_total =  mean(alt_twitter_total, na.rm = TRUE),
            total_sd = sd(news_all_total, na.rm = TRUE),
            online_total_sd = sd(alt_online_all_total, na.rm = TRUE),
            twitter_total_sd =  sd(alt_twitter_total, na.rm = TRUE),
            all_n = n())%>%
  mutate(
            
            total_se = total_sd / sqrt(all_n),
            online_total_se = online_total_sd / sqrt(all_n),
            twitter_total_se =  twitter_total_sd / sqrt(all_n),
            
            total_lci = total - qt(1 - (0.05 / 2), all_n - 1) * total_se,
            online_total_lci = online_total - qt(1 - (0.05 / 2), all_n - 1) * online_total_se,
            twitter_total_lci =  twitter_total - qt(1 - (0.05 / 2), all_n - 1) * twitter_total_se,
            
            total_uci = total + qt(1 - (0.05 / 2), all_n - 1) * total_se,
            online_total_uci = online_total + qt(1 - (0.05 / 2), all_n - 1) * online_total_se,
            twitter_total_uci =  twitter_total + qt(1 - (0.05 / 2), all_n - 1) * twitter_total_se)%>%
  mutate(across(2:17, \(x) round(x, 3)))

colnames(mean_values_field)[1] <- "comparison"
colnames(mean_values_field)[2] <- "field"
```

Plot the means comparison:
```{r}
mean_values_field$field <- factor(mean_values_field$field,
                                   levels = c("Physical Sciences",
                                              "Life Sciences",
                                              "Health Sciences",
                                              "Social Sciences",
                                              "Arts and Humanities"))
mean_values_field$comparison <- ordered(mean_values_field$comparison,
                                   levels = c("m", "w"))

significance_testing <-  field_comparisons

significance_testing <-  significance_testing %>%
  filter(comparison == "ttest")%>%
  mutate_at(vars(`online_total`, `total`, `twitter_total`), .funs = list(
    ~case_when(
      . <= 0.001 ~ '***',
      . <= 0.01 ~ '**',
      . <= 0.05 ~ '*',
      . <= 0.1 ~ '',
      . > 0.1 ~ ''
    )))

significance_testing$field <- factor(significance_testing$field,
                                   levels = c("Arts and Humanities",
                                              "Social Sciences",
                                              "Health Sciences",
                                               "Life Sciences",
                                              "Physical Sciences"
                                              ))
significance_testing <- significance_testing %>%
  arrange(field)

significance_testing$group1 <- "m"
significance_testing$group2 <- "w"
significance_testing$x <- c(1,2,3,4, 5)
significance_testing$xmin <- c(0.75,1.75,2.75,3.75, 4.75)
significance_testing$xmax <- c(1.25,2.25, 3.25,4.25, 5.25)
significance_testing$comparison <- "m"


average_news <- mean_values_field %>%
  ggplot(aes(x=fct_rev(field), y=total, fill = fct_rev(comparison), color = fct_rev(comparison))) + 
  geom_bar(position=position_dodge(.5),stat="identity", alpha=1, width = 0.5)+
  geom_errorbar(
    aes(y=total, 
        x = fct_rev(field),
        group = fct_rev(comparison),
        ymin = total_lci, 
        ymax = total_uci
    ),
    width = 0.2,
    stat="identity",
    position=position_dodge(.5),)+
  guides(fill = guide_legend(reverse = TRUE, title = "Inferred gender"))+
  scale_fill_manual(values =  c("#F5C710", "#61D04F")  , labels = c("Women", "Men"))+
  scale_color_manual(values =  c("#997b06", "#338a25")  , labels = c("Women", "Men"), guide="none")+
  ggtitle("Printed news attention")+
  stat_pvalue_manual(
    rev(significance_testing),
    y.position = rep(150, 5),
    label.size = 3,
    coord.flip = TRUE,
    tip.length = 0.005,
    label = "{total}",
    remove.bracket = FALSE,
    hide.ns = TRUE
  )+
  scale_y_continuous(limits = c(-30, 150), breaks = seq(-30, 150, by = 30))+
  ylab("Average mentions over lifetime")+
  xlab("Field")+
  labs(color = "Inferred gender")+
  theme_minimal_vgrid()+
  theme(plot.title = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 11),
        axis.text.x = element_text(size = 10) ,
        axis.title.x = element_text(size = 11),
        legend.title=element_text(size=11), 
        legend.text=element_text(size=10))+
      coord_flip()
    
average_online <- mean_values_field %>%
  ggplot(aes(x=fct_rev(field), y=online_total, fill = fct_rev(comparison), color = fct_rev(comparison))) + 
  geom_bar(position=position_dodge(.5),stat="identity", alpha=1, width = 0.5)+
  geom_errorbar(
    aes(y=total, 
        x = fct_rev(field),
        group = fct_rev(comparison),
        ymin = online_total_lci, 
        ymax = online_total_uci
    ),
    width = 0.2,
    stat="identity",
    position=position_dodge(.5),)+
  guides(fill = guide_legend(reverse = TRUE, title = "Inferred gender"))+
  scale_fill_manual(values =  c("#F5C710", "#61D04F")  , labels = c("Women", "Men"))+
  scale_color_manual(values =  c("#997b06", "#338a25")  , labels = c("Women", "Men"), guide="none")+
  ggtitle("Online news attention")+
  scale_y_continuous(limits = c(-10, 86), breaks = seq(-10, 86, by = 16))+
  stat_pvalue_manual(
    significance_testing,
    y.position = rep(84, 5),
    label.size = 3,
    coord.flip = TRUE,
    tip.length = 0.005,
    label = "{online_total}",
  )+
  ylab("Average mentions over lifetime")+
  labs(color = "Inferred gender")+
  theme_minimal_vgrid()+
  theme(plot.title = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 11),
        axis.text.x = element_text(size = 10) ,
        axis.title.x = element_text(size = 11),
        legend.title=element_text(size=11), 
        legend.text=element_text(size=10))+
  coord_flip()+
  xlab("Field")


average_twitter <- mean_values_field %>%
  ggplot(aes(x=fct_rev(field), y=twitter_total, fill = fct_rev(comparison), color = fct_rev(comparison))) + 
  geom_bar(position=position_dodge(.5),stat="identity", alpha=1, width = 0.5)+
  geom_errorbar(
    aes(y=total, 
        x = fct_rev(field),
        group = fct_rev(comparison),
        ymin = twitter_total_lci, 
        ymax = twitter_total_uci
    ),
    width = 0.2,
    stat="identity",
    position=position_dodge(.5),)+
  guides(fill = guide_legend(reverse = TRUE, title = "Inferred gender"))+
  scale_fill_manual(values =  c("#F5C710", "#61D04F")  , labels = c("Women", "Men"))+
  scale_color_manual(values =  c("#997b06", "#338a25")  , labels = c("Women", "Men"), guide="none")+
  ggtitle("Twitter/X attention")+
  stat_pvalue_manual(
    significance_testing,
    y.position = rep(184, 5),
    label.size = 3,
    coord.flip = TRUE,
    tip.length = 0.005,
    label = "{twitter_total}",
    remove.bracket = FALSE,
  )+
  scale_y_continuous(limits = c(-25, 185), breaks = seq(-25, 185, by = 35))+
  ylab("Average mentions over lifetime")+
  labs(color = "Inferred gender")+
  theme_minimal_vgrid()+
  theme(plot.title = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.y = element_text(size = 11),
        axis.text.x = element_text(size = 10) ,
        axis.title.x = element_text(size = 11),
        legend.title=element_text(size=11), 
        legend.text=element_text(size=10))+
  coord_flip()+
  xlab("Field")
```

Combine these plots into one (Figure 1, panel A):
```{r fig.width=10, fig.height=3}
legend_average <- get_legend(
  # create some space to the left of the legend
  average_news
)

combi_plot_averages <- plot_grid(average_news + 
                                   theme(legend.position="none", 
                                         axis.title.x = element_blank(),
                                         axis.title.y=element_blank())
                                 + panel_border(), 
                                 average_online + theme(legend.position="none",
                                                        axis.title.x = element_blank(),
                                                        axis.title.y=element_blank(),
                                                        axis.text.y = element_blank())
                                 + panel_border(), 
                                 average_twitter + theme(legend.position="none",
                                                         axis.title.y=element_blank(),
                                                         axis.title.x = element_blank(),
                                                         axis.text.y = element_blank())
                                 + panel_border(), 
                                 legend_average,
                                 ncol = 4,
                                 rel_widths = c(1.3, 0.9, 0.9, 0.4))

combi_plot_averages


ggsave2(
  filename = "Results/supplement_figures/SI_Fig_S12.png",
  plot = combi_plot_averages,
  width = 11,
  height = 3.5,
  units = c("in"),
  dpi = 1200,
  bg = "white"
)
```

## Table S16
Using the main dataset, get Table S16.

Load the panel:
```{r warning = F, message = F}
prof_panel_filter <- read_csv("panel_datasets/prof_panel_anonymised.csv")
```


Get yearly attention totals:
```{r}
(yearly_prof_totals <- prof_panel_filter %>%
  group_by(year)%>%
  summarise(printed_news_total = sum(news_all, na.rm = TRUE),
            online_news_total = sum(alt_online_all),
            twitter_total = sum(alt_twitter)))
  
```

Write the result out:
```{r}
write_csv(yearly_prof_totals, "Results/supplement_tables/SI_Table_S16.csv")
```


## Table S17
Get the averages and CIs:
```{r}
(yearly_add_averages <- prof_panel_filter_additional %>%
  group_by(year)%>%
  summarise(printed = mean(news_all, na.rm = TRUE),
            online = mean(alt_online_all, na.rm = TRUE),
            twitter =  mean(alt_twitter, na.rm = TRUE),
            printed_sd = sd(news_all, na.rm = TRUE),
            online_sd = sd(alt_online_all, na.rm = TRUE),
            twitter_sd =  sd(alt_twitter, na.rm = TRUE),
            all_n = n())%>%
  mutate(
    printed_se = printed / sqrt(all_n),
    online_se = online_sd / sqrt(all_n),
    twitter_se =  twitter_sd / sqrt(all_n),
    
    printed_lci = printed - qt(1 - (0.05 / 2), all_n - 1) * printed_se,
    online_lci = online - qt(1 - (0.05 / 2), all_n - 1) * online_se,
    twitter_lci =  twitter - qt(1 - (0.05 / 2), all_n - 1) * twitter_se,
    
    printed_uci = printed + qt(1 - (0.05 / 2), all_n - 1) * printed_se,
    online_uci = online + qt(1 - (0.05 / 2), all_n - 1) * online_se,
    twitter_uci =  twitter + qt(1 - (0.05 / 2), all_n - 1) * twitter_se)%>%
  mutate(across(2:17, \(x) round(x, 2)))%>%
  dplyr::select(year, printed, printed_lci, printed_uci, online, online_lci, online_uci, twitter, twitter_lci, twitter_uci))
```

Write this out:
```{r}
write_csv(yearly_add_averages, "Results/supplement_tables/SI_Table_S17.csv")
```

