---
title: "SI Robustness checks: Poisson models"
author: "Ana Macanovic"
date: "2024-07-24"
---

Robustness checks including various Poisson model specifications.
All specifications include standard errors clustered at the professor level.


Load the packages:
```{r message=  F, warning = F, eval = T}
source("helper_functions.R")

packages_to_load <- c("readr", "dplyr", "tidyr", 
                      "ggplot2", "cowplot",
                      "tidyverse", "RPostgres", 
                      "lubridate", "lmtest", 
                      "sandwich", "ggpubr", 
                      "knitr", "scales", 
                      "ggeffects", "flextable", 
                      "officer", "DescTools",
                      "gglorenz", "corrplot")

fpackage_check(packages_to_load)


# For full reproducibility, load the packages with groundhog using the code below instead
# of the fpackage_check function

# library(groundhog)
# groundhog.library(packages_to_load, date = "2024-4-23")
```


```{r include=FALSE}
opts_chunk$set(echo = TRUE)
opts_chunk$set(eval = TRUE)
opts_chunk$set(warning = FALSE)
opts_chunk$set(message = FALSE)
```

Load the panel dataset:
```{r warning = F, message = F}
prof_panel_filter <- read_csv("panel_datasets/prof_panel_anonymised.csv")
```

Make a list to save all the results into:
```{r}
all_reg_rob_list <- list()
```

# Poisson models - main

Models comparable to the main models, but fitting a poisson regression instead.

### Printed news attention

```{r}
news_formula_main_model <- "news_all ~ inferred_gender + news_all_l + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = news_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```

### Online news attention 
```{r}
online_news_formula_main_model <- "alt_online_all ~ inferred_gender + alt_online_all_l + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

online_news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                               formula_list = online_news_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               reg_family = "poisson")
```

### Twitter/X
```{r}
twitter_formula_main_model <- "alt_twitter ~ inferred_gender + alt_twitter_l + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

twitter_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = twitter_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models_poisson <- neat_regression_table(news_model_poisson[[1]],
                                           online_news_model_poisson[[1]],
                                           twitter_model_poisson[[1]])

# add to the list
all_reg_rob_list[['poisson_main']] <- table_models_poisson

(table_models_save <- table_models_poisson %>%
  regulartable() %>%
  set_caption("Poisson model - main")%>%
  autofit())

# word_document_name <-
    read_docx() %>%
    body_add_flextable(table_models_save) %>%
    print(target = "results/supplement_tables/poisson_model_main.docx")
```



# Poisson models - excluding 2020 and 2021

Models comparable to the main models, but fitting a poisson regression instead.

### Printed news attention

```{r}
news_formula_main_model <- "news_all ~ inferred_gender + news_all_l + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter_2020,
                                           formula_list = news_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```

### Online news attention 
```{r}
online_news_formula_main_model <- "alt_online_all ~ inferred_gender + alt_online_all_l + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

online_news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter_2020,
                                               formula_list = online_news_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               reg_family = "poisson")
```

### Twitter/X
```{r}
twitter_formula_main_model <- "alt_twitter ~ inferred_gender + alt_twitter_l + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

twitter_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter_2020,
                                           formula_list = twitter_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models_poisson <- neat_regression_table(news_model_poisson[[1]],
                                           online_news_model_poisson[[1]],
                                           twitter_model_poisson[[1]])

# add to the list
all_reg_rob_list[['poisson_main_2019']] <- table_models_poisson

(table_models_save <- table_models_poisson %>%
  regulartable() %>%
  set_caption("Poisson model - up until 2020")%>%
  autofit())

word_document_name <-
read_docx() %>%
body_add_flextable(table_models_save) %>%
print(target = "results/supplement_tables/poisson_model_main_2019.docx")
```



# Poisson models - without the first lag

Models comparable to the main models, but fitting a poisson regression instead.

### Printed news attention

```{r}
news_formula_main_model <- "news_all ~ inferred_gender + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = news_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```

### Online news attention 
```{r}
online_news_formula_main_model <- "alt_online_all ~ inferred_gender + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

online_news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                               formula_list = online_news_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               reg_family = "poisson")
```

### Twitter/X
```{r}
twitter_formula_main_model <- "alt_twitter ~ inferred_gender + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

twitter_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = twitter_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models_poisson <- neat_regression_table(news_model_poisson[[1]],
                                           online_news_model_poisson[[1]],
                                           twitter_model_poisson[[1]])

# add to the list
all_reg_rob_list[['poisson_main_nolag']] <- table_models_poisson

(table_models_save <- table_models_poisson %>%
  regulartable() %>%
  set_caption("Poisson model - no first lag of the dependent variable")%>%
  autofit())

word_document_name <-
    read_docx() %>%
    body_add_flextable(table_models_save) %>%
    print(target = "results/supplement_tables/poisson_model_main_nolag.docx")
```



# Poisson models - including grants

Models comparable to the main models, but fitting a poisson regression instead.

### Printed news attention

```{r}
news_formula_main_model <- "news_all ~ inferred_gender + news_all_l + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(any_grant_l) + as.factor(year)"

news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = news_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```

### Online news attention 
```{r}
online_news_formula_main_model <- "alt_online_all ~ inferred_gender + alt_online_all_l + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(any_grant_l) + as.factor(year)"

online_news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                               formula_list = online_news_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               reg_family = "poisson")
```

### Twitter/X
```{r}
twitter_formula_main_model <- "alt_twitter ~ inferred_gender + alt_twitter_l + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(any_grant_l) + as.factor(year)"

twitter_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = twitter_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models_poisson <- neat_regression_table(news_model_poisson[[1]],
                                           online_news_model_poisson[[1]],
                                           twitter_model_poisson[[1]])

# add to the list
all_reg_rob_list[['poisson_main_grants']] <- table_models_poisson

(table_models_save <- table_models_poisson %>%
  regulartable() %>%
  set_caption("Poisson model - including grants")%>%
  autofit())

word_document_name <-
    read_docx() %>%
    body_add_flextable(table_models_save) %>%
    print(target = "results/supplement_tables/poisson_model_main_grants.docx")
```


# Poisson models - excluding those who held a public post

Exclude professors who held a government position.

### Printed news attention

```{r}
news_formula_main_model <- "news_all ~ inferred_gender + news_all_l + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter_public,
                                           formula_list = news_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```

### Online news attention 
```{r}
online_news_formula_main_model <- "alt_online_all ~ inferred_gender + alt_online_all_l + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

online_news_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter_public,
                                               formula_list = online_news_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               reg_family = "poisson")
```

### Twitter/X
```{r}
twitter_formula_main_model <- "alt_twitter ~ inferred_gender + alt_twitter_l + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

twitter_model_poisson <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter_public,
                                           formula_list = twitter_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "poisson")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models_poisson <- neat_regression_table(news_model_poisson[[1]],
                                           online_news_model_poisson[[1]],
                                           twitter_model_poisson[[1]])

# add to the list
all_reg_rob_list[['poisson_main_no_public']] <- table_models_poisson

(table_models_save <- table_models_poisson %>%
  regulartable() %>%
  set_caption("Poisson model - excluding those who held a public post")%>%
  autofit())

word_document_name <-
    read_docx() %>%
    body_add_flextable(table_models_save) %>%
    print(target = "results/supplement_tables/poisson_model_main_no_public.docx")
```

Save the list:
```{r}
saveRDS(all_reg_rob_list, "results/poisson_models.RDS")
```

