---
title: "SI Robustness checks: FE and RE models"
author: "Ana Macanovic"
date: "2024-08-13"
---


Robustness checks fitting two-way random and fixed-effects models. 

All specifications include standard errors clustered at the professor level.

Load the packages:
```{r message=  F, warning = F, eval = T}
source("helper_functions.R")

packages_to_load <- c("readr", "dplyr", "tidyr", 
                      "ggplot2", "cowplot",
                      "tidyverse", "RPostgres", 
                      "lubridate", "lmtest", 
                      "sandwich", "ggpubr", 
                      "knitr", "scales", "plm",
                      "ggeffects", "flextable", 
                      "officer", "DescTools",
                      "gglorenz", "corrplot")

fpackage_check(packages_to_load)



# For full reproducibility, load the packages with groundhog using the code below instead
# of the fpackage_check function

# library(groundhog)
# groundhog.library(packages_to_load, date = "2024-4-23")
```


```{r include=FALSE}
opts_chunk$set(echo = TRUE)
opts_chunk$set(eval = TRUE)
opts_chunk$set(warning = FALSE)
opts_chunk$set(message = FALSE)
```

Load the panel dataset:
```{r warning = F, message = F}
prof_panel_filter <- read_csv("panel_datasets/prof_panel_anonymised.csv")
```

Make a list to save all the results into:
```{r}
all_reg_rob_list <- list()
```


## Fixed effects models

### Printed news attention

```{r warning = F}
news_formula_main_model <- "news_all ~ news_all_l + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub"

news_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                            lm_formula = news_formula_main_model,
                                            year_cutoff_upper = 2023,
                                            year_cutoff_lower = 2012,
                                            index = c("profile_id", "year"),
                                            fe_re = "fe")
```


### Online news attention 
```{r}
online_news_formula_main_model <- "alt_online_all ~ alt_online_all_l + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub"

online_news_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                                   lm_formula = online_news_formula_main_model,
                                                   year_cutoff_upper = 2023,
                                                   year_cutoff_lower = 2012,
                                                   index = c("profile_id", "year"),
                                                   fe_re = "fe")
```

### Twitter/X
```{r}
twitter_formula_main_model <- "alt_twitter ~ alt_twitter_l + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub"

twitter_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                               lm_formula = twitter_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               index = c("profile_id", "year"),
                                               fe_re = "fe")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models <- neat_regression_table_scopus(news_model[[1]],
                                             online_news_model[[1]],
                                             twitter_model[[1]],
                                             fe = "yes")

# add to the list
all_reg_rob_list[['fe']] <- table_models

(table_models_save <- table_models %>%
    regulartable() %>% 
    set_caption("Main model - two-way fixed effects")%>%
  autofit())


word_document_name <-
    read_docx() %>%
    body_add_flextable(table_models_save) %>%
    print(target = "results/supplement_tables/main_model_table_fe.docx")
```

Plot out the coefficients:
First, prepare the dataframe:
```{r}
model_news <- news_model[[1]]
model_online_news <- online_news_model[[1]]
model_twitter <- twitter_model[[1]]

model_news$model <- "News attention"
model_online_news$model <- "Online news attention"
model_twitter$model <- "Twitter attention"

all_models_plot <- rbind(model_news,
                         model_online_news,
                         model_twitter)

# do the t-1 of dependent as a single variable
all_models_plot$term <- ifelse(all_models_plot$term %in% c("news_all_l",
                                                           "alt_online_all_l",
                                                           "alt_twitter_l"), 
                               "t_min_1", 
                               all_models_plot$term)


all_models_plot$term <- ordered(all_models_plot$term,
                                levels = c("(Intercept)",
                                           "inferred_genderw",
                                           "cited_by_total_all_l",
                                           "news_all_total_l",
                                           "alt_online_all_total_l", 
                                           "alt_twitter_total_l",
                                           "coa_tot_cited_by_total_l",
                                           "coa_tot_online_all_total_l",
                                           "coa_tot_twitter_total_l",
                                           "years_since_first_pub",
                                           "t_min_1",
                                           "as.factor(year)2014",
                                           "as.factor(year)2015",
                                           "as.factor(year)2016",
                                           "as.factor(year)2017",
                                           "as.factor(year)2018",
                                           "as.factor(year)2019",
                                           "as.factor(year)2020",
                                           "as.factor(year)2021",
                                           "as.factor(year)2022",
                                           "as.factor(year)2023",
                                           "R^2"))

all_models_plot$model <- ordered(all_models_plot$model,
                                 levels = c("News attention",
                                            "Online news attention",
                                            "Twitter attention" ))

all_models_plot$field <- ordered(all_models_plot$field,
                                 levels = c("phys",
                                            "life",
                                            "health",
                                            "soc_sci",
                                            "arts"))

covariate_names <- c(
  't_min_1' = "Dependent variable -\n previous period",
  'news_all_l'="News attention -\nprevious period",
  'alt_online_all_l' = "Online news attention -\nprevious period",
  'alt_twitter_l' = "Twitter attention -\nprevious period",
  'cited_by_total_all_l'="Total citations",
  'news_all_total_l'="Total printed news \nattention",
  'alt_online_all_total_l'="Total online news\n attention",
  'alt_twitter_total_l'="Total Twitter/X \nattention",
  'coa_tot_cited_by_total_l' = "Coauthors' total \ncitations",
  'coa_tot_online_all_total_l' = "Coauthors' total \nonline news attention",
  'coa_tot_twitter_total_l' = "Coauthors' total \nTwitter/X attention"
)
```




## Random effects models

### Printed news attention

```{r warning = F}
news_formula_main_model <- "news_all ~ inferred_gender + news_all_l + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub"

news_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                     lm_formula = news_formula_main_model,
                                     year_cutoff_upper = 2023,
                                     year_cutoff_lower = 2012,
                                     index = c("profile_id", "year"),
                                     fe_re = "re")
```


### Online news attention 
```{r}
online_news_formula_main_model <- "alt_online_all ~ inferred_gender + alt_online_all_l + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub"

online_news_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                            lm_formula = online_news_formula_main_model,
                                            year_cutoff_upper = 2023,
                                            year_cutoff_lower = 2012,
                                            index = c("profile_id", "year"),
                                            fe_re = "re")
```

### Twitter/X
```{r}
twitter_formula_main_model <- "alt_twitter ~ inferred_gender + alt_twitter_l + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub"

twitter_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                        lm_formula = twitter_formula_main_model,
                                        year_cutoff_upper = 2023,
                                        year_cutoff_lower = 2012,
                                        index = c("profile_id", "year"),
                                        fe_re = "re")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models <- neat_regression_table_scopus(news_model[[1]],
                                             online_news_model[[1]],
                                             twitter_model[[1]])

# add to the list
all_reg_rob_list[['re']] <- table_models

(table_models_save <- table_models %>%
    regulartable() %>% 
    set_caption("Main model - random effects")%>%
  autofit())


word_document_name <-
    read_docx() %>%
    body_add_flextable(table_models_save) %>%
    print(target = "results/supplement_tables/main_model_table_re.docx")
```

Save the list:
```{r}
saveRDS(all_reg_rob_list, "results/fe_re_models.RDS")
```


