---
title: "SI Robustness checks: FE models"
author: "Ana Macanovic"
date: "2025-05-10"
---

# SI Robustness checks: FE models

Robustness checks fitting two-way fixed-effects models. 
All specifications include standard errors clustered at the professor level.

Load the packages:
```{r message=  F, warning = F, eval = T}
source("helper_functions.R")

packages_to_load <- c("readr", "dplyr", "tidyr", 
                      "ggplot2", "cowplot",
                      "tidyverse", "RPostgres", 
                      "lubridate", "lmtest", 
                      "sandwich", "ggpubr", 
                      "knitr", "scales", "plm",
                      "ggeffects", "flextable", 
                      "officer", "DescTools",
                      "gglorenz", "corrplot")

fpackage_check(packages_to_load)



# For full reproducibility, load the packages with groundhog using the code below instead
# of the fpackage_check function

# library(groundhog)
# groundhog.library(packages_to_load, date = "2024-4-23")
```


```{r include=FALSE}
opts_chunk$set(echo = TRUE)
opts_chunk$set(eval = TRUE)
opts_chunk$set(warning = FALSE)
opts_chunk$set(message = FALSE)
```

Load the panel dataset:
```{r warning = F, message = F}
prof_panel_filter <- read_csv("panel_datasets/prof_panel_anonymised.csv")

all_reg_rob_list <- list()
```


## FE models: main

Below, we fit the FE models for all three types of attention and including all the 
variables included in the main models.

Printed news attention:
```{r warning = F}
news_formula_main_model <- "log(news_all+1) ~ inferred_gender + years_since_first_pub + as.factor(year) + log(count_pubs_total_l+1) + log(cited_by_total_all_l+1) + log(coa_tot_cited_by_total_l+1) + log(coa_online_combi_total_l+1) + log(alt_online_all_total_l+1) + log(alt_twitter_total_l+1) + avg_sjr_total_l + share_first_au_total_l + institution_dutch_total_narcis"

news_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                            lm_formula = news_formula_main_model,
                                            year_cutoff_upper = 2023,
                                            year_cutoff_lower = 2012,
                                            index = c("profile_id", "year"),
                                            fe_re = "fe")
```

Online news attention:
```{r}
online_news_formula_main_model <- "log(alt_online_all+1) ~ inferred_gender + years_since_first_pub + as.factor(year) + log(count_pubs_total_l+1) + log(cited_by_total_all_l+1) + log(coa_tot_cited_by_total_l+1) + log(coa_online_combi_total_l+1) + log(news_all_total_l+1) + log(alt_twitter_total_l+1) + avg_sjr_total_l + share_first_au_total_l + institution_dutch_total_narcis"


online_news_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                                   lm_formula = online_news_formula_main_model,
                                                   year_cutoff_upper = 2023,
                                                   year_cutoff_lower = 2012,
                                                   index = c("profile_id", "year"),
                                                   fe_re = "fe")
```

Twitter/X:
```{r}
twitter_formula_main_model <- "log(alt_twitter+1) ~ inferred_gender + years_since_first_pub + as.factor(year) + log(count_pubs_total_l+1) + log(cited_by_total_all_l+1) + log(coa_tot_cited_by_total_l+1) + log(coa_online_combi_total_l+1) + log(news_all_total_l+1) + log(alt_online_all_total_l+1) + avg_sjr_total_l + share_first_au_total_l + institution_dutch_total_narcis"

twitter_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                               lm_formula = twitter_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               index = c("profile_id", "year"),
                                               fe_re = "fe")
```


Write out the result table:
```{r warning = F}
options(scipen=999)

table_models <- neat_regression_table_scopus(news_model[[1]],
                                             online_news_model[[1]],
                                             twitter_model[[1]],
                                             fe = "yes")

# add to the list
all_reg_rob_list[['fe']] <- table_models

table_models_save <- table_models %>%
    regulartable() %>% 
    set_caption("Main model - two-way fixed effects")%>%
    autofit()


word_document_name <-
  read_docx() %>%
  body_add_flextable(table_models_save) %>%
  print(target = "results/supplement_tables/SI_online_main_model_table_fe.docx")
```

Show the table below:
```{r}
(table_models_save)
```


## Fixed effects models - first lag

Now, fit the FE models with the first lag of the dependent variable included:

Printed news attention:
```{r warning = F}
news_formula_main_model <- "log(news_all+1) ~ log(news_all_l+1) + inferred_gender + years_since_first_pub + as.factor(year) + log(count_pubs_total_l+1) + log(cited_by_total_all_l+1) + log(coa_tot_cited_by_total_l+1) + log(coa_online_combi_total_l+1) + log(alt_online_all_total_l+1) + log(alt_twitter_total_l+1) + avg_sjr_total_l + share_first_au_total_l + institution_dutch_total_narcis"

news_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                            lm_formula = news_formula_main_model,
                                            year_cutoff_upper = 2023,
                                            year_cutoff_lower = 2012,
                                            index = c("profile_id", "year"),
                                            fe_re = "fe")
```


Online news attention:
```{r}
online_news_formula_main_model <- "log(alt_online_all+1) ~ log(alt_online_all_l+1) + inferred_gender + years_since_first_pub + as.factor(year) + log(count_pubs_total_l+1) + log(cited_by_total_all_l+1) + log(coa_tot_cited_by_total_l+1) + log(coa_online_combi_total_l+1) + log(news_all_total_l+1) + log(alt_twitter_total_l+1) + avg_sjr_total_l + share_first_au_total_l + institution_dutch_total_narcis"


online_news_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                                   lm_formula = online_news_formula_main_model,
                                                   year_cutoff_upper = 2023,
                                                   year_cutoff_lower = 2012,
                                                   index = c("profile_id", "year"),
                                                   fe_re = "fe")
```

Twitter/X:
```{r}
twitter_formula_main_model <- "log(alt_twitter+1) ~ log(alt_twitter_l+1) + inferred_gender + years_since_first_pub + as.factor(year) + log(count_pubs_total_l+1) + log(cited_by_total_all_l+1) + log(coa_tot_cited_by_total_l+1) + log(coa_online_combi_total_l+1) + log(news_all_total_l+1) + log(alt_online_all_total_l+1) + avg_sjr_total_l + share_first_au_total_l + institution_dutch_total_narcis"

twitter_model <- fe_re_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                               lm_formula = twitter_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               index = c("profile_id", "year"),
                                               fe_re = "fe")
```


Combine the models and write out the table:
```{r warning = F}
options(scipen=999)

table_models <- neat_regression_table_scopus(news_model[[1]],
                                             online_news_model[[1]],
                                             twitter_model[[1]],
                                             fe = "yes")

# add to the list
all_reg_rob_list[['fe']] <- table_models

table_models_save <- table_models %>%
    regulartable() %>% 
    set_caption("Main model - two-way fixed effects with lag")%>%
    autofit()


word_document_name <-
  read_docx() %>%
  body_add_flextable(table_models_save) %>%
  print(target = "results/supplement_tables/SI_online_main_model_table_fe_lag.docx")
```

Show the table below:
```{r}
table_models_save
```

```{r}
saveRDS(all_reg_rob_list,  "results/main_models_fe.RDS")
```

## Figure S9:

Plot out the coefficients.

First, preparing the coefficient dataframe:
```{r}
model_news <- news_model[[1]]
model_online_news <- online_news_model[[1]]
model_twitter <- twitter_model[[1]]

model_news$model <- "News attention"
model_online_news$model <- "Online news attention"
model_twitter$model <- "Twitter attention"

all_models_plot <- rbind(model_news,
                         model_online_news,
                         model_twitter)

# do the t-1 of dependent as a single variable
all_models_plot$term <- ifelse(all_models_plot$term %in% c("log(news_all_l + 1)",
                                                           "log(alt_online_all_l + 1)",
                                                           "log(alt_twitter_l + 1)"), 
                               "t_min_1", 
                               all_models_plot$term)


all_models_plot$term <- ordered(all_models_plot$term,
                                levels = c(
                                  "(Intercept)",
                                  "t_min_1",
                                  "log(count_pubs_total_l + 1)",
                                  "share_first_au_total_l",
                                  "log(cited_by_total_all_l + 1)",
                                  "avg_sjr_total_l",
                                  "log(news_all_total_l + 1)",
                                  "log(alt_online_all_total_l + 1)", 
                                  "log(alt_twitter_total_l + 1)",
                                  "log(coa_tot_cited_by_total_l + 1)",
                                  "log(coa_online_combi_total_l + 1)",
                                  "years_since_first_pub",
                                  "as.factor(year)2014",
                                  "as.factor(year)2015",
                                  "as.factor(year)2016",
                                  "as.factor(year)2017",
                                  "as.factor(year)2018",
                                  "as.factor(year)2019",
                                  "as.factor(year)2020",
                                  "as.factor(year)2021",
                                  "as.factor(year)2022",
                                  "as.factor(year)2023",
                                  "institution_dutch_total_narcisuni_1",
                                  "institution_dutch_total_narcisuni_2",
                                  "institution_dutch_total_narcisuni_3",
                                  "institution_dutch_total_narcisuni_4",
                                  "institution_dutch_total_narcisuni_5",
                                  "institution_dutch_total_narcisuni_6",
                                  "institution_dutch_total_narcisuni_7",
                                  "institution_dutch_total_narcisuni_8",
                                  "institution_dutch_total_narcisuni_9",
                                  "institution_dutch_total_narcisuni_10",
                                  "institution_dutch_total_narcisuni_11",
                                  "institution_dutch_total_narcisuni_12",
                                  "institution_dutch_total_narcisuni_13",
                                  "institution_dutch_total_narcisuni_14",
                                  "institution_dutch_total_narcisuni_15",
                                  "R^2"))

all_models_plot$model <- ordered(all_models_plot$model,
                                 levels = c("News attention",
                                            "Online news attention",
                                            "Twitter attention" ))

all_models_plot$field <- ordered(all_models_plot$field,
                                 levels = c("phys",
                                            "life",
                                            "health",
                                            "soc_sci",
                                            "arts"))

covariate_names <- c(
  't_min_1' = "Dependent variable -\n previous period",
  'log(cited_by_total_all_l + 1)'="Total citations\n(log-transformed)",
  'log(count_pubs_total_l + 1)'="Total publications\n(log-transformed)",
  'log(news_all_total_l + 1)'="Total printed news \nattention (log-transformed)",
  'log(alt_online_all_total_l + 1)'="Total online news\n attention (log-transformed)",
  'log(alt_twitter_total_l + 1)'="Total Twitter/X \nattention (log-transformed)",
  'log(coa_tot_cited_by_total_l + 1)' = "Coauthors' total citations\n(log-transformed)",
  'log(coa_online_combi_total_l + 1)' = "Coauthors' total online \nnews and Twitter/X attention\n(log-transformed)",
  'share_first_au_total_l' = "Total share of first- and \nsingle-authored publications",
  'avg_sjr_total_l' = "Total average SJR \nscore of publications"
)
```

Draw the plot:
```{r fig.width=8, fig.height=13}
field_names <- c("arts" = "Arts and\n Humanities",
                 "health" = "Health \nsciences",
                 "soc_sci" = "Social \nsciences",
                 "life" = "Life sciences",
                 "phys" = "Physical \nsciences")

media_names <- c('News attention' = "Printed news",
                 'Online news attention' = "Online news",
                 'Twitter attention' = "Twitter/X")

media_field_names <- c(media_names,
                       field_names)


(all_plot <- all_models_plot %>%
    filter(term %in% c(
      "t_min_1",
      "log(count_pubs_total_l + 1)",
      "share_first_au_total_l",
      "log(cited_by_total_all_l + 1)",
      "avg_sjr_total_l",
      "log(coa_tot_cited_by_total_l + 1)",
      "log(coa_online_combi_total_l + 1)")) %>%
    ggplot(aes(Estimate, fct_rev(term), color = model, shape = model, label = stars)) +
    geom_point(position = position_dodge(width = -0.7), size = 3) +
    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci),
                  width=0,
                  size=0.7,
                  position = position_dodge(width = -0.7)) +
    geom_text(hjust=0, vjust=0, position = position_dodge(width = -0.7), size = 3.5)+
    scale_y_discrete(labels=covariate_names,
                     name = "Field")+
    scale_color_manual(labels = c("Printed news", "Online news", "Twitter/X"), values = c("#bb7693", "#ef6f6a", "#6388b4"))+
    scale_shape_discrete(labels = c("Printed news", "Online news", "Twitter/X"))+
    #scale_x_continuous(limits = c(0, 4.5), breaks = seq(0, 4.5, by = 0.5))+
    labs(
      x = "Regression coefficient",
      y = NULL,
      color = "Attention type",
      shape = "Attention type"
    ) + 
    geom_vline(xintercept = 0,  colour="black", linetype = "longdash")+
    facet_grid(field ~ model, labeller = as_labeller(media_field_names), scales = "free_x")+
    theme_minimal_hgrid()+
    theme(plot.title = element_text(size = 11),
          axis.text.y = element_text(size = 10),
          axis.title.y = element_blank(),
          axis.text.x = element_text(size = 10, angle = 30, hjust = 0.9) ,
          axis.title.x = element_text(size = 10),
          legend.position = "none")+
    panel_border())



ggsave2(
  filename = "results/supplement_figures/SI_Fig_S9.png",
  plot = all_plot,
  width = 8,
  height = 13,
  units = c("in"),
  dpi = 1200,
  bg = "white"
)

```
