---
title: "SI Robustness checks: logistic models"
author: "Ana Macanovic"
date: "2024-07-24"
---


Robustness checks including various logistic model specifications.
All specifications include standard errors clustered at the professor level.

Load the packages:
```{r message=  F, warning = F, eval = T}
source("helper_functions.R")

packages_to_load <- c("readr", "dplyr", "tidyr", 
                      "ggplot2", "cowplot",
                      "tidyverse", "RPostgres", 
                      "lubridate", "lmtest", 
                      "sandwich", "ggpubr", 
                      "knitr", "scales", 
                      "ggeffects", "flextable", 
                      "officer", "DescTools",
                      "gglorenz", "corrplot")

fpackage_check(packages_to_load)


# For full reproducibility, load the packages with groundhog using the code below instead
# of the fpackage_check function

# library(groundhog)
# groundhog.library(packages_to_load, date = "2024-4-23")
```


```{r include=FALSE}
opts_chunk$set(echo = TRUE)
opts_chunk$set(eval = TRUE)
opts_chunk$set(warning = FALSE)
opts_chunk$set(message = FALSE)
```


Load the panel dataset:
```{r warning = F, message = F}
prof_panel_filter <- read_csv("panel_datasets/prof_panel_anonymised.csv")
```

Make a list to save all the results into:
```{r}
all_reg_rob_list <- list()
```

## Logistic models - any attetion

Model with a binary indicator of whether the professor received any attention of
a certain type in a given year.

### Printed news attention

```{r warning = F}
news_formula_main_model <- "any_news  ~ inferred_gender + news_all_l + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

news_model_logit <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                         formula_list = news_formula_main_model,
                                         year_cutoff_upper = 2023,
                                         year_cutoff_lower = 2012,
                                         reg_family = "binomial")
```

### Online news attention 
```{r warning = F}
online_news_formula_main_model <- "any_online_news  ~ inferred_gender + alt_online_all_l + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

online_news_model_logit <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                               formula_list = online_news_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               reg_family = "binomial")
```

### Twitter/X
```{r warning = F}
twitter_formula_main_model <- "any_twitter  ~ inferred_gender + alt_twitter_l + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

twitter_model_logit <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = twitter_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "binomial")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models_logit <- neat_regression_table_scopus(news_model_logit[[1]],
                                           online_news_model_logit[[1]],
                                           twitter_model_logit[[1]])
# add to the list
all_reg_rob_list[['logit_any']] <- table_models_logit

(table_models_save <- table_models_logit %>%
  regulartable() %>%
  set_caption("Logistic model - any attention")%>%
  autofit())

word_document_name <-
    read_docx() %>%
    body_add_flextable(table_models_save) %>%
    print(target = "results/supplement_tables/logistic_model_any_att.docx")
```



## Logistic models - top 10% attetion

Model with a binary indicator of whether the professor was in the top 10% of professors
within an  attention type in a given year.

### Printed news attention

```{r ?, warning=FALSE}
news_formula_main_model <- "news_all_top_10  ~ inferred_gender + news_all_l + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

news_model_logit <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = news_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "binomial")
```

### Online news attention 
```{r warning = F}
online_news_formula_main_model <- "alt_online_all_top_10  ~ inferred_gender + alt_online_all_l + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

online_news_model_logit <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                               formula_list = online_news_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               reg_family = "binomial")
```

### Twitter/X
```{r warning = F}
twitter_formula_main_model <- "alt_twitter_top_10  ~ inferred_gender + alt_twitter_l + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

twitter_model_logit <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = twitter_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "binomial")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models_logit <- neat_regression_table_scopus(news_model_logit[[1]],
                                           online_news_model_logit[[1]],
                                           twitter_model_logit[[1]])

# add to the list
all_reg_rob_list[['logit_top_10']] <- table_models_logit

(table_models_save <- table_models_logit %>%
  regulartable() %>%
  set_caption("Logistic model - top 10% of attention")%>%
  autofit())

word_document_name <-
    read_docx() %>%
    body_add_flextable(table_models_save) %>%
    print(target = "results/supplement_tables/logistic_model_top10_att.docx")
```


## Logistic models - top 20% attetion

Model with a binary indicator of whether the professor was in the top 20% of professors
within an  attention type in a given year.

### Printed news attention

```{r warning = F}
news_formula_main_model <- "news_all_top_20  ~ inferred_gender + news_all_l + cited_by_total_all_l + alt_online_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

news_model_logit <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = news_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "binomial")
```

### Online news attention 
```{r warning = F}
online_news_formula_main_model <- "alt_online_all_top_20  ~ inferred_gender + alt_online_all_l + cited_by_total_all_l + news_all_total_l + alt_twitter_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

online_news_model_logit <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                               formula_list = online_news_formula_main_model,
                                               year_cutoff_upper = 2023,
                                               year_cutoff_lower = 2012,
                                               reg_family = "binomial")
```

### Twitter/X
```{r warning = F}
twitter_formula_main_model <- "alt_twitter_top_20  ~ inferred_gender + alt_twitter_l + cited_by_total_all_l + news_all_total_l + alt_online_all_total_l +coa_tot_cited_by_total_l + coa_tot_online_all_total_l + coa_tot_twitter_total_l+years_since_first_pub + as.factor(year)"

twitter_model_logit <- glm_fitter_cl_robust_scopus(panel_dataset = prof_panel_filter,
                                           formula_list = twitter_formula_main_model,
                                           year_cutoff_upper = 2023,
                                           year_cutoff_lower = 2012,
                                           reg_family = "binomial")
```


### Combined coefficients

Combine this all to plot the coefficients in one plot.
```{r warning = F}
options(scipen=999)

table_models_logit <- neat_regression_table_scopus(news_model_logit[[1]],
                                           online_news_model_logit[[1]],
                                           twitter_model_logit[[1]])

# add to the list
all_reg_rob_list[['logit_top_20']] <- table_models_logit

(table_models_save <- table_models_logit %>%
  regulartable() %>%
  set_caption("Logistic model - top 20% of attention")%>%
  autofit())

word_document_name <-
    read_docx() %>%
    body_add_flextable(table_models_save) %>%
    print(target = "results/supplement_tables/logistic_model_top20_att.docx")
```


Save the list:
```{r}
saveRDS(all_reg_rob_list, "results/logit_models.RDS")
```
