---
title: "Preparation: Data Coverage"
author: "Ana Macanovic"
date: "2024-02-14"
output: html_document
---

This script provides a description of various tables in our final database.
Finally, it compares the coverage of OpenAlex to NARCIS.

Load the necessary packages:
```{r message=  F, warning = F, eval = T}
source("helper_functions.R")
packages_to_load <- c("readr", "dplyr", "jsonlite", "tidyr",
                      "stringr", "ggplot2", "RPostgres", "lubridate",
                      "digest","DBI", "RODBC", "odbc", "knitr", "tidyverse")

fpackage_check(packages_to_load)

# For full reproducibility, load the packages with groundhog using the code below instead
# of the fpackage_check function
# library(groundhog)
# groundhog.library(packages_to_load, date = "2023-12-01")
```

```{r include=FALSE}
opts_chunk$set(echo = TRUE)
opts_chunk$set(eval = FALSE)
opts_chunk$set(warning = FALSE)
opts_chunk$set(message = FALSE)
```

Connect to our database:
```{r}
port <- 5432
user <- "postgres"
password <- "dutchmediaprofssql"
database_name <- "postgres"

con <- dbConnect(Postgres(),
                 dbname= database_name,
                 port = port,
                 user = user, 
                 password = password)
```


# Data descriptives

## NARCIS data

First, the counts of professor profiles and NARCIS publications:
```{r}
profs_full <- dbGetQuery(con, "select * from narcis_prof_info;")
prof_pubs_full <- dbGetQuery(con, "select * from narcis_pub_info;")

nrow(profs_full)
nrow(prof_pubs_full)
```

ORCIDs:
```{r}
prof_orcids <- dbGetQuery(con, "select * from orcid_mapping;")

prof_orcids_unique <- distinct(prof_orcids, profile_id, .keep_all = TRUE)

narcis_orcids <- filter(profs_full, !is.na(ORCID))

nrow(narcis_orcids)

prof_orcids_unique_new <- filter(prof_orcids_unique,
                                 ! profile_id %in% narcis_orcids$profile_id)

nrow(prof_orcids_unique_new)

nrow(prof_orcids_unique)
```

## Grant data

Grant info.
1. NWO:
```{r}
narcis_nwo_grant_info <- dbGetQuery(con, "select * from narcis_nwo_grant_info;")

nrow(narcis_nwo_grant_info)

nwo_per_prof <- narcis_nwo_grant_info %>%
  group_by(profile_id)%>%
  summarise(n_veni = sum(grant == "veni"),
            n_vidi = sum(grant == "vidi"),
            n_vici = sum(grant == "vici"),
            n_spinoza = sum(grant == "spinoza"),
            n_stevin = sum(grant == "stevin"),
            any = n())

nrow(nwo_per_prof)

mean(nwo_per_prof$any)


nwo_summary <- narcis_nwo_grant_info %>%
  group_by(grant)%>%
  summarise(n = n())

nwo_summary
```

2. ERC:
```{r}
erc_grant_info <- dbGetQuery(con, "select * from erc_grant_info;")

nrow(erc_grant_info)

erc_per_prof <- erc_grant_info %>%
  group_by(profile_id)%>%
  summarise(any = n())

nrow(erc_per_prof)
mean(erc_per_prof$any)

erc_summary <- erc_grant_info %>%
  group_by(grant_type)%>%
  summarise(n = n())

erc_summary
```

## OpenAlex data

### OA IDs

Now, information about OA IDs:
```{r}
oa_id_mapping <- dbGetQuery(con, "select * from oa_id_mapping;")

missing <- filter(profs_full, ! profile_id %in% oa_id_mapping$profile_id)
# missing IDs
nrow(missing)
```
Source of OA IDs:
```{r}
oa_id_mapping$source2 <- ifelse(oa_id_mapping$source == "name",
                                "name",
                                "doi_orcid") 

oa_id_mapping_sources <- distinct(oa_id_mapping, profile_id,
                                  .keep_all = TRUE)

table(oa_id_mapping_sources$source2)
prop.table(table(oa_id_mapping_sources$source2))*100
```

Average OA IDs per professor:
```{r}
oa_id_mapping_avg <- oa_id_mapping %>%
  group_by(profile_id)%>%
  summarise(n = n())

mean(oa_id_mapping_avg$n)
median(oa_id_mapping_avg$n)
sd(oa_id_mapping_avg$n)
```

### OA publications

Counts of publications we retrieve from OA:
```{r}
oa_prof_pubs <- dbGetQuery(con, "select * from oa_prof_pubs;")

oa_prof_pubs_unique <- distinct(oa_prof_pubs, id, .keep_all = TRUE)

nrow(oa_prof_pubs_unique)

oa_pubs_per_prof <- oa_prof_pubs_unique %>%
  group_by(profile_id)%>%
  summarise(n = n())

mean(oa_pubs_per_prof$n)
median(oa_pubs_per_prof$n)
sd(oa_pubs_per_prof$n)
quantile(oa_pubs_per_prof$n)
```

## Coauthors
Information on coauthors:
```{r}
oa_prof_coauthors <- dbGetQuery(con, "select * from oa_coauthor_info;")

oa_prof_coauthors_unique <- distinct(oa_prof_coauthors, au_id, .keep_all = TRUE)

oa_coauthors_per_prof <- oa_prof_coauthors_unique %>%
  group_by(profile_id)%>%
  summarise(n = n())

mean(oa_coauthors_per_prof$n)
median(oa_coauthors_per_prof$n)
sd(oa_coauthors_per_prof$n)
quantile(oa_coauthors_per_prof$n)
```

### Coauthor attention

```{r}
altmetric_coauthor_attention <- dbGetQuery(con, "select * from altmetric_coauthor_attention;")

altmetric_coauthor_attention_unique <- distinct(altmetric_coauthor_attention,
                                                id, 
                                                .keep_all = TRUE)

nrow(altmetric_coauthor_attention_unique)
```

### Coauthor first names

```{r}
coauthor_name_gender <- dbGetQuery(con, "select * from coauthor_name_gender;")

coauthor_name_list <- dbGetQuery(con, "select * from oa_coauthor_name_list;")

# which ones have no first name?
no_first_coauthors <- filter(oa_prof_coauthors_unique,
                             ! au_id %in% coauthor_name_list$id)

nrow(no_first_coauthors)
nrow(no_first_coauthors)/nrow(oa_prof_coauthors_unique)*100

# NAs in the gender list
nrow(coauthor_name_gender)
nrow(filter(coauthor_name_gender, !is.na(gender)))
nrow(filter(coauthor_name_gender, is.na(gender)))

# which ones have gender determined
coauthor_name_list$name <- tolower(coauthor_name_list$first)
coauthor_name_list_match <- merge(coauthor_name_list,
                                  coauthor_name_gender,
                                  by = "name",
                                  all.x = TRUE)

nrow(coauthor_name_list)
coauthor_name_list_not_na <- filter(coauthor_name_list_match,
                                    !is.na(gender))

nrow(coauthor_name_list_not_na)
table(coauthor_name_list_not_na$gender)
prop.table(table(coauthor_name_list_not_na$gender))*100
```

## Attention data

News attention:
```{r}
altmetric_pub_att_blogs <- dbGetQuery(con, "select * from altmetric_pub_att_blogs;")
altmetric_pub_att_news <- dbGetQuery(con, "select * from altmetric_pub_att_news;")
altmetric_pub_att_reddit <- dbGetQuery(con, "select * from altmetric_pub_att_reddit;")
altmetric_pub_att_wiki <- dbGetQuery(con, "select * from altmetric_pub_att_wiki;")
altmetric_pub_att_policy <- dbGetQuery(con, "select * from altmetric_pub_att_policy;")
# altmetric_pub_att_twitter <- dbGetQuery(con, "select * from altmetric_pub_att_twitter;")

```

Average mentions per publication:
```{r}
items <- c("blogs", "news", "reddit", "wiki", "policy")
total_pubs <- 1208052

for (item in items){
  data <- get(paste0("altmetric_pub_att_", item))
  
  grouped <- data %>%
    group_by(id)%>%
    summarise(n = n())
  
  print(item)
  print(paste("attention count:", nrow(data)))
  print(paste("publications receiving attention:", nrow(grouped)))
  print(paste("share w/ att. out of all pub:", nrow(grouped)/total_pubs*100))
  print(paste("attention per mentioned pub:", sum(grouped$n)/nrow(grouped)))
  print(paste("attention per any pub:", sum(grouped$n)/total_pubs))
}
```


# OA vs NARCIS publication coverage

Using DOIs and titles, estimate the extent to which OA covers our NARCIS data.

Get the coverage table per professor:
```{r}
# if needed, query the full NARCIS and OA publication lists
narcis_pubs <- dbGetQuery(con, "select * from narcis_pub_info;")
oa_pubs <- dbGetQuery(con, "select * from oa_prof_pubs;")
# for OA, only the unique publications (since the oa_prof_pubs table is in pub/year format)
oa_pubs <- distinct(oa_pubs, id, profile_id, .keep_all = TRUE)

# remove the html parts of the doi from both
narcis_pubs$doi_match <- str_remove(narcis_pubs$DOI, "https://doi.org/")
oa_pubs$doi_match <- str_remove(oa_pubs$doi, "https://doi.org/")

# clean the titles of both
narcis_pubs$title_match <- str_squish(tolower(str_remove_all(narcis_pubs$Title, "[^[:alnum:] ]")))
oa_pubs$title_match <- str_squish(tolower(str_remove_all(oa_pubs$display_name, "[^[:alnum:] ]")))

# find which NARCIS pubs also in OA and vice versa

# first, seek matches by DOI unless DOI is NA
narcis_pubs$in_oa_doi <- ifelse((narcis_pubs$doi_match %in% oa_pubs$doi_match) & !is.na(narcis_pubs$DOI),
                                TRUE,
                                FALSE)

oa_pubs$in_narcis_doi <- ifelse((oa_pubs$doi_match %in% narcis_pubs$doi_match) & !is.na(oa_pubs$doi),
                                TRUE,
                                FALSE)

# then, seek matches per title unless title is NA
narcis_pubs$in_oa_title <- ifelse((narcis_pubs$title_match %in% oa_pubs$title_match) & !is.na(narcis_pubs$title_match),
                                  TRUE,
                                  FALSE)

oa_pubs$in_narcis_title <- ifelse((oa_pubs$title_match %in% narcis_pubs$title_match) & !is.na(oa_pubs$title_match),
                                  TRUE,
                                  FALSE)

# if any of the two match, match is TRUE, otherwise FALSE
narcis_pubs$in_oa <- ifelse(narcis_pubs$in_oa_doi == TRUE | narcis_pubs$in_oa_title == TRUE,
                            TRUE,
                            FALSE)

oa_pubs$in_narcis <- ifelse(oa_pubs$in_narcis_doi == TRUE | oa_pubs$in_narcis_title == TRUE,
                            TRUE,
                            FALSE)


# per professor, get counts in each dataset and then get the count of matches
# against the other database
# NARCIS pubs and NARCIS pubs also found in OA
narcis_prof <- narcis_pubs %>%
  group_by(profile_id)%>%
  summarise(n_narcis = n(),
            narcis_vs_oa = sum(in_oa == TRUE))

# OA pubs and OA pubs also found in NARCIS
oa_prof <- oa_pubs %>%
  group_by(profile_id)%>%
  summarise(n_oa = n(),
            oa_vs_narcis = sum(in_narcis == TRUE))

# combine the two, replace NAs
full_prof_coverage <- merge(narcis_prof,
                            oa_prof,
                            by = "profile_id",
                            all.x = TRUE,
                            all.y = TRUE)%>%
  replace(is.na(.), 0)

# replace with NAs if either of the sources is empty
# get share of NARCIS pubs that are in OA, and the share of OA pubs that are in NARCIS
full_prof_coverage$coverage_narcis_oa <- ifelse(full_prof_coverage$n_narcis == 0|full_prof_coverage$n_oa == 0,
                                                NA,
                                                round(full_prof_coverage$narcis_vs_oa/full_prof_coverage$n_narcis, 2))

full_prof_coverage$coverage_oa_narcis <- ifelse(full_prof_coverage$n_oa == 0|full_prof_coverage$n_narcis == 0,
                                                NA,
                                                round(full_prof_coverage$oa_vs_narcis/full_prof_coverage$n_oa, 2))


```

So, in total, we get the coverage data for 6798 out of 6830 professors (99.5 %, missing 32).

## Overall statistics
We have NARCIS publications for 5627 professors, or 82% of our NARCIS dataset. 
```{r}
length(which(full_prof_coverage$n_narcis != 0))
length(which(full_prof_coverage$n_narcis != 0))/6830*100
```
We have ORCID publications for 6798 professors, or 99% of our NARCIS dataset. 
```{r}
length(which(full_prof_coverage$n_oa != 0))
length(which(full_prof_coverage$n_oa != 0))/6830*100
```

## NARCIS vs OA
Check the share of publications we retrieve from NARCIS that are also present in our
OA data.

On average, 79% of publications in our NARCIS dataset are also in our OA dataset.
```{r}
round(mean(full_prof_coverage$coverage_narcis_oa, na.rm = TRUE), 2)
```
Median coverage is 91%:
```{r}
summary(full_prof_coverage$coverage_narcis_oa)
```

## OA vs NARCIS
On average, 42% of publications in our OA dataset are also in our NARCIS dataset.
```{r}
round(mean(full_prof_coverage$coverage_oa_narcis, na.rm = TRUE), 2)
```

Median coverage is 42%:
```{r}
summary(full_prof_coverage$coverage_oa_narcis)
```

# A flat table of professor statistics
```{r}
oa_prof_pubs_unique <- dbReadTable(con, "oa_prof_pubs_unique")

altmetric_pub_att_news <- dbReadTable(con, "altmetric_pub_att_news")
altmetric_pub_att_wiki <- dbReadTable(con, "altmetric_pub_att_wiki")

# merge

grouped_news <- altmetric_pub_att_news %>%
  group_by(id)%>%
  summarise(n_news = n())

grouped_wiki <- altmetric_pub_att_wiki %>%
  group_by(id)%>%
  summarise(n_wiki = n())

grouped_policy <- altmetric_pub_att_policy %>%
  group_by(id)%>%
  summarise(n_policy = n())

oa_prof_pubs_merge <- merge(oa_prof_pubs,
                            grouped_news,
                            all.x = TRUE,
                            by = "id")

oa_prof_pubs_merge <- merge(oa_prof_pubs_merge,
                            grouped_wiki,
                            all.x = TRUE,
                            by = "id")

oa_prof_pubs_merge <- merge(oa_prof_pubs_merge,
                            grouped_policy,
                            all.x = TRUE,
                            by = "id")

per_prof_stats <- oa_prof_pubs_merge %>%
  group_by(profile_id)%>%
  summarise(n = n(),
            news = sum(n_news))

```

