---
title: "Preparation: NWO Grant preparation"
author: "Ana Macanovic"
date: "2023-12-20"
---

In this script, we tidy up the grant information on Veni/Vidi/Vici grants parsed
from the NWO website, and match the grant recipients with professors in our data.


Load the libraries that we need:
```{r eval = T, echo=FALSE, results='hide', message = F, warning=F}
source("helper_functions.R")
packages_to_load <- c("readr", "dplyr", "knitr",
                      "stringr", "ggplot2", "DBI", "RODBC", "odbc")

fpackage_check(packages_to_load)

# For full reproducibility, load the packages with groundhog using the code below instead
# of the fpackage_check function

# library(groundhog)
# groundhog.library(packages_to_load, date = "2023-12-01")
```

```{r include = F}
knitr::opts_chunk$set(echo = TRUE)
opts_chunk$set(eval = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)

```

Connect to the database:
```{r}
# fill in own credentials
port <- 5432
user <- "postgres"
password <- "dutchmediaprofssql"
database_name <- "postgres"


con <- dbConnect(Postgres(),
                 dbname= database_name,
                 port = port,
                 user = user, 
                 password = password)

con # Checks connection is working
```


# Parse NWO Veni, Vidi, Vici grant information

Read in the data about grant awards:
```{r warning = F, message = F}
professor_grant_awards <- read_csv("../dutch_media_profs_python/output-data/professor_grant_awards.csv")[, -1]

# deduplicate
professor_grant_awards$duplicates <- duplicated(professor_grant_awards)
professor_grant_awards <- filter(professor_grant_awards,
                                 duplicates == FALSE)

# remove the duplicatees indicator column
professor_grant_awards <- professor_grant_awards[, -ncol(professor_grant_awards)]
```

Now, we want to extract professor names from here. 
The easiest way is using the gender in the brackets of awardees, which we can 
replace by an easy token indicating splits:
```{r}
# introduce an easy "splitting" token instead of gender notions
professor_grant_awards$name_extract <- professor_grant_awards$professor
professor_grant_awards$name_extract <- str_squish(professor_grant_awards$name_extract)
professor_grant_awards$name_extract <- str_replace(professor_grant_awards$name_extract, "\\(m\\)",
                                                   "(*)")
professor_grant_awards$name_extract <- str_replace(professor_grant_awards$name_extract, "\\(v\\)",
                                                   "(*)")
professor_grant_awards$name_extract <- str_replace(professor_grant_awards$name_extract, "\\(f\\)",
                                                   "(*)")
professor_grant_awards$name_extract <- str_replace(professor_grant_awards$name_extract, "\\(M\\)",
                                                   "(*)")
professor_grant_awards$name_extract <- str_replace(professor_grant_awards$name_extract, "\\(V\\)",
                                                   "(*)")
professor_grant_awards$name_extract <- str_replace(professor_grant_awards$name_extract, "\\(F\\)",
                                                   "(*)")

# if there is no (*) identified, replace the first comma
professor_grant_awards$name_extract <- ifelse(str_detect(professor_grant_awards$name_extract, "\\(\\*\\)" ) == TRUE,
                                              professor_grant_awards$name_extract,
                                              str_replace(professor_grant_awards$name_extract, "\\,", " (*),")
                                              )
# if still none, replace the first -
professor_grant_awards$name_extract <- ifelse(str_detect(professor_grant_awards$name_extract, "\\(\\*\\)" ) == TRUE,
                                              professor_grant_awards$name_extract,
                                              str_replace(professor_grant_awards$name_extract, "\\b \\– \\b", " (*),")
                                              )

# extract only the part before the gender notion
professor_grant_awards$name_extracted <- str_split_i(professor_grant_awards$name_extract, "\\(\\*\\)", 1)

# remove the titles
titles_to_remove <- "\\b(Prof dr. ir. |Prof. dr. |Dr. ir.|Prof. |Dr. |ir. |Ph.D. |PhD | PhD|Dr.ing. |dr.|Dr.|Drs. |ing. |Ir.|ir.|Ing.|Prof.dr|mr.|Ir. |Prof.|ir ing.)\\b"
professor_grant_awards$name_extracted <- str_remove_all(professor_grant_awards$name_extracted, titles_to_remove)

# remove that one professor's birth date that lingers, and some institutions that also linger
remove_rest <- paste(c("- Amsterdam UMC", "27-03-1977",  "EUR MC - Neurosciences", "UU - Nanomaterial Science",
                 "- Hubrecht Institute", " - UMCG- Psychiatry", " - VU - Dept. of Functional Genomics", "\\(m0",
                 " - AMC - Rheumatology and clinical immunology"), collapse = "|")
professor_grant_awards$name_extracted <- str_remove_all(professor_grant_awards$name_extracted, remove_rest)



# clear the leading/trailing whitespaces
professor_grant_awards$name_extracted <- trimws(professor_grant_awards$name_extracted)
```

Clean this up a bit, removing empty rows and some misspecified lines:
```{r}
professor_grant_awards_clean <- filter(professor_grant_awards,
                                       name_extracted != "")

# count words and remove those with less than 1 and more than 5
professor_grant_awards_clean$words <- str_count(professor_grant_awards_clean$name_extracted, " ")
professor_grant_awards_clean <- filter(professor_grant_awards_clean,
                                       words > 0 & words < 6)

# delete any that contain institution/paper mentions
professor_grant_awards_clean$institution_paper <- str_detect(professor_grant_awards_clean$name_extracted,
                                                             "\\b(Leiden|Criminal|Semantics|wortelinteracties|Radboudumc|Institute|Department|Sciences|University|Erasmus|Faculty|
                                                             strategy|Imaging|E.coli|E. coli|Embodied|Escherichia coli|governance|tuberculosis|Research|This Vici was awarded|economic|horse|center|centrum)\\b")

professor_grant_awards_clean <- filter(professor_grant_awards_clean,
                                       institution_paper == FALSE)

# remove solitary dots at the beginning of the string
professor_grant_awards_clean$name_extracted <- str_replace(professor_grant_awards_clean$name_extracted, '^\\.', '')

# remove commas that made it in
professor_grant_awards_clean$name_extracted <- str_replace_all(professor_grant_awards_clean$name_extracted, ',', '')

# tidy up the dataframe
professor_grant_awards_clean <- professor_grant_awards_clean[c("professor", "grant", "year", "name_extracted")]

# still need to remove some titles
professor_grant_awards_clean$name_extracted <- str_remove(professor_grant_awards_clean$name_extracted, "Dr.|Mr. dr.|dr.|Ing.|Prof.|mr.")

# trim whitespaces again
professor_grant_awards_clean$name_extracted <- trimws(professor_grant_awards_clean$name_extracted)
```

Extract first and last names, as well as their initials:
```{r}
# are there any brackets surrounding the first name?
professor_grant_awards_clean$first_tf <- str_detect(professor_grant_awards_clean$name_extracted, 
                                                    "\\(")

# get the name within brackets
professor_grant_awards_clean$first <- gsub("(?<=\\()[^()]*(?=\\))(*SKIP)(*F)|.", 
                                     "", 
                                     professor_grant_awards_clean$name_extracted, 
                                     perl=T)

# there are only a few people without names in brackets whose first names are mentioned
#let us manually replace their first name fields:
professor_grant_awards_clean$first <- ifelse(professor_grant_awards_clean$name_extracted == "A.V. Artem Belopolsky", 
                                             "Artem",
                                             ifelse(professor_grant_awards_clean$name_extracted == "E. Enrique Jimenez-Melero",
                                                    "Enrique",
                                                    ifelse(professor_grant_awards_clean$name_extracted =="W. Willem Schinkel",
                                                           "Willem",
                                                           ifelse(professor_grant_awards_clean$name_extracted =="E.W. [Elmar] Tobi",
                                                                  "Elmar", professor_grant_awards_clean$first))))



# initials are before the first name in brackets, or before the space if no first name
professor_grant_awards_clean$initials <- ifelse(professor_grant_awards_clean$first_tf == TRUE,
                                                str_split_i(professor_grant_awards_clean$name_extracted, 
                                                            "\\(", 
                                                            1),
                                                str_split_i(professor_grant_awards_clean$name_extracted, 
                                                            " ", 
                                                            1))

# last name is after the bracket, or the last element if splitting by the dots in initials
professor_grant_awards_clean$last <- ifelse(professor_grant_awards_clean$first_tf == TRUE,
                                            str_split_i(professor_grant_awards_clean$name_extracted, 
                                                        "\\)", 
                                                        2),
                                            
                                            NA)

# if none, then split by the dot and take the last element
professor_grant_awards_clean$last <- ifelse(professor_grant_awards_clean$first_tf == FALSE,
                                            str_split_i(professor_grant_awards_clean$name_extracted, 
                                                        "\\. ", 
                                                        length(str_split(professor_grant_awards_clean$name_extracted, 
                                                                         "\\. ")[[1]])),
                                            
                                            
                                            professor_grant_awards_clean$last)
                                            
                                            
# only one professor without the last name left, manually adjust:
professor_grant_awards_clean$last <- ifelse(professor_grant_awards_clean$name_extracted == "Roseriet Beijers",
                                            "Beijers",
                                            professor_grant_awards_clean$last)
professor_grant_awards_clean$first <- ifelse(professor_grant_awards_clean$name_extracted == "Roseriet Beijers",
                                            "Roseriet",
                                            professor_grant_awards_clean$first)
professor_grant_awards_clean$initials <- ifelse(professor_grant_awards_clean$name_extracted == "Roseriet Beijers",
                                            "R",
                                            professor_grant_awards_clean$initials)

# and a few more for manual adjustment
professor_grant_awards_clean$last <- ifelse(professor_grant_awards_clean$name_extracted == "A.V. Artem Belopolsky", 
                                             "Belopolsky",
                                             ifelse(professor_grant_awards_clean$name_extracted == "E. Enrique Jimenez-Melero",
                                                    "Jimenez-Melero",
                                                    ifelse(professor_grant_awards_clean$name_extracted =="W. Willem Schinkel",
                                                           "Schinkel",
                                                           ifelse(professor_grant_awards_clean$name_extracted =="E.W. [Elmar] Tobi",
                                                                  "Tobi", professor_grant_awards_clean$last))))

# tidy up trailing white spaces
professor_grant_awards_clean$first <- trimws(professor_grant_awards_clean$first)
professor_grant_awards_clean$initials <- trimws(professor_grant_awards_clean$initials)
professor_grant_awards_clean$last <- trimws(professor_grant_awards_clean$last)
```

Now, clean up the data frame further:
```{r}
# rearrange
professor_grant_awards_final <- professor_grant_awards_clean[c("grant", "year", "first", "initials", "last", "professor")]
colnames(professor_grant_awards_final)[ncol(professor_grant_awards_final)] <- "full_string"

# delete any outstanding duplicates
professor_grant_awards_final$duplicate <- duplicated(professor_grant_awards_final[, c("grant", "year", "first", "initials", "last")])
professor_grant_awards_final <- filter(professor_grant_awards_final,
                                       duplicate == FALSE)

# delete the duplicate column
professor_grant_awards_final <- professor_grant_awards_final[, -c(ncol(professor_grant_awards_final))]
```

Some more cleaning up needed for the more recent years:
```{r}
professor_grant_awards_final <- filter(professor_grant_awards_final,
                                       ! initials %in% c("Donders", "Amsterdam", "Faculteit"))

# some professors are missing last names, so get them
professor_grant_awards_missing_last <- filter(professor_grant_awards_final,
                                             is.na(last))

# and extract the word after their first name
professor_grant_awards_missing_last$first_correction <- str_extract(professor_grant_awards_missing_last$full_string, 
                                                                    paste0("(?<=", professor_grant_awards_missing_last$initials, "\\s)[^;]+"))

professor_grant_awards_missing_last$last <- str_split_i(professor_grant_awards_missing_last$first_correction, " ", 1)
professor_grant_awards_missing_last$last <- str_remove(professor_grant_awards_missing_last$last, ",")

# manual replpacement for some last names containing "Van"
professor_grant_awards_missing_last$last[which(professor_grant_awards_missing_last$full_string  == "dr. E van Roekel (F), VU Amsterdam")] <- "van Roekel"
professor_grant_awards_missing_last$last[which(professor_grant_awards_missing_last$full_string  == "Lisanne van Dijk PhD, University Medical Center Groningen (UMCG)")] <- "van Dijk"
professor_grant_awards_missing_last$last[which(professor_grant_awards_missing_last$full_string  == "Dr. A van der Ent, Wageningen University &amp; Research")] <- "van der Ent"
professor_grant_awards_missing_last$last[which(professor_grant_awards_missing_last$initials  == "P")] <- "Wan"

# get the first names from the initials field where applicable
professor_grant_awards_missing_last$first[which(! professor_grant_awards_missing_last$initials  %in% c("P", "E", "J.S.L", "L", "A", "SRM"))] <- professor_grant_awards_missing_last$initials[which(! professor_grant_awards_missing_last$initials  %in% c("P", "E", "J.S.L", "L", "A", "SRM"))]

# turn their names into initials where applicable
professor_grant_awards_missing_last$initials[which(! professor_grant_awards_missing_last$initials  %in% c("P", "E", "J.S.L", "L", "A", "SRM"))] <- str_sub(professor_grant_awards_missing_last$initials, 1, 1)[which(! professor_grant_awards_missing_last$initials  %in% c("P", "E", "J.S.L", "L", "A", "SRM"))]

# add a full stop to the end of their initials
professor_grant_awards_missing_last$initials <- paste0(professor_grant_awards_missing_last$initials, ".")
professor_grant_awards_missing_last$initials[which(professor_grant_awards_missing_last$initials  == "SRM.")] <- "S.R.M"

# add this back on
professor_grant_awards_final_1 <- filter(professor_grant_awards_final,
                                         !is.na(last))

professor_grant_awards_final <- rbind(professor_grant_awards_final_1,
                                        professor_grant_awards_missing_last[colnames(professor_grant_awards_final_1)])
```


```{r}
# drop any redundant objects from memory
rm(professor_grant_awards)
rm(professor_grant_awards_clean)
rm(professor_grant_awards_final_1)
rm(professor_grant_awards_missing_last)
```

# Match grant information to professors 

Load the professor profiles:
```{r message = F, warning = F}
load("raw_data/media_profs_profiles.rda")
profs <- read_csv("raw_data/dutch_profs_urls.csv")

# merge the profs with their ORCIDs
colnames(profs)[c(1,7)] <- c("id", "profile_id")

profs_full <- merge(profs,
                    metadf[, c(1:4, 361)],
                    by = "profile_id")
```

Match by first and last names:
```{r}
professor_grant_match <- professor_grant_awards_final

professor_grant_match$both_match <- ifelse(((tolower(professor_grant_match$last) %in% profs_full$last) & (tolower(professor_grant_match$first) %in% profs_full$first)),
                                           TRUE,
                                           FALSE)
```

Filter only grants awarded to our profs:
```{r}
professor_grant_awards_narcis <- filter(professor_grant_match,
                                        both_match == TRUE)
```

Get the exact matching:
```{r}
professor_grant_awards_narcis$first_last <- tolower(paste(professor_grant_awards_narcis$first, 
                                                  professor_grant_awards_narcis$last))

profs_full$first_last <- tolower(paste(profs_full$first, profs_full$last))

professor_grant_awards_narcis_match <- merge(professor_grant_awards_narcis,
                                             profs_full[, c("profile_id", "first_last")],
                                             by = "first_last")
```

Since 2021, however, there are no first names on NWO pages, so let's check by last names:
```{r}
# also, filter out venis, because our professors are unlikely to have received those recently
professor_grant_match_2021 <- filter(professor_grant_awards_final,
                                     year > 2020 & grant != "veni")

professor_grant_match_2021$initials_last <- tolower(paste(professor_grant_match_2021$initials, professor_grant_match_2021$last))
profs_full$initials_last <- tolower(paste(str_split_i(profs_full$initialen, " \\(", 1), profs_full$last))

professor_grant_awards_narcis_match_2021 <- merge(professor_grant_match_2021,
                                             profs_full[, c("profile_id", "initials_last")],
                                             by = "initials_last")

# one duplicate with R. Vliegenthart, manually checking shows it's Rens and not Rozemarijn:
professor_grant_awards_narcis_match_2021 <- filter(professor_grant_awards_narcis_match_2021,
                                                   profile_id != "https://www.narcis.nl/person/RecordID/PRS1325655")

```

Merge the two parts of the dataset:
```{r}
professor_grant_awards_narcis_match <- professor_grant_awards_narcis_match[c("grant",
                                                                             "year",
                                                                             "profile_id")]

professor_grant_awards_narcis_match_2021 <- professor_grant_awards_narcis_match_2021[c("grant",
                                                                             "year",
                                                                             "profile_id")]

professor_grant_awards_narcis_final <- rbind(professor_grant_awards_narcis_match,
                                             professor_grant_awards_narcis_match_2021)
```


Write this out:
```{r}
saveRDS(professor_grant_awards_narcis_final, "processed_data/nwo_grants_intermediate.RDS")
```


