---
title: "Preparation: News source classification and other functions"
author: "Ana Macanovic"
date: "2024-07-24"
---

This script shows the content of .R files we use to classify types of printed
and online news sources. Additionally, it shows the source code of all custom
functions used in our analyses. 

# News source classification 

Printed news classification criteria. In the main analyses, everything but  
"national_news_nl", "regional_news_nl", and "high_profile_int" is classified as "other".

These categories match those describe in main text as follows:

1. national_news_nl: National news (NL)
2. regional_news_nl: Regional news (NL)
3. high_profile_int: International news
4. rest: Other sources

```{r, code = readLines("resources/lexis_news_outlet_classification.R")}
```

Online news classification criteria are as follows:

```{r, code = readLines("resources/altmetric_news_outlet_classification.R")}
```

# Other functions

Below we list the source code of all functions we use in our analyses.
```{r, code = readLines("helper_functions.R")}

```


