---
title: "Preparation: Professor-year panel compilation"
author: "Ana Macanovic"
date: "2025-04-10"
output: html_document
---

# Panel data compilation

This script compiles our various data resources into a panel dataset of professors'
publications, citations, mentions, and coauthorships per year.

The code below also produces some variables not used in the main analyses.
Refer to *Table S4* in the SI Appendix for the final variables used in our analysis. 

Load the packages:
```{r message=  F, warning = F, eval = T}
# load the helper function file
source("helper_functions.R")
packages_to_load <- c("readr", "dplyr", "tidyr", "PerformanceAnalytics",
                      "tidyverse", "RPostgres", "lubridate", "psych",
                      "digest", "DBI", "RODBC", "odbc", "gridExtra",
                      "panelr", "skimr", "foreach", "vegan", "knitr",
                      "doParallel")

fpackage_check(packages_to_load)

# For full reproducibility, load the packages with groundhog using the code below instead
# of the fpackage_check function

# library(groundhog)
# groundhog.library(packages_to_load, date = "2023-12-01")
```

```{r include=FALSE}
opts_chunk$set(echo = TRUE)
opts_chunk$set(eval = FALSE)
opts_chunk$set(warning = FALSE)
opts_chunk$set(message = FALSE)
```

Connect to the database:
```{r}
# fill in own credentials
port <- 5432
user <- "postgres"
password <- "dutchmediaprofssql"
database_name <- "postgres"


con <- dbConnect(Postgres(),
                 dbname= database_name,
                 port = port,
                 user = user, 
                 password = password)

con # Checks connection is working
```

# NARCIS data

Load the professor NARCIS profiles to start with
```{r message = F, warning = F}
narcis_prof_info <- dbReadTable(con, "narcis_prof_info")
```

Get a foundational panel dataset spanning between 1973 and 2023:
```{r}
baseline_panel <- expand.grid(unique(narcis_prof_info$profile_id), c(1973:2023))
colnames(baseline_panel) <- c("profile_id", "year")
```


# Publications and citations

Load publication info for all professors and tidy it up:
```{r}
# all professors, their pubs, and the yearly citation breakdown
oa_prof_pubs <- dbReadTable(con, "oa_prof_pubs")

# detailed information about pubications
oa_pubs_unique <- dbReadTable(con, "oa_prof_pubs_unique")

# dataset matching professor IDs to publications
oa_prof_pub_matching <- dbReadTable(con, "oa_prof_pub_match")

# match publication infromation with professors
oa_prof_pubs_unique <- merge(oa_pubs_unique,
                             oa_prof_pub_matching[c("id", "au_id", "au_display_name", "profile_id")],
                             all.x = TRUE,
                             all.y = TRUE,
                             by = "id")
```

Get single author publications only:
```{r}
# get information listing coauthors (au_id) per paper (id)
coauthor_info <- dbGetQuery(con, "select \"id\", \"au_id\" FROM oa_coauthor_info;")

# leave only publications without any coauthors
oa_prof_pubs_unique_single_au <- filter(oa_prof_pubs_unique, 
                                        ! id %in% coauthor_info$id)
```

## Yearly publication counts 

Get yearly publication counts per professor, filtering out everything but articles,
books, book chapters:
```{r}
prof_year_pubs <- oa_prof_pubs_unique %>% 
  filter(!is.na(publication_year) & publication_year >= 1973 & publication_year <= 2023 & 
           type %in% c("article", "book", "book-chapter"))%>%
  group_by(profile_id, publication_year)%>%
  summarise(count_pubs = n())%>%
  arrange(profile_id, publication_year)%>%
  mutate(count_pubs_total = cumsum(count_pubs))%>%
  arrange(profile_id, publication_year)

# rename for merging
colnames(prof_year_pubs)[which(colnames(prof_year_pubs) == "publication_year")] <- "year"
```

Now, get their yearly citations (2012-2023):
```{r}
prof_year_citations <- oa_prof_pubs %>% 
  filter(!is.na(publication_year) & !is.na(counts_by_year_year) & publication_year >= 1973 & publication_year <= 2023 &
           type %in% c("article", "book", "book-chapter"))%>%
  group_by(profile_id, counts_by_year_year)%>%
  summarise(cited_by = sum(counts_by_year_cited_by_count))%>%
  arrange(profile_id, counts_by_year_year) %>%
  mutate(cited_by_total_oa = cumsum(cited_by))%>%
  arrange(profile_id, counts_by_year_year)

# rename for merging
colnames(prof_year_citations)[which(colnames(prof_year_citations) == "counts_by_year_year")] <- "year"

prof_year_citations <- prof_year_citations %>%
  filter(year <= 2023)
```

Now, we want to know how many citations there were before 2012, so we get the totals
and then generate a new column getting the pre-2012 citations + each year's citations:
```{r}
# total citations per prof
prof_total_citations <- oa_prof_pubs_unique %>%
  filter(!is.na(publication_year) & publication_year >= 1973 & publication_year <= 2023 & 
           type %in% c("article", "book", "book-chapter"))%>%
  group_by(profile_id)%>%
  summarise(cited_by_since_pub_2024 = sum(cited_by_count))
# rename for merging
colnames(prof_total_citations)[which(colnames(prof_total_citations) == "publication_year")] <- "year"


# get the citations preceding 2012 by deducting the 2012 citations from the total
latest_citation <- prof_year_citations %>%
  group_by(profile_id)%>%
  slice(which.max(year))

# merge these two, replace NAs
prof_total_citations <- merge(prof_total_citations,
                              latest_citation[c("profile_id", "cited_by_total_oa")],
                              by = "profile_id",
                              all.x = TRUE,
                              all.y = TRUE)

prof_total_citations <- prof_total_citations %>%
  replace(is.na(.), 0)

# get the citation count for profs before 2012
prof_total_citations$cited_by_before_2012 <- prof_total_citations$cited_by_since_pub_2024 - prof_total_citations$cited_by_total_oa
  
# if this number negative (which it can be due to OA problems), replace by 0
prof_total_citations$cited_by_before_2012 <- ifelse(prof_total_citations$cited_by_before_2012 < 0,
                                                    0,
                                                    prof_total_citations$cited_by_before_2012)

# merge this with citation data
prof_year_citations <- merge(prof_year_citations,
                             prof_total_citations[c("profile_id", "cited_by_before_2012")],
                             all.x = TRUE,
                             by = "profile_id")

# get cumulative citations of pre 2012 + the year in question
prof_year_citations$cited_by_total_all <- prof_year_citations$cited_by_total_oa + prof_year_citations$cited_by_before_2012
```

Merge the publication and citation counts with the baseline panel:
```{r}
prof_year_pubs_citations <- merge(baseline_panel,
                                  prof_year_pubs,
                                  all.x = TRUE,
                                  all.y = TRUE,
                                  by = c("profile_id", "year"))


prof_year_pubs_citations <- merge(prof_year_pubs_citations,
                                  prof_year_citations,
                                  all.x = TRUE,
                                  all.y = TRUE,
                                  by = c("profile_id", "year"))
```

Tidy this all up:

```{r}
# fill some NAs for publication counts, but we will not do this for citations
prof_year_pubs_citations$count_pubs <- ifelse(is.na(prof_year_pubs_citations$count_pubs),
                                              0,
                                              prof_year_pubs_citations$count_pubs)

prof_year_pubs_citations <- prof_year_pubs_citations %>%
  arrange(profile_id, year)%>%
  group_by(profile_id)%>%
  mutate(count_pubs_total = cumsum(count_pubs))


# fill the citations before 2012
prof_year_pubs_citations <- prof_year_pubs_citations %>%
  group_by(profile_id)%>%
  fill(cited_by_before_2012, .direction = "up")
```

For each professor, get the first publication year and merge with the rest:
```{r}
# get professor entry years
prof_entry_year <- oa_prof_pubs_unique %>%
  filter(publication_year >= 1973 & publication_year <= 2023 & 
           type %in% c("article", "book", "book-chapter"))%>%
  group_by(profile_id)%>%
  slice(which.min(publication_year))%>%
  select(profile_id, publication_year)

# rename
colnames(prof_entry_year)[2] <- "first_pub"

# merge
prof_year_pubs_citations <- merge(prof_year_pubs_citations,
                                  prof_entry_year,
                                  all.x = TRUE,
                                  by = "profile_id")

# get indicator of years since first pub
prof_year_pubs_citations$years_since_first_pub <- prof_year_pubs_citations$year - prof_year_pubs_citations$first_pub
```

Merge this with professor gender:
```{r}
prof_gender <- dbReadTable(con, "gender_table")

prof_year_pubs_citations <- merge(prof_year_pubs_citations,
                                  prof_gender[c("profile_id", "inferred_gender")],
                                  all.x = TRUE,
                                  by = "profile_id")
```

Add information about their publications.
Load the Scimago scores:
```{r}
oa_pubs_all_scimago <- dbReadTable(con, "oa_prof_pubs_unique_scimago")
```

Tidy up the data and compile:
```{r}
oa_pubs_all_scimago$sjr <- as.numeric(str_replace(oa_pubs_all_scimago$sjr, ",", "."))

yearly_scimago <- oa_pubs_all_scimago %>%
  filter(publication_year >=1973 & publication_year <= 2023) %>%
  group_by(profile_id, publication_year)%>%
  summarise(sum_sjr = sum(sjr, na.rm = TRUE),
            sum_hindex = sum(h_index, na.rm = TRUE),
            count_q1 = sum(sjr_best_quartile == "Q1"),
            count_scimago_indicators = n())
```
Merge with the publication and citation data:
```{r}
prof_year_pubs_citations_sci <- merge(prof_year_pubs_citations,
                                      yearly_scimago,
                                      by.x = c("profile_id", "year"),
                                      by.y = c("profile_id", "publication_year"),
                                      all.x = TRUE)
```

Replace NAs with 0s if year is after 1999:
```{r}
prof_year_pubs_citations_sci <- prof_year_pubs_citations_sci%>% 
  mutate(sum_sjr  =  ifelse(year >= 1999 & is.na(sum_sjr), 0 , sum_sjr),
         sum_hindex  =  ifelse(year >= 1999 & is.na(sum_hindex), 0 , sum_hindex),
         count_q1  =  ifelse(year >= 1999 & is.na(count_q1), 0 , count_q1),
         count_scimago_indicators = ifelse(year >= 1999 & is.na(count_scimago_indicators), 0 , count_scimago_indicators)
  )
```


Write this out:
```{r}
write_csv(prof_year_pubs_citations_sci, "panel_datasets/prof_year_pubs_citations.csv")
```

# Grant information

Get all the grant information:
```{r}
nwo_grants <- dbReadTable(con, "narcis_nwo_grant_info")
erc_grants <- dbReadTable(con, "erc_grant_info")
```

Get this into a binary format:
```{r}
# for NWO
nwo_grants$veni <- ifelse(nwo_grants$grant == "veni", 1, 0)
nwo_grants$vidi <- ifelse(nwo_grants$grant == "vidi", 1, 0)
nwo_grants$vici <- ifelse(nwo_grants$grant == "vici", 1, 0)
nwo_grants$spinoza <- ifelse(nwo_grants$grant == "spinoza", 1, 0)
nwo_grants$stevin <- ifelse(nwo_grants$grant == "stevin", 1, 0)
# select only the necessary columns
nwo_grants <- nwo_grants %>%
  select(year:stevin)

# any grant
nwo_grants$any_nwo <- ifelse(rowSums(nwo_grants[, 3:7]) > 0, 1, 0)

# for ERC
erc_grants$advanced <- ifelse(erc_grants$grant == "Advanced grants", 1, 0)
erc_grants$consolidator <- ifelse(erc_grants$grant == "Consolidator grants", 1, 0)
erc_grants$starting  <- ifelse(erc_grants$grant == "Starting grants", 1, 0)
erc_grants$synergy <- ifelse(erc_grants$grant == "Synergy grants", 1, 0)
# select only the necessary columns
erc_grants <- erc_grants %>%
  select(profile_id:synergy)

# any grant
erc_grants$any_erc <- ifelse(rowSums(erc_grants[, 3:6]) > 0, 1, 0)
```

Accumulate grants, make sure there are no duplicates, and arrange nicely:
```{r}
nwo_cumulative <- nwo_grants %>%
  filter(year >= 1973 & year <= 2023)%>%
  arrange(profile_id, year)%>%
  group_by(profile_id)%>%
  mutate(nwo_total = cumsum(any_nwo))%>%
  distinct(profile_id, year, .keep_all = TRUE)

erc_cumulative <- erc_grants %>%
  filter(year >= 1973 & year <= 2023)%>%
  arrange(profile_id, year)%>%
  group_by(profile_id)%>%
  mutate(erc_total = cumsum(any_erc))%>%
  distinct(profile_id,year, .keep_all = TRUE)
```

Combine this with pubs and citations:
```{r}
prof_year_pubs_citations_grants <- merge(prof_year_pubs_citations_sci,
                                         nwo_cumulative,
                                         all.x = TRUE,
                                         by = c("profile_id", "year"))

prof_year_pubs_citations_grants <- merge(prof_year_pubs_citations_grants,
                                         erc_cumulative,
                                         all.x = TRUE,
                                         by = c("profile_id", "year"))

# replace NAs
prof_year_pubs_citations_grants <- prof_year_pubs_citations_grants %>%
  mutate_at(vars(veni:erc_total), ~replace_na(., 0))

# fix the cumulatives
prof_year_pubs_citations_grants <- prof_year_pubs_citations_grants %>%
  arrange(profile_id, year)%>%
  group_by(profile_id)%>%
  mutate(nwo_total = cumsum(any_nwo),
         erc_total = cumsum(any_erc))
```

Write this out:
```{r}
write_csv(prof_year_pubs_citations_grants, "panel_datasets/prof_year_pubs_citations_grants.csv")
```

```{r}
gc()
rm(erc_grants)
rm(erc_cumulative)
rm(nwo_cumulative)
rm(nwo_grants)
```

# Altmetric attention

Get all the attention measures we have per paper:
```{r}
attention_news <- dbReadTable(con, "altmetric_pub_att_news")
attention_blogs <- dbReadTable(con, "altmetric_pub_att_blogs")

# merge the papers with their authors
attention_news_profs <- merge(attention_news,
                        oa_prof_pub_matching[c("id", "profile_id")],
                        by = "id")

# merge the papers with their authors
attention_blogs_profs <- merge(attention_blogs,
                        oa_prof_pub_matching[c("id", "profile_id")],
                        by = "id")
```

Compile the two attention sources together:
```{r}
attention_news_profs <- attention_news_profs[c("id", "title", "url", "license", "posted_on", 
                                               "summary", "author_name", "author_url", "profile_id")]

attention_blogs_profs <- attention_blogs_profs[c("id", "title", "url", "license", "posted_on", 
                                               "summary", "author_name", "author_url", "profile_id")]

attention_news_blogs_profs <- rbind(attention_news_profs,
                                    attention_blogs_profs)
```

Load in news mentions with full text ("response" not an error, but 200 for success)
and match to professors, seeking if their last name is mentioned here:
```{r}
attention_news_full <- dbGetQuery(con, "select * from pub_att_news_full_text where \"response\"='200'")

attention_news_full_match <- merge(attention_news_full,
                                   attention_news_blogs_profs[c("url", "profile_id", "id")],
                                   by = c("url"))

# merge this with professor last names
attention_news_full_match <- merge(attention_news_full_match,
                                   narcis_prof_info[c("profile_id", "last", "first")],
                                   by = "profile_id")

# remove the duplicates
attention_news_full_match$dupl <- duplicated(attention_news_full_match[c("url", "id", "profile_id")])

attention_news_full_match <- attention_news_full_match %>%
  filter(dupl == FALSE)%>%
  select(-dupl)

attention_news_full_match$first_last <- paste(attention_news_full_match$first, attention_news_full_match$last)
```

Get the language of each mention:
```{r}
attention_news_lang <- rep(NA, nrow(attention_news_full_match))

for (i in 1:nrow(attention_news_full_match)){
  content <- attention_news_full_match$content[i]
  
  if (!is.na(content)){
    
    #now, identify the language based on the first 300 characters of the content,
    #or, if shorter, the whole string
    if (nchar(content)>300){
      language <- fastText::language_identification(input_obj = substr(content, 1, 300),
                                                    pre_trained_language_model_path = "resources/lid.176.ftz",
                                                    k = 1,
                                                    th = 0.0,
                                                    verbose = FALSE)
      language <- as.character(language$iso_lang_1)
      
    }else{
      language <- fastText::language_identification(input_obj = content,
                                                    pre_trained_language_model_path = "resources/lid.176.ftz",
                                                    k = 1,
                                                    th = 0.0,
                                                    verbose = FALSE)
      language <- as.charact
      er(language$iso_lang_1)
    }
    attention_news_lang[i] <- language
  }
    
 print(i)   
}
    
```

Seek professor last name mentions in the full texts of news articles:
```{r}
attention_news_full_match$last_name_mention <- str_detect(tolower(attention_news_full_match$content), paste0("\\b", attention_news_full_match$last, "\\b"))

attention_news_full_match$first_last_mention <- str_detect(tolower(attention_news_full_match$content), paste0("\\b", attention_news_full_match$first_last, "\\b"))

keyword_list_1 <- c("hoogleraar", "universitair docent", "universitair hoofddocent", "assistant professor", "associate professor",
                  "onderzoeker", "researcher", "universiteitshoogleraar", "professor")

keyword_list_1 <- paste(paste0("\\b", keyword_list_1, "\\b"), collapse ="|")

keyword_list_final <- paste(keyword_list_1, paste(c("^\\bwetenschap", "^\\bscien",  "^\\buniversit",
                                                    "\\bdr\\.", "\\bprof\\."), collapse = "|"), collapse = "|")

attention_news_full_match$keyword <- str_detect(tolower(attention_news_full_match$content), keyword_list_final)

# both name and keyword!
attention_news_full_match$first_last_key <- ifelse(attention_news_full_match$first_last_mention == TRUE & 
                                                     attention_news_full_match$keyword == TRUE,
                                                   TRUE,
                                                   FALSE)

```

Merge the name mentions with the rest of the data:
```{r}
attention_news_blogs_profs_names <- merge(attention_news_blogs_profs,
                                          attention_news_full_match[c("profile_id", "url", "id", 
                                                                      "last_name_mention", "first_last_mention")],
                                          by = c("profile_id","url", "id"),
                                          all.x = TRUE)
```

Classify news attention:
```{r}
# load the classification objects
source("resources/altmetric_news_outlet_classification.R")

attention_news_blogs_profs_names$source_type <- NA

attention_news_blogs_profs_names$source_type <- ifelse(attention_news_blogs_profs_names$author_name %in% att_news_aggregator,
                                                 "news_aggregator",
                                                 attention_news_blogs_profs_names$source_type)

attention_news_blogs_profs_names$source_type <- ifelse(attention_news_blogs_profs_names$author_name %in% att_news_sci_aggregator,
                                                 "sci_news_aggregator",
                                                 attention_news_blogs_profs_names$source_type)

attention_news_blogs_profs_names$source_type <- ifelse(attention_news_blogs_profs_names$author_name %in% att_news_finance,
                                                 "finance_news",
                                                 attention_news_blogs_profs_names$source_type)

attention_news_blogs_profs_names$source_type <- ifelse(attention_news_blogs_profs_names$author_name %in% att_news_general,
                                                 "general_interest_news",
                                                 attention_news_blogs_profs_names$source_type)

attention_news_blogs_profs_names$source_type <- ifelse(attention_news_blogs_profs_names$author_name %in% att_news_general_local,
                                                 "general_interest_local_news",
                                                 attention_news_blogs_profs_names$source_type)

attention_news_blogs_profs_names$source_type <- ifelse(attention_news_blogs_profs_names$author_name %in% att_news_medical,
                                                 "medical_news",
                                                 attention_news_blogs_profs_names$source_type)

attention_news_blogs_profs_names$source_type <- ifelse(attention_news_blogs_profs_names$author_name %in% att_news_pop_sci,
                                                 "popsci_news",
                                                 attention_news_blogs_profs_names$source_type)

attention_news_blogs_profs_names$source_type <- ifelse(attention_news_blogs_profs_names$author_name %in% att_news_sci_portal,
                                                 "science_news",
                                                 attention_news_blogs_profs_names$source_type)

# if nothing yet, check for blogs
blog_names <- unique(attention_blogs$author_name)

attention_news_blogs_profs_names$source_type <- ifelse((is.na(attention_news_blogs_profs_names$source_type) & attention_news_blogs_profs_names$author_name %in% blog_names),
                                                 "online_blog",
                                                 attention_news_blogs_profs_names$source_type)

# if nothing yet, set as other
attention_news_blogs_profs_names$source_type <- ifelse(is.na(attention_news_blogs_profs_names$source_type),
                                                 "other_news",
                                                 attention_news_blogs_profs_names$source_type)

```

Write this out into the database:
```{r}
dbWriteTable(con, "altmetric_att_prepared", attention_news_blogs_profs_names)
```


Compile the attention per professor per year:
```{r}
# get a year from the "posted on" string
attention_news_blogs_profs_names$year <- year(as_date(attention_news_blogs_profs_names$posted_on))

prof_year_attention_online <- attention_news_blogs_profs_names %>%
  filter(year >= 2011 & year <= 2023)%>%
  group_by(profile_id, source_type, year)%>%
  summarise(alt_attn = n())%>%
  arrange(profile_id, source_type, year)%>%
  pivot_wider(names_from = source_type, values_from = c(alt_attn))%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year)

colnames(prof_year_attention_online)[-c(1:2)] <- paste0("alt_", colnames(prof_year_attention_online)[-c(1:2)])
```

Do the same, but deduplicating multiple paper mentions in single news articles:
```{r}
prof_year_attention_online_dedupe <- attention_news_blogs_profs_names %>%
  filter(year >= 2011 & year <= 2023)%>%
  distinct(profile_id, url, title, posted_on, author_name,.keep_all = TRUE)%>%
  group_by(profile_id, source_type, year)%>%
  summarise(alt_attn = n())%>%
  arrange(profile_id, source_type, year)%>%
  pivot_wider(names_from = source_type, values_from = c(alt_attn))%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year)

colnames(prof_year_attention_online_dedupe)[-c(1:2)] <- paste0("alt_ded_", colnames(prof_year_attention_online_dedupe)[-c(1:2)])

# rearrange to match the column order of the other dataframe above
prof_year_attention_online_dedupe <- prof_year_attention_online_dedupe[c("profile_id", "year", "alt_ded_news_aggregator", "alt_ded_online_blog", "alt_ded_sci_news_aggregator" , "alt_ded_finance_news" , "alt_ded_general_interest_local_news", "alt_ded_general_interest_news", "alt_ded_medical_news", "alt_ded_other_news", "alt_ded_popsci_news", "alt_ded_science_news")]
```

Do the same only for those where we have names last included:
```{r}
prof_year_attention_online_names <- attention_news_blogs_profs_names %>%
  filter(year >= 2011 & year <= 2023 & last_name_mention == TRUE)%>%
  group_by(profile_id, source_type, year)%>%
  summarise(alt_attn = n())%>%
  arrange(profile_id, source_type, year)%>%
  pivot_wider(names_from = source_type, values_from = c(alt_attn))%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year)

colnames(prof_year_attention_online_names)[-c(1:2)] <- paste0("alt_name_", colnames(prof_year_attention_online_names)[-c(1:2)])

# rearrange to match the column order of the other dataframe above
prof_year_attention_online_names <- prof_year_attention_online_names[c("profile_id", "year", "alt_name_news_aggregator", "alt_name_online_blog", "alt_name_sci_news_aggregator" , "alt_name_finance_news" , "alt_name_general_interest_local_news", "alt_name_general_interest_news", "alt_name_medical_news", "alt_name_other_news", "alt_name_popsci_news", "alt_name_science_news")]
```

And for the full name included:
```{r}
prof_year_attention_online_full_names <- attention_news_blogs_profs_names %>%
  filter(year >= 2011 & year <= 2023 & first_last_mention == TRUE)%>%
  group_by(profile_id, source_type, year)%>%
  summarise(alt_attn = n())%>%
  arrange(profile_id, source_type, year)%>%
  pivot_wider(names_from = source_type, values_from = c(alt_attn))%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year)

colnames(prof_year_attention_online_full_names)[-c(1:2)] <- paste0("alt_fname_", colnames(prof_year_attention_online_full_names)[-c(1:2)])

# rearrange to match the column order of the other dataframe above
prof_year_attention_online_full_names <- prof_year_attention_online_full_names[c("profile_id", "year", "alt_fname_news_aggregator", "alt_fname_online_blog", "alt_fname_sci_news_aggregator" , "alt_fname_finance_news" , "alt_fname_general_interest_local_news", "alt_fname_general_interest_news", "alt_fname_medical_news", "alt_fname_other_news", "alt_fname_popsci_news", "alt_fname_science_news")]
```

And now only for single-authored papers:
```{r}
prof_year_attention_online_single_au <- attention_news_blogs_profs_names %>%
  filter(year >= 2011 & year <= 2023 & id %in% oa_prof_pubs_unique_single_au$id)%>%
  distinct(profile_id, url, title, posted_on, author_name,.keep_all = TRUE)%>%
  group_by(profile_id, source_type, year)%>%
  summarise(alt_attn = n())%>%
  arrange(profile_id, source_type, year)%>%
  pivot_wider(names_from = source_type, values_from = c(alt_attn))%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year)

colnames(prof_year_attention_online_single_au)[-c(1:2)] <- paste0("alt_single_", colnames(prof_year_attention_online_single_au)[-c(1:2)])

prof_year_attention_online_single_au <- prof_year_attention_online_single_au[c("profile_id", "year", "alt_single_news_aggregator", "alt_single_online_blog", "alt_single_sci_news_aggregator" , "alt_single_finance_news" , "alt_single_general_interest_local_news", "alt_single_general_interest_news", "alt_single_medical_news", "alt_single_other_news", "alt_single_popsci_news", "alt_single_science_news")]
```

And for dutch mentions only:
```{r}
prof_year_attention_online_dutch <- attention_news_blogs_profs_names %>%
  filter(year >= 2011 & year <= 2023 & lang == "nl")%>%
  distinct(profile_id, url, title, posted_on, author_name,.keep_all = TRUE)%>%
  group_by(profile_id, source_type, year)%>%
  summarise(alt_attn = n())%>%
  arrange(profile_id, source_type, year)%>%
  pivot_wider(names_from = source_type, values_from = c(alt_attn))%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year)

colnames(prof_year_attention_online_dutch)[-c(1:2)] <- paste0("alt_dutch_", colnames(prof_year_attention_online_dutch)[-c(1:2)])

prof_year_attention_online_dutch$alt_dutch_general_interest_local_news <- 0

prof_year_attention_online_dutch <- prof_year_attention_online_dutch[c("profile_id", "year", "alt_dutch_news_aggregator", "alt_dutch_online_blog", "alt_dutch_sci_news_aggregator" , "alt_dutch_finance_news" , "alt_dutch_general_interest_local_news", "alt_dutch_general_interest_news", "alt_dutch_medical_news", "alt_dutch_other_news", "alt_dutch_popsci_news", "alt_dutch_science_news")]
```


Merge the attention with the rest: 
```{r}
prof_year_p_c_g_a <- merge(prof_year_pubs_citations_grants,
                           prof_year_attention_online,
                           by = c("profile_id", "year"),
                           all.x = TRUE)

prof_year_p_c_g_a <- merge(prof_year_p_c_g_a,
                           prof_year_attention_online_dedupe,
                           by = c("profile_id", "year"),
                           all.x = TRUE)

prof_year_p_c_g_a <- merge(prof_year_p_c_g_a,
                           prof_year_attention_online_single_au,
                           by = c("profile_id", "year"),
                           all.x = TRUE)


prof_year_p_c_g_a <- merge(prof_year_p_c_g_a,
                           prof_year_attention_online_names,
                           by = c("profile_id", "year"),
                           all.x = TRUE)

prof_year_p_c_g_a <- merge(prof_year_p_c_g_a,
                           prof_year_attention_online_full_names,
                           by = c("profile_id", "year"),
                           all.x = TRUE)

prof_year_p_c_g_a <- merge(prof_year_p_c_g_a,
                           prof_year_attention_online_dutch,
                           by = c("profile_id", "year"),
                           all.x = TRUE)


# get the cumulatives
# As Altmetric data goes back to 2011 in principle, set attention to 0 if year >= 2011, leave as NA
# otherwise:
prof_year_p_c_g_a <- prof_year_p_c_g_a %>%
  arrange(profile_id, year)%>%
  mutate_at(vars(contains('alt_')), ~ifelse(is.na(.), 0, .))%>%
  group_by(profile_id)%>%
  mutate(across(alt_news_aggregator:alt_dutch_science_news, ~cumsum(.x), .names = "{col}_total"))%>%
  mutate_at(vars(contains('alt_')), ~ifelse(. == 0 & year < 2011, NA, .))
```

Combine this with Twitter attention, which we only obtain using ORCIDs (for now).
```{r}
twitter_orcid_attention <- dbGetQuery(con, statement = "select * from altmetric_prof_attention where \"mention_type\"='tweet'")

# rename the columns and get cumulatives
twitter_orcid_attention <- twitter_orcid_attention %>%
  select(profile_id, year, yearly_count)

colnames(twitter_orcid_attention)[which(colnames(twitter_orcid_attention) == "yearly_count")] <- "alt_twitter"


prof_year_p_c_g_a <- merge(prof_year_p_c_g_a,
                           twitter_orcid_attention,
                           by = c("profile_id", "year"),
                           all.x = TRUE)

prof_year_p_c_g_a <- prof_year_p_c_g_a %>%
  arrange(profile_id, year)%>%
  mutate_at(vars(contains('twitter')), ~ifelse(is.na(.), 0, .))%>%
  group_by(profile_id)%>%
  mutate(across(alt_twitter, ~cumsum(.x), .names = "{col}_total"))%>%
  mutate_at(vars(contains('twitter')), ~ifelse(. == 0 & year < 2011, NA, .))
```

Get total altmetrics as well as totals of "general interest" outlets:
```{r}
prof_year_p_c_g_a$alt_online_all <- rowSums(prof_year_p_c_g_a[,c("alt_news_aggregator",
                                                                 "alt_online_blog",
                                                                 "alt_sci_news_aggregator",
                                                                 "alt_finance_news",
                                                                 "alt_general_interest_local_news",
                                                                 "alt_general_interest_news",            
                                                                 "alt_medical_news",
                                                                 "alt_other_news",
                                                                 "alt_popsci_news",
                                                                 "alt_science_news")])

prof_year_p_c_g_a$alt_online_ded_all <- rowSums(prof_year_p_c_g_a[,c("alt_ded_news_aggregator",
                                                                     "alt_ded_online_blog",
                                                                     "alt_ded_sci_news_aggregator",
                                                                     "alt_ded_finance_news",
                                                                     "alt_ded_general_interest_local_news",
                                                                     "alt_ded_general_interest_news",            
                                                                     "alt_ded_medical_news",
                                                                     "alt_ded_other_news",
                                                                     "alt_ded_popsci_news",
                                                                     "alt_ded_science_news")])

prof_year_p_c_g_a$alt_online_name_all <- rowSums(prof_year_p_c_g_a[,c("alt_name_news_aggregator",
                                                                      "alt_name_online_blog",
                                                                      "alt_name_sci_news_aggregator",
                                                                      "alt_name_finance_news",
                                                                      "alt_name_general_interest_local_news",
                                                                      "alt_name_general_interest_news",            
                                                                      "alt_name_medical_news",
                                                                      "alt_name_other_news",
                                                                      "alt_name_popsci_news",
                                                                      "alt_name_science_news")])

prof_year_p_c_g_a$alt_online_fname_all <- rowSums(prof_year_p_c_g_a[,c("alt_fname_news_aggregator",
                                                                       "alt_fname_online_blog",
                                                                       "alt_fname_sci_news_aggregator",
                                                                       "alt_fname_finance_news",
                                                                       "alt_fname_general_interest_local_news",
                                                                       "alt_fname_general_interest_news",            
                                                                       "alt_fname_medical_news",
                                                                       "alt_fname_other_news",
                                                                       "alt_fname_popsci_news",
                                                                       "alt_fname_science_news")])

prof_year_p_c_g_a$alt_online_single_all <- rowSums(prof_year_p_c_g_a[,c("alt_single_news_aggregator",
                                                                        "alt_single_online_blog",
                                                                        "alt_single_sci_news_aggregator",
                                                                        "alt_single_finance_news",
                                                                        "alt_single_general_interest_local_news",
                                                                        "alt_single_general_interest_news",            
                                                                        "alt_single_medical_news",
                                                                        "alt_single_other_news",
                                                                        "alt_single_popsci_news",
                                                                        "alt_single_science_news")])

prof_year_p_c_g_a$alt_online_dutch_all <- rowSums(prof_year_p_c_g_a[,c("alt_dutch_news_aggregator",
                                                                        "alt_dutch_online_blog",
                                                                        "alt_dutch_sci_news_aggregator",
                                                                        "alt_dutch_finance_news",
                                                                        "alt_dutch_general_interest_local_news",
                                                                        "alt_dutch_general_interest_news",            
                                                                        "alt_dutch_medical_news",
                                                                        "alt_dutch_other_news",
                                                                        "alt_dutch_popsci_news",
                                                                        "alt_dutch_science_news")])

prof_year_p_c_g_a$alt_online_all_total <- rowSums(prof_year_p_c_g_a[,c("alt_news_aggregator_total",
                                                                       "alt_online_blog_total",
                                                                       "alt_sci_news_aggregator_total",
                                                                       "alt_finance_news_total",
                                                                       "alt_general_interest_local_news_total",
                                                                       "alt_general_interest_news_total",            
                                                                       "alt_medical_news_total",
                                                                       "alt_other_news_total",
                                                                       "alt_popsci_news_total",
                                                                       "alt_science_news_total")])

prof_year_p_c_g_a$alt_online_ded_all_total <- rowSums(prof_year_p_c_g_a[,c("alt_ded_news_aggregator_total",
                                                                           "alt_ded_online_blog_total",
                                                                           "alt_ded_sci_news_aggregator_total",
                                                                           "alt_ded_finance_news_total",
                                                                           "alt_ded_general_interest_local_news_total",
                                                                           "alt_ded_general_interest_news_total",            
                                                                           "alt_ded_medical_news_total",
                                                                           "alt_ded_other_news_total",
                                                                           "alt_ded_popsci_news_total",
                                                                           "alt_ded_science_news_total")])

prof_year_p_c_g_a$alt_online_name_all_total <- rowSums(prof_year_p_c_g_a[,c("alt_name_news_aggregator_total",
                                                                            "alt_name_online_blog_total",
                                                                            "alt_name_sci_news_aggregator_total",
                                                                            "alt_name_finance_news_total",
                                                                            "alt_name_general_interest_local_news_total",
                                                                            "alt_name_general_interest_news_total",            
                                                                            "alt_name_medical_news_total",
                                                                            "alt_name_other_news_total",
                                                                            "alt_name_popsci_news_total",
                                                                            "alt_name_science_news_total")])

prof_year_p_c_g_a$alt_online_fname_all_total <- rowSums(prof_year_p_c_g_a[,c("alt_fname_news_aggregator_total",
                                                                             "alt_fname_online_blog_total",
                                                                             "alt_fname_sci_news_aggregator_total",
                                                                             "alt_fname_finance_news_total",
                                                                             "alt_fname_general_interest_local_news_total",
                                                                             "alt_fname_general_interest_news_total",            
                                                                             "alt_fname_medical_news_total",
                                                                             "alt_fname_other_news_total",
                                                                             "alt_fname_popsci_news_total",
                                                                             "alt_fname_science_news_total")])

prof_year_p_c_g_a$alt_online_single_all_total <- rowSums(prof_year_p_c_g_a[,c("alt_single_news_aggregator_total",
                                                                              "alt_single_online_blog_total",
                                                                              "alt_single_sci_news_aggregator_total",
                                                                              "alt_single_finance_news_total",
                                                                              "alt_single_general_interest_local_news_total",
                                                                              "alt_single_general_interest_news_total",            
                                                                              "alt_single_medical_news_total",
                                                                              "alt_single_other_news_total",
                                                                              "alt_single_popsci_news_total",
                                                                              "alt_single_science_news_total")])

prof_year_p_c_g_a$alt_online_dutch_all_total <- rowSums(prof_year_p_c_g_a[,c("alt_dutch_news_aggregator_total",
                                                                              "alt_dutch_online_blog_total",
                                                                              "alt_dutch_sci_news_aggregator_total",
                                                                              "alt_dutch_finance_news_total",
                                                                              "alt_dutch_general_interest_local_news_total",
                                                                              "alt_dutch_general_interest_news_total",            
                                                                              "alt_dutch_medical_news_total",
                                                                              "alt_dutch_other_news_total",
                                                                              "alt_dutch_popsci_news_total",
                                                                              "alt_dutch_science_news_total")])


prof_year_p_c_g_a$alt_online_general_all <- rowSums(prof_year_p_c_g_a[,c(
  "alt_finance_news",
  "alt_general_interest_local_news",
  "alt_general_interest_news",  
  "alt_popsci_news")])

prof_year_p_c_g_a$alt_online_general_ded_all <- rowSums(prof_year_p_c_g_a[,c(
  "alt_ded_finance_news",
  "alt_ded_general_interest_local_news",
  "alt_ded_general_interest_news",       
  "alt_ded_popsci_news")])

prof_year_p_c_g_a$alt_online_general_name_all <- rowSums(prof_year_p_c_g_a[,c(
  "alt_name_finance_news",
  "alt_name_general_interest_local_news",
  "alt_name_general_interest_news",       
  "alt_name_popsci_news")])

prof_year_p_c_g_a$alt_online_general_fname_all <- rowSums(prof_year_p_c_g_a[,c(
  "alt_fname_finance_news",
  "alt_fname_general_interest_local_news",
  "alt_fname_general_interest_news",       
  "alt_fname_popsci_news")])

prof_year_p_c_g_a$alt_online_general_single_all <- rowSums(prof_year_p_c_g_a[,c(
  "alt_single_finance_news",
  "alt_single_general_interest_local_news",
  "alt_single_general_interest_news",       
  "alt_single_popsci_news")])

prof_year_p_c_g_a$alt_online_general_dutch_all <- rowSums(prof_year_p_c_g_a[,c(
  "alt_dutch_finance_news",
  "alt_dutch_general_interest_local_news",
  "alt_dutch_general_interest_news",       
  "alt_dutch_popsci_news")])

prof_year_p_c_g_a$alt_online_general_all_total <- rowSums(prof_year_p_c_g_a[,c(
  "alt_finance_news_total",
  "alt_general_interest_local_news_total",
  "alt_general_interest_news_total",            
  "alt_popsci_news_total")])

prof_year_p_c_g_a$alt_online_general_ded_all_total <- rowSums(prof_year_p_c_g_a[,c(
  "alt_ded_finance_news_total",
  "alt_ded_general_interest_local_news_total",
  "alt_ded_general_interest_news_total",  
  "alt_ded_popsci_news_total")])

prof_year_p_c_g_a$alt_online_general_name_all_total <- rowSums(prof_year_p_c_g_a[,c(
  "alt_name_finance_news_total",
  "alt_name_general_interest_local_news_total",
  "alt_name_general_interest_news_total",  
  "alt_name_popsci_news_total")])


prof_year_p_c_g_a$alt_online_general_fname_all_total <- rowSums(prof_year_p_c_g_a[,c(
  "alt_fname_finance_news_total",
  "alt_fname_general_interest_local_news_total",
  "alt_fname_general_interest_news_total",  
  "alt_fname_popsci_news_total")])

prof_year_p_c_g_a$alt_online_general_single_all_total <- rowSums(prof_year_p_c_g_a[,c(
  "alt_single_finance_news_total",
  "alt_single_general_interest_local_news_total",
  "alt_single_general_interest_news_total",  
  "alt_single_popsci_news_total")])

prof_year_p_c_g_a$alt_online_general_dutch_all_total <- rowSums(prof_year_p_c_g_a[,c(
  "alt_dutch_finance_news_total",
  "alt_dutch_general_interest_local_news_total",
  "alt_dutch_general_interest_news_total",  
  "alt_dutch_popsci_news_total")])
```

Write this out:
```{r}
write_csv(prof_year_p_c_g_a, "panel_datasets/prof_year_pubs_citations_grants_alt.csv")
```


Clear the memory, remove some redundant objects:
```{r}
rm(twitter_orcid_attention)
rm(attention_blogs)
rm(attention_blogs_profs)
rm(attention_news)
rm(attention_news_blogs_profs)
rm(attention_news_blogs_profs_names)
rm(latest_citation)
gc()
```


# Printed news attention

Load the LexisNexis articles:
```{r}
lexis_data <- dbReadTable(con, "lexis_nexis_mentions")
```

Now, aggregate professor mentions per year and per source, wherever relevant:
```{r}
# combine sources for easier handling:
prof_news_year <- lexis_data %>%
  filter(!is.na(year) & year >= 1973 & year <= 2023)%>%
  arrange(profile_id, year)%>%
  group_by(profile_id, year, source_type)%>%
  summarise(n = n())%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year, source_type)%>%
  group_by(profile_id, source_type)%>%
  mutate(cumsum = cumsum(n))%>%
  pivot_wider(names_from = source_type, values_from = c(n, cumsum))%>%
  fill(cumsum_national_nl:cumsum_high_prof_intl)%>%
  replace(is.na(.), 0)

prof_news_year <- prof_news_year[c("profile_id", "year", "n_national_nl", 
                                   "n_news_aggr", "n_finance", "n_other", 
                                   "n_regional_nl", "n_science", "n_prof", 
                                   "n_local_int", "n_unknown", "n_high_prof_intl",
                                   "n_other_int", "n_blog", "cumsum_national_nl", 
                                   "cumsum_news_aggr", "cumsum_finance", "cumsum_other", 
                                   "cumsum_regional_nl", "cumsum_science", "cumsum_prof", 
                                   "cumsum_local_int", "cumsum_unknown", "cumsum_high_prof_intl",
                                   "cumsum_other_int", "cumsum_blog" )]

# tidy up the columns
colnames(prof_news_year)[3:26] <- c("news_national", "news_aggr", "news_finance",
                                    "news_other", "news_regional", "news_science",
                                    "news_professional", "news_local_intl", "news_unknown",
                                    "news_intl", "news_intl_other", "news_blog",
                                    "news_national_total", "news_aggr_total", "news_finance_total",
                                    "news_other_total", "news_regional_total", "news_science_total",
                                    "news_professional_total", "news_local_intl_total", "news_unknown_total",
                                    "news_intl_total", "news_intl_other_total", "news_blog_total")

# add total counts
prof_news_year$news_all <- rowSums(prof_news_year[3:14])
prof_news_year$news_all_total <- rowSums(prof_news_year[15:26])
   
# add general interest counts
prof_news_year$news_general_all <- rowSums(prof_news_year[c("news_national", "news_regional", "news_intl",
                                                            "news_local_intl", "news_intl_other")])

prof_news_year$news_general_all_total <- rowSums(prof_news_year[c("news_national_total", "news_regional_total", "news_intl_total",
                                                            "news_local_intl_total", "news_intl_other_total")])
   
# rearrange a bit
prof_news_year <- prof_news_year %>%
  select(profile_id, year, news_national, news_regional, news_intl, news_local_intl,
         news_intl_other, news_general_all, news_finance, news_professional, news_science, news_blog,
         news_aggr, news_unknown, news_other, news_all,
         news_national_total, news_regional_total, 
         news_intl_total, news_local_intl_total, news_intl_other_total, news_general_all_total, 
         news_finance_total, news_professional_total, news_science_total, news_blog_total,
         news_aggr_total, news_unknown_total, news_other_total, news_all_total)
```

Deduplicated regional news:
```{r}
# combine sources for easier handling:
prof_news_year_ded <- lexis_data %>%
  filter(!is.na(year) & year >= 1973 & year <= 2023 & regional_duplicate == FALSE)%>%
  arrange(profile_id, year)%>%
  group_by(profile_id, year, source_type)%>%
  summarise(n = n())%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year, source_type)%>%
  group_by(profile_id, source_type)%>%
  mutate(cumsum = cumsum(n))%>%
  pivot_wider(names_from = source_type, values_from = c(n, cumsum))%>%
  fill(cumsum_national_nl:cumsum_high_prof_intl)%>%
  replace(is.na(.), 0)

prof_news_year_ded <- prof_news_year_ded[c("profile_id", "year", "n_national_nl", 
                                           "n_news_aggr", "n_finance", "n_other", 
                                           "n_regional_nl", "n_science", "n_prof", 
                                           "n_local_int", "n_unknown", "n_high_prof_intl",
                                           "n_other_int", "n_blog", "cumsum_national_nl", 
                                           "cumsum_news_aggr", "cumsum_finance", "cumsum_other", 
                                           "cumsum_regional_nl", "cumsum_science", "cumsum_prof", 
                                           "cumsum_local_int", "cumsum_unknown", "cumsum_high_prof_intl",
                                           "cumsum_other_int", "cumsum_blog" )]

# tidy up the columns
colnames(prof_news_year_ded)[3:26] <- c("news_ded_national", "news_ded_aggr", "news_ded_finance",
                                    "news_ded_other", "news_ded_regional", "news_ded_science",
                                    "news_ded_professional", "news_ded_local_intl", "news_ded_unknown",
                                    "news_ded_intl", "news_ded_intl_other", "news_ded_blog",
                                    "news_ded_national_total", "news_ded_aggr_total", "news_ded_finance_total",
                                    "news_ded_other_total", "news_ded_regional_total", "news_ded_science_total",
                                    "news_ded_professional_total", "news_ded_local_intl_total", "news_ded_unknown_total",
                                    "news_ded_intl_total", "news_ded_intl_other_total", "news_ded_blog_total")

# add total counts
prof_news_year_ded$news_ded_all <- rowSums(prof_news_year_ded[3:14])
prof_news_year_ded$news_ded_all_total <- rowSums(prof_news_year_ded[15:26])
   
# add general interest counts
prof_news_year_ded$news_ded_general_all <- rowSums(prof_news_year_ded[c("news_ded_national", "news_ded_regional", "news_ded_intl",
                                                            "news_ded_local_intl", "news_ded_intl_other")])
                                                   
prof_news_year_ded$news_ded_general_all_total <- rowSums(prof_news_year_ded[c("news_ded_national_total", "news_ded_regional_total",
                                                                              "news_ded_intl_total", "news_ded_local_intl_total",
                                                                              "news_ded_intl_other_total")])
   
# rearrange a bit
prof_news_year_ded <- prof_news_year_ded %>%
  select(profile_id, year, news_ded_regional, news_ded_general_all, news_ded_all,
         news_ded_regional_total, news_ded_general_all_total, news_ded_all_total)
```

Do the same, but excluding online resources:
```{r}
prof_news_year_offline <- lexis_data %>%
  filter(!is.na(year) & year >= 1973 & year <= 2023 & online_resource == FALSE)%>%
  arrange(profile_id, year)%>%
  group_by(profile_id, year, source_type)%>%
  summarise(n = n())%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year, source_type)%>%
  group_by(profile_id, source_type)%>%
  mutate(cumsum = cumsum(n))%>%
  pivot_wider(names_from = source_type, values_from = c(n, cumsum))%>%
  fill(cumsum_national_nl:cumsum_high_prof_intl)%>%
  replace(is.na(.), 0)

prof_news_year_offline <- prof_news_year_offline[c("profile_id", "year", "n_national_nl", 
                                                   "n_news_aggr", "n_finance", "n_other", 
                                                   "n_regional_nl", "n_science", "n_prof", 
                                                   "n_local_int", "n_unknown", "n_high_prof_intl",
                                                   "n_other_int", "n_blog", "cumsum_national_nl", 
                                                   "cumsum_news_aggr", "cumsum_finance", "cumsum_other", 
                                                   "cumsum_regional_nl", "cumsum_science", "cumsum_prof", 
                                                   "cumsum_local_int", "cumsum_unknown", "cumsum_high_prof_intl",
                                                   "cumsum_other_int", "cumsum_blog" )]

# tidy up the columns
colnames(prof_news_year_offline)[3:26] <- c("news_off_national", "news_off_aggr", "news_off_finance",
                                            "news_off_other", "news_off_regional", "news_off_science",
                                            "news_off_professional", "news_off_local_intl", "news_off_unknown",
                                            "news_off_intl", "news_off_intl_other", "news_off_blog",
                                            "news_off_national_total", "news_off_aggr_total", "news_off_finance_total",
                                            "news_off_other_total", "news_off_regional_total", "news_off_science_total",
                                            "news_off_professional_total", "news_off_local_intl_total", "news_off_unknown_total",
                                            "news_off_intl_total", "news_off_intl_other_total", "news_off_blog_total")
  
# add total counts
prof_news_year_offline$news_off_all <- rowSums(prof_news_year_offline[3:14])
prof_news_year_offline$news_off_all_total <- rowSums(prof_news_year_offline[15:26])
   
# add general interest counts
prof_news_year_offline$news_off_general_all <- rowSums(prof_news_year_offline[c("news_off_national", "news_off_regional", "news_off_intl",
                                                            "news_off_local_intl", "news_off_intl_other")])
prof_news_year_offline$news_off_general_all_total <- rowSums(prof_news_year_offline[c("news_off_national_total", 
                                                                                      "news_off_regional_total",
                                                                                      "news_off_intl_total", 
                                                                                      "news_off_local_intl_total",
                                                                                      "news_off_intl_other_total")])
   
# rearrange a bit
prof_news_year_offline <- prof_news_year_offline %>%
  select(profile_id, year, news_off_national, news_off_regional, news_off_intl, news_off_local_intl,
         news_off_intl_other, news_off_general_all, news_off_finance, news_off_professional, news_off_science, news_off_blog,
         news_off_aggr, news_off_unknown, news_off_other, news_off_all,
         news_off_national_total, news_off_regional_total, 
         news_off_intl_total, news_off_local_intl_total, news_off_intl_other_total, news_off_general_all_total, 
         news_off_finance_total, news_off_professional_total, news_off_science_total, news_off_blog_total,
         news_off_aggr_total, news_off_unknown_total, news_off_other_total, news_off_all_total)
```

Now cover only resources with institutional affiliation mentioned:
```{r}
prof_news_year_inst <- lexis_data %>%
  filter(!is.na(year) & year >= 1973 & year <= 2023 & affiliation == TRUE)%>%
  arrange(profile_id, year)%>%
  group_by(profile_id, year, source_type)%>%
  summarise(n = n())%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year, source_type)%>%
  group_by(profile_id, source_type)%>%
  mutate(cumsum = cumsum(n))%>%
  pivot_wider(names_from = source_type, values_from = c(n, cumsum))%>%
  fill(cumsum_national_nl:cumsum_high_prof_intl)%>%
  replace(is.na(.), 0)

prof_news_year_inst <- prof_news_year_inst[c("profile_id", "year", "n_national_nl", 
                                             "n_news_aggr", "n_finance", "n_other", 
                                             "n_regional_nl", "n_science", "n_prof", 
                                             "n_local_int", "n_unknown", "n_high_prof_intl",
                                             "n_other_int", "n_blog", "cumsum_national_nl", 
                                             "cumsum_news_aggr", "cumsum_finance", "cumsum_other", 
                                             "cumsum_regional_nl", "cumsum_science", "cumsum_prof", 
                                             "cumsum_local_int", "cumsum_unknown", "cumsum_high_prof_intl",
                                             "cumsum_other_int", "cumsum_blog" )]

# tidy up the columns
colnames(prof_news_year_inst)[3:26] <- c("news_inst_national", "news_inst_aggr", "news_inst_finance",
                                            "news_inst_other", "news_inst_regional", "news_inst_science",
                                            "news_inst_professional", "news_inst_local_intl", "news_inst_unknown",
                                            "news_inst_intl", "news_inst_intl_other", "news_inst_blog",
                                            "news_inst_national_total", "news_inst_aggr_total", "news_inst_finance_total",
                                            "news_inst_other_total", "news_inst_regional_total", "news_inst_science_total",
                                            "news_inst_professional_total", "news_inst_local_intl_total", "news_inst_unknown_total",
                                            "news_inst_intl_total", "news_inst_intl_other_total", "news_inst_blog_total")
  
# add total counts
prof_news_year_inst$news_inst_all <- rowSums(prof_news_year_inst[3:14])
prof_news_year_inst$news_inst_all_total <- rowSums(prof_news_year_inst[15:26])
   
# add general interest counts
prof_news_year_inst$news_inst_general_all <- rowSums(prof_news_year_inst[c("news_inst_national", "news_inst_regional", "news_inst_intl",
                                                            "news_inst_local_intl", "news_inst_intl_other")])

prof_news_year_inst$news_inst_general_all_total <- rowSums(prof_news_year_inst[c("news_inst_national_total", 
                                                                                      "news_inst_regional_total",
                                                                                      "news_inst_intl_total", 
                                                                                      "news_inst_local_intl_total",
                                                                                      "news_inst_intl_other_total")])
   
# rearrange a bit
prof_news_year_inst <- prof_news_year_inst %>%
  select(profile_id, year, news_inst_national, news_inst_regional, news_inst_intl, news_inst_local_intl,
         news_inst_intl_other, news_inst_general_all, news_inst_finance, news_inst_professional, news_inst_science, news_inst_blog,
         news_inst_aggr, news_inst_unknown, news_inst_other, news_inst_all,
         news_inst_national_total, news_inst_regional_total, 
         news_inst_intl_total, news_inst_local_intl_total, news_inst_intl_other_total, news_inst_general_all_total, 
         news_inst_finance_total, news_inst_professional_total, news_inst_science_total, news_inst_blog_total,
         news_inst_aggr_total, news_inst_unknown_total, news_inst_other_total, news_inst_all_total)
```

And deduplicated:
```{r}
prof_news_year_inst_ded <- lexis_data %>%
  filter(!is.na(year) & year >= 1973 & year <= 2023 & affiliation == TRUE & regional_duplicate == FALSE)%>%
  arrange(profile_id, year, source_type)%>%
  group_by(profile_id, year, source_type)%>%
  summarise(n = n())%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year, source_type)%>%
  group_by(profile_id, source_type)%>%
  mutate(cumsum = cumsum(n))%>%
  pivot_wider(names_from = source_type, values_from = c(n, cumsum))%>%
  fill(cumsum_national_nl:cumsum_high_prof_intl)%>%
  replace(is.na(.), 0)

prof_news_year_inst_ded <- prof_news_year_inst_ded[c("profile_id", "year", "n_national_nl", 
                                                     "n_news_aggr", "n_finance", "n_other", 
                                                     "n_regional_nl", "n_science", "n_prof", 
                                                     "n_local_int", "n_unknown", "n_high_prof_intl",
                                                     "n_other_int", "n_blog", "cumsum_national_nl", 
                                                     "cumsum_news_aggr", "cumsum_finance", "cumsum_other", 
                                                     "cumsum_regional_nl", "cumsum_science", "cumsum_prof", 
                                                     "cumsum_local_int", "cumsum_unknown", "cumsum_high_prof_intl",
                                                     "cumsum_other_int", "cumsum_blog" )]

# tidy up the columns
colnames(prof_news_year_inst_ded)[3:26] <- c("news_ded_inst_national", "news_ded_inst_aggr", "news_ded_inst_finance",
                                            "news_ded_inst_other", "news_ded_inst_regional", "news_ded_inst_science",
                                            "news_ded_inst_professional", "news_ded_inst_local_intl", "news_ded_inst_unknown",
                                            "news_ded_inst_intl", "news_ded_inst_intl_other", "news_ded_inst_blog",
                                            "news_ded_inst_national_total", "news_ded_inst_aggr_total", "news_ded_inst_finance_total",
                                            "news_ded_inst_other_total", "news_ded_inst_regional_total", "news_ded_inst_science_total",
                                            "news_ded_inst_professional_total", "news_ded_inst_local_intl_total", "news_ded_inst_unknown_total",
                                            "news_ded_inst_intl_total", "news_ded_inst_intl_other_total", "news_ded_inst_blog_total")
  
# add total counts
prof_news_year_inst_ded$news_ded_inst_all <- rowSums(prof_news_year_inst_ded[3:14])
prof_news_year_inst_ded$news_ded_inst_all_total <- rowSums(prof_news_year_inst_ded[15:26])
   
# add general interest counts
prof_news_year_inst_ded$news_ded_inst_general_all <- rowSums(prof_news_year_inst_ded[c("news_ded_inst_national", "news_ded_inst_regional", "news_ded_inst_intl",
                                                            "news_ded_inst_local_intl", "news_ded_inst_intl_other")])

prof_news_year_inst_ded$news_ded_inst_general_all_total <- rowSums(prof_news_year_inst_ded[c("news_ded_inst_national_total", 
                                                                                      "news_ded_inst_regional_total",
                                                                                      "news_ded_inst_intl_total", 
                                                                                      "news_ded_inst_local_intl_total",
                                                                                      "news_ded_inst_intl_other_total")])
   
# rearrange a bit
prof_news_year_inst_ded <- prof_news_year_inst_ded %>%
  select(profile_id, year, news_ded_inst_national, news_ded_inst_regional, news_ded_inst_intl, news_ded_inst_local_intl,
         news_ded_inst_intl_other, news_ded_inst_general_all, news_ded_inst_finance, news_ded_inst_professional, news_ded_inst_science, news_ded_inst_blog,
         news_ded_inst_aggr, news_ded_inst_unknown, news_ded_inst_other, news_ded_inst_all,
         news_ded_inst_national_total, news_ded_inst_regional_total, 
         news_ded_inst_intl_total, news_ded_inst_local_intl_total, news_ded_inst_intl_other_total, news_ded_inst_general_all_total, 
         news_ded_inst_finance_total, news_ded_inst_professional_total, news_ded_inst_science_total, news_ded_inst_blog_total,
         news_ded_inst_aggr_total, news_ded_inst_unknown_total, news_ded_inst_other_total, news_ded_inst_all_total)
```

Finally, deduplicated resources with strict name criteria inlcuded:
```{r}
lexis_data_strict <- dbReadTable(con, "lexis_nexis_mentions_strict_criterion")

prof_news_year_strict <- lexis_data_strict %>%
  filter(!is.na(year) & year >= 1973 & year <= 2023 & strict_criteria == TRUE)%>%
  arrange(profile_id, year, source_type)%>%
  group_by(profile_id, year, source_type)%>%
  summarise(n = n())%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, year, source_type)%>%
  group_by(profile_id, source_type)%>%
  mutate(cumsum = cumsum(n))%>%
  pivot_wider(names_from = source_type, values_from = c(n, cumsum))%>%
  fill(cumsum_national_nl:cumsum_high_prof_intl)%>%
  replace(is.na(.), 0)

prof_news_year_strict <- prof_news_year_strict[c("profile_id", "year", "n_national_nl", 
                                                 "n_news_aggr", "n_finance", "n_other", 
                                                 "n_regional_nl", "n_science", "n_prof", 
                                                 "n_local_int", "n_unknown", "n_high_prof_intl",
                                                 "n_other_int", "n_blog", "cumsum_national_nl", 
                                                 "cumsum_news_aggr", "cumsum_finance", "cumsum_other", 
                                                 "cumsum_regional_nl", "cumsum_science", "cumsum_prof", 
                                                 "cumsum_local_int", "cumsum_unknown", "cumsum_high_prof_intl",
                                                 "cumsum_other_int", "cumsum_blog" )]

# tidy up the columns
colnames(prof_news_year_strict)[3:26] <- c("news_strict_national", "news_strict_aggr", "news_strict_finance",
                                            "news_strict_other", "news_strict_regional", "news_strict_science",
                                            "news_strict_professional", "news_strict_local_intl", "news_strict_unknown",
                                            "news_strict_intl", "news_strict_intl_other", "news_strict_blog",
                                            "news_strict_national_total", "news_strict_aggr_total", "news_strict_finance_total",
                                            "news_strict_other_total", "news_strict_regional_total", "news_strict_science_total",
                                            "news_strict_professional_total", "news_strict_local_intl_total", "news_strict_unknown_total",
                                            "news_strict_intl_total", "news_strict_intl_other_total", "news_strict_blog_total")
  
# add total counts
prof_news_year_strict$news_strict_all <- rowSums(prof_news_year_strict[3:14])
prof_news_year_strict$news_strict_all_total <- rowSums(prof_news_year_strict[15:26])
   
# add general interest counts
prof_news_year_strict$news_strict_general_all <- rowSums(prof_news_year_strict[c("news_strict_national", "news_strict_regional", "news_strict_intl",
                                                            "news_strict_local_intl", "news_strict_intl_other")])

prof_news_year_strict$news_strict_general_all_total <- rowSums(prof_news_year_strict[c("news_strict_national_total", 
                                                                                      "news_strict_regional_total",
                                                                                      "news_strict_intl_total", 
                                                                                      "news_strict_local_intl_total",
                                                                                      "news_strict_intl_other_total")])
   
# rearrange a bit
prof_news_year_strict <- prof_news_year_strict %>%
  select(profile_id, year, news_strict_national, news_strict_regional, news_strict_intl, news_strict_local_intl,
         news_strict_intl_other, news_strict_general_all, news_strict_finance, news_strict_professional, news_strict_science, news_strict_blog,
         news_strict_aggr, news_strict_unknown, news_strict_other, news_strict_all,
         news_strict_national_total, news_strict_regional_total, 
         news_strict_intl_total, news_strict_local_intl_total, news_strict_intl_other_total, news_strict_general_all_total, 
         news_strict_finance_total, news_strict_professional_total, news_strict_science_total, news_strict_blog_total,
         news_strict_aggr_total, news_strict_unknown_total, news_strict_other_total, news_strict_all_total)
```


Merge the lexis sub-data-frames:
```{r}
prof_news_year <- merge(prof_news_year,
                        prof_news_year_ded,
                        all.x = TRUE,
                        all.y = TRUE,
                        by = c("profile_id", "year"))

prof_news_year <- merge(prof_news_year,
                        prof_news_year_offline,
                        all.x = TRUE,
                        all.y = TRUE,
                        by = c("profile_id", "year"))

prof_news_year <- merge(prof_news_year,
                        prof_news_year_inst,
                        all.x = TRUE,
                        all.y = TRUE,
                        by = c("profile_id", "year"))

prof_news_year <- merge(prof_news_year,
                        prof_news_year_inst_ded,
                        all.x = TRUE,
                        all.y = TRUE,
                        by = c("profile_id", "year"))

prof_news_year <- merge(prof_news_year,
                        prof_news_year_strict,
                        all.x = TRUE,
                        all.y = TRUE,
                        by = c("profile_id", "year"))
```

Pad lexis data with the professor panel:
```{r}
# get all observations in the panel
prof_lexis_year_pad <- merge(prof_news_year,
                             prof_year_p_c_g_a[c("profile_id", "year")],
                             all.y= TRUE,
                             all.x = TRUE)

# fill down on totals and replace NAs with zeroes
prof_lexis_year_pad <- prof_lexis_year_pad %>%
  group_by(profile_id)%>%
  fill(news_national_total, news_regional_total,
       news_intl_total,news_local_intl_total, news_intl_other_total,
       news_general_all_total, news_finance_total, news_professional_total,
       news_science_total, news_blog_total,news_aggr_total,
       news_unknown_total, news_other_total, news_all_total,
       news_ded_regional_total, news_ded_general_all_total, news_ded_all_total,
       news_off_national_total, news_off_regional_total, news_off_intl_total, 
       news_off_local_intl_total,
       news_off_intl_other_total, news_off_general_all_total, news_off_finance_total,
       news_off_professional_total, news_off_science_total, news_off_blog_total,
       news_off_aggr_total, news_off_unknown_total, news_off_other_total,
       news_off_all_total, 
       news_inst_national_total, news_inst_regional_total, news_inst_intl_total,
       news_inst_local_intl_total, news_inst_intl_other_total, news_inst_general_all_total,
       news_inst_finance_total, news_inst_professional_total, news_inst_science_total,
       news_inst_blog_total, news_inst_aggr_total, news_inst_unknown_total,
       news_inst_other_total, news_inst_all_total,
       news_ded_inst_national_total, news_ded_inst_regional_total,
       news_ded_inst_intl_total, news_ded_inst_local_intl_total, news_ded_inst_intl_other_total,
       news_ded_inst_general_all_total, news_ded_inst_finance_total, news_ded_inst_professional_total,
       news_ded_inst_science_total, news_ded_inst_blog_total, news_ded_inst_aggr_total,
       news_ded_inst_unknown_total, news_ded_inst_other_total, news_ded_inst_all_total, 
       news_strict_national_total, news_strict_regional_total,
       news_strict_intl_total, news_strict_local_intl_total, news_strict_intl_other_total,
       news_strict_general_all_total, news_strict_finance_total, news_strict_professional_total,
       news_strict_science_total, news_strict_blog_total, news_strict_aggr_total,
       news_strict_unknown_total, news_strict_other_total, news_strict_all_total, 
       .direction = "down")%>%
  mutate(across(contains('news'), replace_na, 0))
```

If excluded professors, set to NAs:
```{r}
exclude_profs <- c() # redacted for privacy

prof_lexis_year_pad[which(prof_lexis_year_pad$profile_id %in% paste0("https://www.narcis.nl/person/RecordID/",exclude_profs)),3:148] <- NA
```


Combine our professor panel with lexis data:
```{r}
prof_year_p_c_g_a_l <- merge(prof_year_p_c_g_a,
                             prof_lexis_year_pad,
                             by = c("profile_id", "year"),
                             all.x = TRUE)
```

Write this out:
```{r}
write_csv(prof_year_p_c_g_a_l, "panel_datasets/prof_year_pubs_citations_grants_alt_lexis.csv")
```

```{r}
rm(lexis_data)
rm(lexis_data_filt)
rm(lexis_data_filt_ded)
rm(prof_news_year)
rm(prof_news_year_ded)
rm(prof_news_year_inst)
rm(prof_news_year_inst_ded)
rm(prof_lexis_year_pad)
gc()
```


# Field classification

Get each professor's main field in a given year based on their papers, and get 
their overall specialization.

First, fetching the topics: 
```{r}
oa_pubs_topics <- dbReadTable(con, "oa_pubs_topics")

oa_pubs_topics <- merge(oa_prof_pub_matching,
                        oa_pubs_topics,
                        by = "id",
                        all.x = TRUE)
 
oa_pubs_topics <- merge(oa_pubs_topics,
                        oa_pubs_unique[c("id", "publication_year")],
                        by = "id")

# leave the domain as is, unless it's arts and humanities
oa_pubs_topics$scopus_domain_adj <- ifelse(oa_pubs_topics$field_display_name == "Arts and Humanities",
                                           "Arts and Humanities",
                                           oa_pubs_topics$domain_display_name)
```

Professor's topic diversity per year and in total:
```{r}
oa_pubs_topics$field_display_name <- as.factor(oa_pubs_topics$field_display_name)

# per year
prof_year_field <- oa_pubs_topics %>%
  group_by(profile_id, field_display_name, publication_year) %>%
  summarise(count = n())%>%
  filter(!is.na(field_display_name))%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, field_display_name, publication_year)%>%
  group_by(profile_id, field_display_name) %>%
  pivot_wider(names_from = field_display_name, values_from = count)%>%
  replace(is.na(.), 0)
  
  
diversity_year <- diversity(prof_year_field[, -c(1:2)], index = "shannon")

prof_year_field_div <- cbind.data.frame(prof_year_field[, c(1:2)],
                                        yearly_diversity = diversity_year)

prof_year_field_div$yearly_field_evennes <- prof_year_field_div$yearly_diversity/log(26)

colnames(prof_year_field_div)[2] <- "year"

# in total
prof_total_field <- oa_pubs_topics %>%
  group_by(profile_id, field_display_name) %>%
  summarise(count = n())%>%
  filter(!is.na(field_display_name))%>%
  replace(is.na(.), 0)%>%
  arrange(profile_id, field_display_name)%>%
  pivot_wider(names_from = field_display_name, values_from = c(count))%>%
  replace(is.na(.), 0)
  
  
diversity_total <- diversity(prof_total_field[, -c(1)], index = "shannon")


prof_field_div <- cbind.data.frame(prof_total_field[, c(1)],
                                        total_diversity = diversity_total)

prof_field_div$total_field_evennes <- prof_field_div$total_diversity/log(26)

```

Merge this with our data:
```{r}
prof_year_p_c_g_a_l_f <- merge(prof_year_p_c_g_a_l,
                             prof_year_field_div,
                             by = c("profile_id", "year"),
                             all.x = TRUE,
                             all.y = FALSE) 

prof_year_p_c_g_a_l_f <- merge(prof_year_p_c_g_a_l_f,
                             prof_field_div,
                             by = c("profile_id"),
                             all.x = TRUE,
                             all.y = FALSE) 
```

Fields and subfields per prof per year and in total
```{r}
# per year field
prof_year_field <- oa_pubs_topics %>%
  group_by(profile_id, publication_year, field_display_name) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_year_field)[c(2,3)] <- c("year","yearly_field" )

# per year subfield
prof_year_subfield <- oa_pubs_topics %>%
  group_by(profile_id, publication_year, subfield_display_name) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_year_subfield)[c(2,3)] <- c("year","yearly_subfield") 

# per year adjusted
prof_year_domain <- oa_pubs_topics %>%
  group_by(profile_id, publication_year, scopus_domain_adj) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_year_domain)[c(2,3)] <- c("year", "yearly_adj_domain") 


# overall 
prof_total_subfield <- oa_pubs_topics %>%
  group_by(profile_id, subfield_display_name) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_total_subfield)[2] <- c("overall_subfield" )

prof_total_field <- oa_pubs_topics %>%
  group_by(profile_id, field_display_name) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_total_field)[2] <- c("overall_field" )

# overal adjusted
prof_total_domain <- oa_pubs_topics %>%
  group_by(profile_id, scopus_domain_adj) %>%
  summarise(n = n())%>%
  slice_max(n, with_ties = FALSE)%>%
  select(-n)

colnames(prof_total_domain)[2] <- c("overall_adj_domain") 


# merge profs and their fields
prof_year_p_c_g_a_l_f <- merge(prof_year_p_c_g_a_l_f,
                             prof_year_field[c("profile_id", "yearly_field", "year")],
                             by = c("profile_id", "year"),
                             all.x = TRUE,
                             all.y = FALSE) 

prof_year_p_c_g_a_l_f <- merge(prof_year_p_c_g_a_l_f,
                             prof_year_subfield[c("profile_id", "yearly_subfield", "year")],
                             by = c("profile_id", "year"),
                             all.x = TRUE,
                             all.y = FALSE) 

prof_year_p_c_g_a_l_f <- merge(prof_year_p_c_g_a_l_f,
                             prof_year_domain[c("profile_id", "yearly_adj_domain", "year")],
                             by = c("profile_id", "year"),
                             all.x = TRUE,
                             all.y = FALSE) 

prof_year_p_c_g_a_l_f <- merge(prof_year_p_c_g_a_l_f,
                             prof_total_field[c("profile_id", "overall_field")],
                             by = c("profile_id"),
                             all.x = TRUE,
                             all.y = FALSE) 

prof_year_p_c_g_a_l_f <- merge(prof_year_p_c_g_a_l_f,
                             prof_total_subfield[c("profile_id", "overall_subfield")],
                             by = c("profile_id"),
                             all.x = TRUE,
                             all.y = FALSE) 

prof_year_p_c_g_a_l_f <- merge(prof_year_p_c_g_a_l_f,
                             prof_total_domain[c("profile_id", "overall_adj_domain")],
                             by = c("profile_id"),
                             all.x = TRUE,
                             all.y = FALSE) 
```

Remove duplicates, if any:
```{r}
prof_year_p_c_g_a_l_f$dupl <- duplicated(prof_year_p_c_g_a_l_f[c("profile_id", "year")])

prof_year_p_c_g_a_l_f <- prof_year_p_c_g_a_l_f %>%
  filter(dupl == FALSE)%>%
  select(-dupl)

# fill
prof_year_p_c_g_a_l_f <- prof_year_p_c_g_a_l_f %>%
  group_by(profile_id)%>%
  fill(yearly_field, yearly_subfield, yearly_adj_domain,  .direction = "down")
```

Write this out:
```{r}
write_csv(prof_year_p_c_g_a_l_f, "panel_datasets/prof_year_pubs_citations_grants_alt_lexis_field.csv")
```

Remove some redundant objects:
```{r}
rm(oa_pubs_topics)
gc()
```

# Institution dummies

Load yearly institution data. Then, find the most frequent institutional
affiliation for each prof for each year.

```{r}
# load the institution data
institution_yearly_data <- dbReadTable(con, "oa_prof_yearly_affiliations")
# merge back to NARCIS IDs
oa_ids <- dbReadTable(con, "oa_id_mapping")
institution_yearly_data <- merge(institution_yearly_data,
                                 oa_ids[c("profile_id", "oa_id")],
                                 by.x = "au_id",
                                 by.y = "oa_id")

```

Now, recode the institutions capture University units and UMCs associated to all the Dutch universities, binning
other institutions (also including e.g., Hogeshools, governmental institutes, and foreign institutions as "Other").
```{r}
# we manually extract the relevant university units from the OpenAlex dataset
uva_string <- c("University of Amsterdam",
                "Amsterdam University Medical Centers",
                "Amsterdam Neuroscience",
                "Amsterdam University of the Arts",
                "Academic Center for Dentistry Amsterdam",
                "Cancer Center Amsterdam")

vu_string <- c("Vrije Universiteit Amsterdam",
               "Amsterdam UMC Location VUmc")

rug_string <- c("University of Groningen",
                "University Medical Center Groningen",
                "Dialyse Centrum Groningen")

leiden_string <- c("Leiden University",
                   "Leiden University Medical Center",
                   "Leiden Observatory")

maastrict_string <- c("Maastricht University",
                      "Maastricht University Medical Centre",
                      "Maastricht School of Management",
                      "Clinical Trial Center Maastricht")

ru_string <- c("Radboud University Nijmegen",
               "Radboud University Medical Center",
               "Radboud Institute for Molecular Life Sciences")


eu_string <- c("Erasmus University Rotterdam",
               "Erasmus MC",
               "Erasmus MC Cancer Institute",
               "Erasmus MC - Sophia Childrens Hospital",
               "Erasmus Optical Imaging Centre")

tilburg_string <- c("Tilburg University")

uu_string <- c("Utrecht University",
              "University Medical Center Utrecht")

delft_string <- c("Delft University of Technology")

eindhoven_string <- c("Eindhoven University of Technology")

twente_string <- c("University of Twente")

wageningen_string <- c("Wageningen University & Research")

institution_yearly_data$dutch_uni_var <- ifelse(
  institution_yearly_data$display_name %in% uva_string,
  "uni_1",
  ifelse(
    institution_yearly_data$display_name %in% vu_string,
    "uni_2",
    ifelse(
      institution_yearly_data$display_name %in% rug_string,
      "uni_3",
      ifelse(
        institution_yearly_data$display_name %in% leiden_string,
        "uni_4",
        ifelse(
          institution_yearly_data$display_name %in% maastrict_string,
          "uni_5",
          ifelse(
            institution_yearly_data$display_name %in% ru_string,
            "uni_6",
            ifelse(
              institution_yearly_data$display_name %in% eu_string,
              "uni_7",
              ifelse(
                institution_yearly_data$display_name %in% tilburg_string,
                "uni_8",
                ifelse(
                  institution_yearly_data$display_name %in% uu_string,
                  "uni_9",
                  ifelse(
                    institution_yearly_data$display_name %in% delft_string,
                    "uni_10",
                    ifelse(
                      institution_yearly_data$display_name %in% eindhoven_string,
                      "uni_11",
                      ifelse(
                        institution_yearly_data$display_name %in% twente_string,
                        "uni_12",
                        ifelse(
                          institution_yearly_data$display_name %in% wageningen_string,
                          "uni_13",
                              "other")))))))))))))

# now, encode the diplay names of institutions to protect professors' anonymity in the final set
# generate new ID mapping
unique_id <- unique(institution_yearly_data$id)
new_ids <- paste("inst", c(1:length(unique_id)), sep= "_")

new_id_mapping <- data.frame(id = unique_id,
                             inst_id = new_ids)

dbWriteTable(con, "anonymous_institution_id_mapping", new_id_mapping, row.names=FALSE, append=TRUE)

# combine the panel with the new ID mapping
institution_yearly_data <- merge(institution_yearly_data,
                                 new_id_mapping,
                                 by = "id",
                                 all.x = TRUE)

```

Get the model institution in general, and also between 2012 and 2023, which is our
focus period:
```{r}
modal_institution <- institution_yearly_data %>%
  group_by(profile_id, years)%>%
  summarise(institution_id_yearly = collapse::fmode(inst_id),
            institution_dutch_yearly = collapse::fmode(dutch_uni_var))

colnames(modal_institution)[2] <- "year"

modal_institution_2012 <- institution_yearly_data %>%
  filter(years >= 2012)%>%
  group_by(profile_id, years)%>%
  summarise(institution_id_yearly_since2012 = collapse::fmode(inst_id),
            institution_dutch_yearly_since2012 = collapse::fmode(dutch_uni_var))

colnames(modal_institution_2012)[2] <- "year"
```
Prepare the following as well: make sure that if a dutch university affiliaton makes up at least an equal part of affiliations
in a year to denote that year's affiliation as the dutch university affiliation.

```{r}
profile_ids <- unique(prof_year_p_c_g_a_l_f$profile_id)

institution_yearly_data$inst_id_dutch <- ifelse(institution_yearly_data$dutch_uni_var != "other",
                                                institution_yearly_data$dutch_uni_var,
                                                institution_yearly_data$inst_id)

prof_affiliations_yearly_dutch <- data.frame(matrix(NA, ncol = 0, nrow = 0))

for (prof in profile_ids){
  
  # get this professor's affiliations
  prof_affiliations <- institution_yearly_data %>%
    filter(profile_id == prof)%>%
    group_by(years, inst_id_dutch)%>%
    summarise(n = n()) %>%
    mutate(freq = n / sum(n))
  
  if(nrow(prof_affiliations) > 0){
  
  # get yearly totals
  prof_yearly <- institution_yearly_data %>%
    filter(profile_id == prof)%>%
    group_by(years)%>%
    summarise(yearly_total = n())
  
  # merge
  prof_affiliations <- merge(prof_affiliations,
                             prof_yearly,
                             by = "years")
  
  # determine the minimal share for equal share of a dutch institution
  prof_affiliations$ideal_share <- 1/prof_affiliations$yearly_total
  
  # mark all dutch universities as one
  prof_affiliations$dutch_uni_main <- ifelse(prof_affiliations$freq == prof_affiliations$ideal_share & str_detect(prof_affiliations$inst_id_dutch, "uni"), "yes", "no")
  
  # now filter out only the dutch university affiliations
  prof_affiliations_dutch <- prof_affiliations %>%
    filter(dutch_uni_main == "yes")%>%
    select(years, inst_id_dutch)
  
  if (nrow(prof_affiliations_dutch) > 0){
  
  prof_affiliations_dutch$profile_id <- prof
  prof_affiliations_dutch$institution_id_yearly <- prof_affiliations_dutch$inst_id_dutch
  
  colnames(prof_affiliations_dutch)[2] <- c("institution_dutch_yearly")
  }

  # for years without dutch affiliation, get the modal one
  prof_affiliations_nondutch <- institution_yearly_data %>%
    filter(profile_id == prof & !years %in% prof_affiliations_dutch$years)%>%
    group_by(profile_id, years)%>%
    summarise(institution_id_yearly = collapse::fmode(inst_id),
              institution_dutch_yearly = collapse::fmode(dutch_uni_var))
  
  if (nrow(prof_affiliations_dutch) > 0){
    prof_affiliations_dutch <- prof_affiliations_dutch[colnames(prof_affiliations_nondutch)]
  }
  
  if (nrow(prof_affiliations_dutch) > 0 & nrow(prof_affiliations_nondutch) > 0 ){
  
  prof_affliations_yearly_all <- rbind(prof_affiliations_dutch,
                                       prof_affiliations_nondutch)
  }
  if (nrow(prof_affiliations_dutch) > 0 & nrow(prof_affiliations_nondutch) == 0 ){
  
  prof_affliations_yearly_all <- prof_affiliations_dutch
  }
  
  if (nrow(prof_affiliations_dutch) == 0 & nrow(prof_affiliations_nondutch) > 0 ){
  
  prof_affliations_yearly_all <- prof_affiliations_nondutch
  }
  
  
  prof_affliations_yearly_all <- prof_affliations_yearly_all %>% 
    arrange(profile_id, years)%>%
    distinct(years, institution_dutch_yearly, .keep_all = TRUE)
  
  colnames(prof_affliations_yearly_all)[2] <- "year"
  
  prof_affiliations_yearly_dutch <- rbind(prof_affiliations_yearly_dutch,
                                          prof_affliations_yearly_all)
  }
  
  print(which(profile_ids == prof))
}

colnames(prof_affiliations_yearly_dutch)[4] <- "institution_dutch_yearly_strict"
```

Deduplicate this:
```{r}
 prof_affiliations_yearly_dutch_dedupe <- prof_affiliations_yearly_dutch %>% 
  distinct(profile_id, year, .keep_all = TRUE)
```


Merge with the panel:
```{r}
prof_year_p_c_g_a_l_f_i <- merge(prof_year_p_c_g_a_l_f,
                                 modal_institution,
                                 by = c("profile_id", "year"),
                                 all.x = TRUE)

prof_year_p_c_g_a_l_f_i <- merge(prof_year_p_c_g_a_l_f_i,
                                 modal_institution_2012,
                                 by = c("profile_id", "year"),
                                 all.x = TRUE)

prof_year_p_c_g_a_l_f_i <- merge(prof_year_p_c_g_a_l_f_i,
                                 prof_affiliations_yearly_dutch_dedupe[c("profile_id", "year", "institution_dutch_yearly_strict")],
                                 by = c("profile_id", "year"),
                                 all.x = TRUE)
```

For years where we can't obtain this information from publication data,
we use the last known institutional affiliation:
```{r}
prof_year_p_c_g_a_l_f_i <- prof_year_p_c_g_a_l_f_i %>%
  arrange(profile_id, year)%>%
  group_by(profile_id)%>%
  fill(institution_id_yearly, institution_dutch_yearly, institution_id_yearly_since2012, institution_dutch_yearly_since2012, institution_dutch_yearly_strict, .direction = "down")
```

Now get their career-wide affiliations:
```{r}
modal_institution_total <- institution_yearly_data %>%
  group_by(profile_id)%>%
  summarise(institution_id_total = collapse::fmode(inst_id),
            institution_dutch_total = collapse::fmode(dutch_uni_var))


modal_institution_total_2012 <- institution_yearly_data %>%
  filter(years >= 2012)%>%
  group_by(profile_id)%>%
  summarise(institution_id_total_since2012 = collapse::fmode(inst_id),
            institution_dutch_total_since2012 = collapse::fmode(dutch_uni_var))

```

Merge with the panel:
```{r}
prof_year_p_c_g_a_l_f_i <- merge(prof_year_p_c_g_a_l_f_i,
                                 modal_institution_total,
                                 by = c("profile_id"),
                                 all.x = TRUE)

prof_year_p_c_g_a_l_f_i <- merge(prof_year_p_c_g_a_l_f_i,
                                 modal_institution_total_2012,
                                 by = c("profile_id"),
                                 all.x = TRUE)
```

OpenAlex info might not always be accurate. Fetch the NARCIS affiliation information:
```{r}
narcis_institution <- dbReadTable(con, "narcis_institution")

colnames(narcis_institution)[2] <- "institution_dutch_total_narcis"

prof_year_p_c_g_a_l_f_i <- merge(prof_year_p_c_g_a_l_f_i,
                                      narcis_institution,
                                      by = "profile_id")
```


Write this out:
```{r}
write_csv(prof_year_p_c_g_a_l_f_i, "panel_datasets/prof_year_pubs_citations_grants_alt_lexis_field_institution.csv")
```

Remove some redundant objects:
```{r}
rm(institution_yearly_data)
gc()
```

# First, last authorship

Extracting information on professors' authorship on each paper:
```{r}
oa_prof_pubs_authorship <- oa_prof_pubs %>%
  distinct(id, .keep_all = TRUE)%>%
  select(id, publication_year, author_position, type)

# merge with professor data
oa_prof_pubs_authorship <- merge(oa_prof_pubs_authorship,
                                 oa_prof_pub_matching,
                                 all.x = TRUE,
                                 all.y = TRUE,
                                 by = "id")

```

Check number of coauthors for each paper:
```{r}
coauthor_info_paper <- coauthor_info  %>%
  group_by(id)%>%
  summarise(n = n())
```

Merge the professor's authorship info with the total number of authors for each paper:
```{r}
oa_prof_pubs_authorship_coa <- merge(oa_prof_pubs_authorship,
                                     coauthor_info_paper,
                                     by = "id",
                                     all.x = TRUE)

# determine single authorship
oa_prof_pubs_authorship_coa$author_position <- ifelse(is.na(oa_prof_pubs_authorship_coa$n), 
                                                      "single",
                                                      oa_prof_pubs_authorship_coa$author_position)

# replace NAs in n with ones
oa_prof_pubs_authorship_coa$n <- ifelse(is.na(oa_prof_pubs_authorship_coa$n),
                                        1, 
                                        oa_prof_pubs_authorship_coa$n)
```



Get yearly counts for different authorship positions:
```{r}
yearly_authorship <- oa_prof_pubs_authorship_coa %>%
    filter(!is.na(publication_year) & publication_year >= 1973 & publication_year <= 2023 & 
           type %in% c("article", "book", "book-chapter"))%>%
  group_by(profile_id, publication_year) %>%
  summarise(n_pubs_first_au = sum(author_position == "first"),
            n_pubs_last_au = sum(author_position == "last"),
            n_pubs_single_au = sum(author_position == "single"),
            n_pubs_all_au = n(),
            n_pubs_total_authorships = sum(n))

colnames(yearly_authorship)[2] <- "year"
```
Merge with the panel:
```{r}
prof_year_p_c_g_a_l_f_i_a <- merge(prof_year_p_c_g_a_l_f_i,
                                 yearly_authorship,
                                 by = c("profile_id", "year"),
                                 all.x = TRUE)

# replace with zeroes where appropriate

prof_year_p_c_g_a_l_f_i_a <- prof_year_p_c_g_a_l_f_i_a%>% 
  mutate(n_pubs_first_au  =  ifelse(count_pubs == 0, 0 , n_pubs_first_au),
         n_pubs_last_au  =  ifelse(count_pubs == 0, 0 , n_pubs_last_au),
         n_pubs_single_au  =  ifelse(count_pubs == 0, 0 , n_pubs_single_au),
         n_pubs_all_au  =  ifelse(count_pubs == 0, 0 , n_pubs_all_au),
         n_pubs_total_authorships  =  ifelse(count_pubs == 0, 0 , n_pubs_total_authorships),
  )

# make some new variables

prof_year_p_c_g_a_l_f_i_a$n_pubs_first_last_single_au <- prof_year_p_c_g_a_l_f_i_a$n_pubs_first_au + prof_year_p_c_g_a_l_f_i_a$n_pubs_last_au + prof_year_p_c_g_a_l_f_i_a$n_pubs_single_au

prof_year_p_c_g_a_l_f_i_a$n_pubs_first_single_au <- prof_year_p_c_g_a_l_f_i_a$n_pubs_first_au + prof_year_p_c_g_a_l_f_i_a$n_pubs_single_au

prof_year_p_c_g_a_l_f_i_a$n_pubs_last_single_au <- prof_year_p_c_g_a_l_f_i_a$n_pubs_last_au + prof_year_p_c_g_a_l_f_i_a$n_pubs_single_au
```


Write this out:
```{r}
write_csv(prof_year_p_c_g_a_l_f_i_a, "panel_datasets/prof_year_pubs_citations_grants_alt_lexis_field_institution_authorship.csv")
```

# Get some remaining totals

Get totals for some remaining variables
```{r}
prof_year_p_c_g_a_l_f_i_a <- prof_year_p_c_g_a_l_f_i_a %>%
  group_by(profile_id)%>%
  arrange(year)%>%
  mutate(sum_sjr_total = cumsum(replace_na(sum_sjr, 0)),
         sum_hindex_total = cumsum(replace_na(sum_sjr, 0)),
         count_q1_total = cumsum(replace_na(count_q1, 0)),
         count_scimago_indicators_total = cumsum(replace_na(count_scimago_indicators, 0)),
         n_pubs_first_au_total = cumsum(n_pubs_first_au),
         n_pubs_last_au_total = cumsum(n_pubs_last_au),
         n_pubs_single_au_total = cumsum(n_pubs_single_au),
         n_pubs_all_au_total = cumsum(n_pubs_all_au),
         n_pubs_total_authorships_total = cumsum(n_pubs_total_authorships),
         n_pubs_first_last_single_au_total = cumsum(n_pubs_first_last_single_au) 
  )%>%
  arrange(profile_id, year)%>%
  ungroup()%>%
  mutate(sum_sjr_total  =  ifelse(year < 1999, NA , sum_sjr_total),
         sum_hindex_total  =  ifelse(year < 1999, NA , sum_hindex_total),
         count_q1_total  =  ifelse(year < 1999, NA , count_q1_total),
         count_scimago_indicators_total = ifelse(year < 1999, NA, count_scimago_indicators_total))

```


# Lagged variables

New data frame for lagging:
```{r}
prof_year_p_c_g_a_l_f_i_a_l <- prof_year_p_c_g_a_l_f_i_a
colnames(prof_year_p_c_g_a_l_f_i_a_l)[-c(1:2)] <- paste0(colnames(prof_year_p_c_g_a_l_f_i_a_l)[-c(1:2)], "_l")
```

Lag the relevant variables:
```{r}
prof_year_p_c_g_a_l_f_i_a_l <- prof_year_p_c_g_a_l_f_i_a_l %>%
  arrange(year) %>%
  group_by(profile_id) %>%
  mutate_at(vars(contains('_l')), lag)%>%
  arrange(profile_id, year)
```

Merge with the non-lagged panel:
```{r}
prof_year_p_c_g_a_l_f_i_a_l <- merge(prof_year_p_c_g_a_l_f_i_a,
                                     prof_year_p_c_g_a_l_f_i_a_l,
                                     by = c("profile_id", "year"))
```

Write this out:
```{r}
write_csv(prof_year_p_c_g_a_l_f_i_a_l, "panel_datasets/prof_year_pubs_citations_grants_alt_lexis_field_institution_authorship_lag.csv")
```


# Coauthor data

Fetch all coauthor data, including full info, their inferred gender, and citation counts.
```{r}
oa_coauthor_info <- dbReadTable(con, "oa_coauthor_info")
oa_coauthor_info_name <- dbReadTable(con, "oa_coauthor_name_list")
coauthor_gender <- dbReadTable(con, "coauthor_name_gender")
# add professor gender names, as these are specific for the 
# Dutch context and might help further
prof_gender_names <- dbReadTable(con, "gender_table")%>%
  distinct(first, .keep_all = TRUE)%>%
  select(first, inferred_gender)
oa_coauthor_info_full <- dbReadTable(con, "oa_coauthor_info_full")
```

Match name gender inference with coauthor names:
```{r}
colnames(coauthor_gender)[2] <- "first"
coauthor_gender <- coauthor_gender %>%
  filter(first != "")%>%
  select(first, gender)

# recode the variable
coauthor_gender$gender <- ifelse(coauthor_gender$gender == "male", "m",
                                 ifelse(coauthor_gender$gender == "female", "w", coauthor_gender$gender))

colnames(prof_gender_names)[2] <- "gender"

# combine
all_names <- rbind(coauthor_gender,
                   prof_gender_names)%>%
  distinct(first, .keep_all = TRUE)


# filter out "and" which seems to just be a mistake
oa_coauthor_info_name <- oa_coauthor_info_name %>%
  filter(! tolower(first) %in% c("van", "and", "den"))

oa_coauthor_info_name$first <- tolower(oa_coauthor_info_name$first)

coauthor_name_gender <- merge(oa_coauthor_info_name,
                              all_names,
                              by = "first",
                              all.x = TRUE,
                              all.y = FALSE)

coauthor_name_gender <- coauthor_name_gender %>%
  select(id, gender)%>%
  filter(!is.na(gender))

```

Remove redundant items:
```{r}
#rm(oa_coauthor_info)
gc()
```

For each coauthor, get their cumulative citation counts:
```{r}
coauthor_pubs_cits_cumulative <- oa_coauthor_info_full %>%
  select(id:display_name, works_count:counts_by_year_cited_by_count)%>%
  group_by(id)%>%
  arrange(counts_by_year_year)%>%
  mutate(counts_by_year_works_count_total = cumsum(counts_by_year_works_count),
         counts_by_year_cited_by_count_total = cumsum(counts_by_year_cited_by_count)) %>%
  arrange(id, counts_by_year_year)

# rename some columns
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_year")] <- "year"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_works_count")] <- "count_pubs"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="works_count")] <- "count_pubs_total"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_works_count_total")] <- "count_pubs_total_oa"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_cited_by_count")] <- "cited_by"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="cited_by_count")] <- "cited_by_total"
colnames(coauthor_pubs_cits_cumulative)[which(colnames(coauthor_pubs_cits_cumulative)=="counts_by_year_cited_by_count_total")] <- "cited_by_total_oa"

# citations prior to 2012
latest_citation_coauthor <- coauthor_pubs_cits_cumulative %>%
  group_by(id)%>%
  slice(which.max(year))

latest_citation_coauthor$cited_by_before_2012 <- latest_citation_coauthor$cited_by_total - latest_citation_coauthor$cited_by_total_oa
latest_citation_coauthor$count_pubs_before_2012 <- latest_citation_coauthor$count_pubs_total - latest_citation_coauthor$count_pubs_total_oa

# replace by 0 if negative (OA issue ticket opened)
latest_citation_coauthor$cited_by_before_2012 <- ifelse(latest_citation_coauthor$cited_by_before_2012<0,
                                                        0,
                                                        latest_citation_coauthor$cited_by_before_2012)

latest_citation_coauthor$count_pubs_before_2012 <- ifelse(latest_citation_coauthor$count_pubs_before_2012<0,
                                                        0,
                                                        latest_citation_coauthor$count_pubs_before_2012)

# merge with the rest
coauthor_pubs_cits_cumulative <- merge(coauthor_pubs_cits_cumulative,
                         latest_citation_coauthor[c("id", "cited_by_before_2012", "count_pubs_before_2012")],
                         by = "id",
                         all.x = TRUE)

coauthor_pubs_cits_cumulative$cited_by_total_all <- coauthor_pubs_cits_cumulative$cited_by_before_2012 + coauthor_pubs_cits_cumulative$cited_by_total_oa
coauthor_pubs_cits_cumulative$count_pubs_total_all <- coauthor_pubs_cits_cumulative$count_pubs_before_2012 + coauthor_pubs_cits_cumulative$count_pubs_total_oa

coauthor_year_p_c <- coauthor_pubs_cits_cumulative %>%
  arrange(id, year)%>%
  select(-display_name, -count_pubs_total, -cited_by_total)
```

Get their attention:
```{r}
coauthor_attention <- dbReadTable(con, "altmetric_coauthor_attention")

selected_attention <- coauthor_attention %>%
  filter(., mention_type %in% c("msm", "blog", "tweet"))
```

Cumulatives:
```{r}
coauthor_attention_table <- selected_attention %>%
  pivot_wider(names_from = mention_type, values_from = yearly_count, values_fill = 0)

coauthor_attention_table <- coauthor_attention_table %>%
  group_by(id)%>%
  arrange(year)%>%
  mutate(msm_total = cumsum(msm),
         blog_total = cumsum(blog),
         tweet_total = cumsum(tweet)) %>%
  arrange(id, year)

# rename some columns
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="msm")] <- "coa_attn_news_by"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="msm_total")] <- "coa_attn_news_by_total"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="blog")] <- "coa_attn_blog_by"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="blog_total")] <- "coa_attn_blog_by_total"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="tweet")] <- "coa_attn_twitter_by"
colnames(coauthor_attention_table)[which(colnames(coauthor_attention_table)=="tweet_total")] <- "coa_attn_twitter_by_total"
```

Combine citations and attention. Set mentions to 0 if we have coauthors' ORCID 
and there are no mentions; if we don't have their ORCID, set mentions to NA:
```{r}
coauthor_year_p_c_a <- merge(coauthor_year_p_c,
                             coauthor_attention_table,
                             by = c("id", "year"),
                             all.x = TRUE)

coauthor_orcids <- oa_coauthor_info_full %>%
  distinct(id, .keep_all = TRUE)%>%
  select(id, orcid)


coauthor_year_p_c_a <- merge(coauthor_year_p_c_a,
                             coauthor_orcids,
                             all.x = TRUE,
                             by = "id")

# fill the attention by profile ID
coauthor_year_p_c_a2 <- coauthor_year_p_c_a %>%
  group_by(id)%>%
  fill(coa_attn_news_by_total, coa_attn_blog_by_total, coa_attn_twitter_by_total)

coauthor_year_p_c_a2$coa_attn_news_by <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_news_by) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_news_by)
coauthor_year_p_c_a2$coa_attn_news_by_total <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_news_by_total) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_news_by_total)

coauthor_year_p_c_a2$coa_attn_blog_by <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_blog_by) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_blog_by)
coauthor_year_p_c_a2$coa_attn_blog_by_total <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_blog_by_total) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_blog_by_total)

coauthor_year_p_c_a2$coa_attn_twitter_by <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_twitter_by) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_twitter_by)
coauthor_year_p_c_a2$coa_attn_twitter_by_total <- ifelse((is.na(coauthor_year_p_c_a2$coa_attn_twitter_by_total) & !is.na(coauthor_year_p_c_a2$orcid)),
                                               0,
                                               coauthor_year_p_c_a2$coa_attn_twitter_by_total)
```

Append gender:
```{r}
colnames(coauthor_name_gender)[1] <- "id"

coauthor_year_p_c_a_g <- merge(coauthor_year_p_c_a2,
                               coauthor_name_gender,
                               by = "id",
                               all.x = TRUE)

coauthor_year_p_c_a_g <- coauthor_year_p_c_a_g%>%
  arrange(id, year)

write_csv(coauthor_year_p_c_a_g, "panel_datasets/coauthor_year_panel_26_7.csv")
```

Filter out coauthor observations without year:
```{r}
coauthor_year_p_c_a_g$dupl <- duplicated(coauthor_year_p_c_a_g[c("profile_id", "year")])

coauthor_year_p_c_a_g <- filter(coauthor_year_p_c_a_g, 
                                !is.na(year))%>%
  select(-dupl)
```

Marge coauthors with inferred gender:
```{r}
colnames(coauthor_name_gender) <- c("au_id", "inferred_gender")
oa_coauthor_info_gender <- merge(oa_coauthor_info,
                                 coauthor_name_gender,
                                 all.x = TRUE,
                                 by = "au_id")

oa_coauthor_info_gender$inferred_gender <- ifelse(is.na(oa_coauthor_info_gender$inferred_gender),
                                                  "unknown",
                                                  oa_coauthor_info_gender$inferred_gender)
```

Clean the memory a bit:
```{r}
rm(oa_coauthor_info)
rm(coauthor_name_gender)
rm(coauthor_gender)
rm(all_names)
gc()
```

For each author, match their coauthors from that year:
```{r}
oa_coauthor_matching <- dbReadTable(con, "oa_coauthor_matching")
oa_coauthor_matching <- oa_coauthor_matching[c("id", "au_id", "profile_id", "publication_year")]

profile_ids <- unique(prof_year_p_c_g_a_l_f_i_a_l$profile_id)
```

Now, compile coauthor data for each professor:
```{r warning = F, message = F}
prof_panel_combined <- as.data.frame(matrix(NA, nrow = 0, ncol = 118))

for (i in 1:length(profile_ids)){
  prof_output <- NA
  try(
    prof_output <- coauthor_data_compiler(profile_id = profile_ids[i],
                                          prof_panel = prof_year_p_c_g_a_l_f_i_a_l,
                                          prof_coauthor_matching = oa_coauthor_matching,
                                          prof_coauthor_panel = coauthor_year_p_c_a_g,
                                          prof_coauthor_info_w_gender = oa_coauthor_info_gender))

 
  if (!all(is.na(prof_output))){
    
    prof_panel_combined <- rbind.data.frame(prof_panel_combined,
                                            prof_output)
  }
  print(paste("done with ", i , " out of", length(profile_ids)))
}
```

Write this:
```{r}
write_csv(prof_panel_combined, "panel_datasets/prof_year_pubs_citations_grants_alt_lexis_field_lag_coauthors.csv")
```


# Tidying up

Tidy up the panel dataset:
```{r warning = F, message = F}
# recode the fields
prof_panel_combined <- prof_panel_combined %>% 
  mutate(general_field = case_match(
    overall_field,
    "Arts and Humanities"  ~ "Arts and Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))

prof_panel_combined <- prof_panel_combined %>% 
  mutate(general_field_yearly = case_match(
    yearly_field,
    "Arts and Humanities"  ~ "Arts and Humanities",
    c("Biochemistry, Genetics and Molecular Biology","Agricultural and Biological Sciences",
      "Chemical Engineering", "Chemistry",  "Computer Science", "Decision Sciences",
      "Earth and Planetary Sciences", "Energy", "Engineering", "Environmental Science",
      "Immunology and Microbiology", "Materials Science", "Mathematics", "Neuroscience", 
      "Physics and Astronomy" ) ~ "STEM",
    c("Dentistry", "Health Professions", "Medicine") ~ "Medicine",
    c("Business, Management and Accounting", "Economics, Econometrics and Finance",
      "Psychology", "Social Sciences") ~ "Social sciences"))
```
 
Rename the columns neatly:
```{r}
prof_panel_tidy <- prof_panel_combined %>%
  select(-c(cited_by_before_2012, cited_by_total_oa, cited_by_total_oa_l, 
           coa_cited_by_before_2012, coa_count_pubs_before_2012, coa_cited_by_before_2012_l,
           coa_count_pubs_before_2012, prof_tot_count_pubs_total_oa, prof_tot_count_pubs_total_oa_l, 
           prof_tot_cited_by_total_oa, prof_tot_cited_by_total_oa_l,
           prof_tot_cited_by_before_2012,prof_tot_cited_by_before_2012_l,
           prof_tot_count_pubs_before_2012, prof_tot_count_pubs_before_2012_l ))%>%
  rename(
    grant_veni = veni,
    grant_veni_l = veni_l,
    grant_vidi = vidi,
    grant_vidi_l = vidi_l,    
    grant_vici = vici,
    grant_vici_l = vici_l,
    grant_stevin = stevin,
    grant_stevin_l = stevin_l,
    grant_spinoza = spinoza,
    grant_spinoza_l = spinoza_l,
    grant_starting = starting,
    grant_starting_l = starting_l,
    grant_advanced = advanced,
    grant_advanced_l = advanced_l,
    grant_consolidator = consolidator,
    grant_consolidator_l = consolidator_l,
    grant_synergy = synergy,
    grant_synergy_l = synergy_l,
    coa_online_news = coa_attn_news_by,
    coa_blogs = coa_attn_blog_by,
    coa_twitter = coa_attn_twitter_by,
    coa_online_news_total = coa_attn_news_by_total,
    coa_blogs_total = coa_attn_blog_by_total,
    coa_twitter_total = coa_attn_twitter_by_total,
    coa_online_news_l = coa_attn_news_by_l,
    coa_blogs_l = coa_attn_blog_by_l,
    coa_twitter_l = coa_attn_twitter_by_l,
    coa_online_news_total_l = coa_attn_news_by_total_l,
    coa_blogs_total_l = coa_attn_blog_by_total_l,
    coa_twitter_total_l = coa_attn_twitter_by_total_l,
    coa_tot_count_pubs = prof_tot_count_pubs, 
    coa_tot_cited_by = prof_tot_cited_by,
    coa_tot_count_pubs_total = prof_tot_count_pubs_total_all,
    coa_tot_cited_by_total = prof_tot_cited_by_total_all,
    coa_tot_online_news = prof_tot_coa_attn_news_by,
    coa_tot_blogs = prof_tot_coa_attn_blog_by,
    coa_tot_twitter = prof_tot_coa_attn_twitter_by,
    coa_tot_online_news_total = prof_tot_coa_attn_news_by_total,
    coa_tot_blogs_total = prof_tot_coa_attn_blog_by_total,
    coa_tot_twitter_total = prof_tot_coa_attn_twitter_by_total,
    coa_tot_unique_m = prof_tot_unique_coa_m,
    coa_tot_unique_w = prof_tot_unique_coa_w,
    coa_tot_unique_u = prof_tot_unique_coa_u,
    coa_tot_count_pubs_l = prof_tot_count_pubs_l, 
    coa_tot_cited_by_l = prof_tot_cited_by_l,
    coa_tot_count_pubs_total_l = prof_tot_count_pubs_total_all_l,
    coa_tot_cited_by_total_l = prof_tot_cited_by_total_all_l,
    coa_tot_online_news_l = prof_tot_coa_attn_news_by_l,
    coa_tot_blogs_l = prof_tot_coa_attn_blog_by_l,
    coa_tot_twitter_l = prof_tot_coa_attn_twitter_by_l,
    coa_tot_online_news_total_l = prof_tot_coa_attn_news_by_total_l,
    coa_tot_blogs_total_l = prof_tot_coa_attn_blog_by_total_l,
    coa_tot_twitter_total_l = prof_tot_coa_attn_twitter_by_total_l,
    coa_tot_unique_m_l = prof_tot_unique_coa_m_l,
    coa_tot_unique_w_l = prof_tot_unique_coa_w_l,
    coa_tot_unique_u_l = prof_tot_unique_coa_u_l)
```
 
Select relevant columns and tidy everything up:
```{r}
prof_panel_tidy <- prof_panel_tidy %>%
  # but not 2024
  filter(year <= 2023 & year >= 2012 & !is.na(year))

# coauthors this year
prof_panel_tidy$coa_online_news <- prof_panel_tidy$coa_online_news + prof_panel_tidy$coa_blogs
prof_panel_tidy$coa_online_news_l <- prof_panel_tidy$coa_online_news_l + prof_panel_tidy$coa_blogs_l
prof_panel_tidy$coa_online_news_total <- prof_panel_tidy$coa_online_news_total + prof_panel_tidy$coa_blogs_total
prof_panel_tidy$coa_online_news_total_l <- prof_panel_tidy$coa_online_news_total_l + prof_panel_tidy$coa_blogs_total_l

# all coauthors up until now
prof_panel_tidy$coa_tot_online_news <- prof_panel_tidy$coa_tot_online_news + prof_panel_tidy$coa_tot_blogs
prof_panel_tidy$coa_tot_online_news_l <- prof_panel_tidy$coa_tot_online_news_l + prof_panel_tidy$coa_tot_blogs_l
prof_panel_tidy$coa_tot_online_news_total <- prof_panel_tidy$coa_tot_online_news_total + prof_panel_tidy$coa_tot_blogs_total
prof_panel_tidy$coa_tot_online_news_total_l <- prof_panel_tidy$coa_tot_online_news_total_l + prof_panel_tidy$coa_tot_blogs_total_l

# get groups per years since entry
prof_panel_tidy$entry_batch <- cut(prof_panel_tidy$years_since_first_pub, breaks = seq(0, 50, by=10))
prof_panel_tidy$years_since_entry <- paste("up to", str_remove(str_split_i(as.character(prof_panel_tidy$entry_batch), ",", 2),"]"))
```

Add the non-time variable entry batch given the 2023 cutoff:
```{r}
prof_panel_tidy$years_since_entry_2023 <- 2023 - prof_panel_tidy$first_pub

prof_panel_tidy$entry_batch_2023 <- ifelse(prof_panel_tidy$years_since_entry_2023 <= 10,
                                     "up to 10",
                                     ifelse(prof_panel_tidy$years_since_entry_2023 <= 20,
                                            "up to 20",
                                            ifelse(prof_panel_tidy$years_since_entry_2023 <= 30,
                                                   "up to 30",
                                                   ifelse(prof_panel_tidy$years_since_entry_2023 <= 40,
                                                          "up to 40",
                                                          ifelse(prof_panel_tidy$years_since_entry_2023 <= 50,
                                                                 "up to 50", NA)))))

```


Scopus fields as per https://service.elsevier.com/app/answers/detail/a_id/12007/supporthub/scopus/:

```{r}
prof_panel_tidy <- prof_panel_tidy %>% 
  mutate(scopus_field_overall = case_match(
    overall_field,
    "Arts and Humanities"  ~ "Arts and Humanities",
    c("Chemical Engineering", "Chemistry", "Computer Science", "Earth and Planetary Sciences",
    "Energy", "Engineering", "Environmental Science", "Materials Science", "Mathematics", 
    "Physics and Astronomy") ~ "Physical Sciences",
    c("Medicine", "Nursing", "Veterinary", "Dentistry", "Health Professions") ~ 
      "Health Sciences",
    c("Business, Management and Accounting", "Decision Sciences", 
      "Economics, Econometrics and Finance", "Psychology", 
      "Social Sciences") ~ "Social Sciences",
    c("Agricultural and Biological Sciences", "Biochemistry, Genetics and Molecular Biology",
      "Immunology and Microbiology", "Neuroscience", 
      "Pharmacology, Toxicology and Pharmaceutics") ~ "Life Sciences"))
```

Write this out:
```{r}
write_csv(prof_panel_tidy, "panel_datasets/prof_panel_tidy.csv")
```


Tidy up some columns, drop professors without general fields:
```{r}
prof_panel_filter <- filter(prof_panel_tidy,
                            year < 2024 & !is.na(general_field))

prof_panel_filter$coa_online_all_total <- prof_panel_filter$coa_online_news_total + prof_panel_filter$coa_blogs_total
prof_panel_filter$coa_online_all_total_l <- prof_panel_filter$coa_online_news_total_l + prof_panel_filter$coa_blogs_total_l
prof_panel_filter$coa_online_all <- prof_panel_filter$coa_online_news + prof_panel_filter$coa_blogs
prof_panel_filter$coa_online_all_l <- prof_panel_filter$coa_online_news_l + prof_panel_filter$coa_blogs_l

prof_panel_filter$coa_tot_online_all_total <- prof_panel_filter$coa_tot_online_news_total + prof_panel_filter$coa_tot_blogs_total
prof_panel_filter$coa_tot_online_all_total_l <- prof_panel_filter$coa_tot_online_news_total_l + prof_panel_filter$coa_tot_blogs_total_l
prof_panel_filter$coa_tot_online_all <- prof_panel_filter$coa_tot_online_news + prof_panel_filter$coa_tot_blogs
prof_panel_filter$coa_tot_online_all_l <- prof_panel_filter$coa_tot_online_news + prof_panel_filter$coa_tot_blogs_l

prof_panel_filter$coa_online_all <- prof_panel_filter$coa_online_news + prof_panel_filter$coa_blogs
```

Obtain binary variables for any attention received that year:
```{r}
prof_panel_filter$any_news <- as.factor(ifelse(prof_panel_filter$news_all > 0, 1, 0))
prof_panel_filter$any_news_l <- as.factor(ifelse(prof_panel_filter$news_all_l > 0, 1, 0))

prof_panel_filter$any_online_news <- as.factor(ifelse(prof_panel_filter$alt_online_all > 0, 1, 0))
prof_panel_filter$any_online_news_l <- as.factor(ifelse(prof_panel_filter$alt_online_all_l > 0, 1, 0))

prof_panel_filter$any_online_news_gen <- as.factor(ifelse(prof_panel_filter$alt_online_general_all > 0, 1, 0))
prof_panel_filter$any_online_news_gen_l <- as.factor(ifelse(prof_panel_filter$alt_online_general_all_l > 0, 1, 0))

prof_panel_filter$any_online_news_name <- as.factor(ifelse(prof_panel_filter$alt_online_all > 0, 1, 0))
prof_panel_filter$any_online_news_l <- as.factor(ifelse(prof_panel_filter$alt_online_all_l > 0, 1, 0))

prof_panel_filter$any_twitter <- as.factor(ifelse(prof_panel_filter$alt_twitter > 0, 1, 0))
prof_panel_filter$any_twitter_l <- as.factor(ifelse(prof_panel_filter$alt_twitter_l > 0, 1, 0))

prof_panel_filter$any_grant <- as.factor(ifelse(prof_panel_filter$any_nwo > 0|prof_panel_filter$any_erc, 1, 0))
prof_panel_filter$any_grant_l <- as.factor(ifelse(prof_panel_filter$any_nwo_l > 0|prof_panel_filter$any_erc_l, 1, 0))
```

Now get some more printed news variables:
```{r}
# only online resources
prof_panel_filter$news_online_all <- prof_panel_filter$news_all - prof_panel_filter$news_off_all
prof_panel_filter$news_online_all_l <- prof_panel_filter$news_all_l - prof_panel_filter$news_off_all_l

# only resources without institutional mentions
prof_panel_filter$news_no_inst_all <- prof_panel_filter$news_all - prof_panel_filter$news_inst_all
prof_panel_filter$news_no_inst_all_l <- prof_panel_filter$news_all_l - prof_panel_filter$news_inst_all_l

prof_panel_filter$news_intl_other_sources <- prof_panel_filter$news_local_intl + prof_panel_filter$news_intl_other + 
  prof_panel_filter$news_finance + prof_panel_filter$news_professional + prof_panel_filter$news_science + prof_panel_filter$news_blog +
  prof_panel_filter$news_aggr + prof_panel_filter$news_unknown + prof_panel_filter$news_other 

prof_panel_filter$news_intl_other_sources_l <- prof_panel_filter$news_local_intl_l + prof_panel_filter$news_intl_other_l + 
  prof_panel_filter$news_finance_l + prof_panel_filter$news_professional_l + prof_panel_filter$news_science_l + prof_panel_filter$news_blog_l +
  prof_panel_filter$news_aggr_l + prof_panel_filter$news_unknown_l + prof_panel_filter$news_other_l



# only online resources
prof_panel_filter$news_online_all_total <- prof_panel_filter$news_all_total - prof_panel_filter$news_off_all_total
prof_panel_filter$news_online_all_total_l <- prof_panel_filter$news_all_total_l - prof_panel_filter$news_off_all_total_l

# only resources without institutional mentions
prof_panel_filter$news_no_inst_all_total <- prof_panel_filter$news_all_total - prof_panel_filter$news_inst_all_total
prof_panel_filter$news_no_inst_all_total_l <- prof_panel_filter$news_all_total_l - prof_panel_filter$news_inst_all_total_l

prof_panel_filter$news_intl_other_sources_total <- prof_panel_filter$news_local_intl_total + prof_panel_filter$news_intl_other_total + 
  prof_panel_filter$news_finance_total + prof_panel_filter$news_professional_total + prof_panel_filter$news_science_total +
  prof_panel_filter$news_blog_total + prof_panel_filter$news_aggr_total + prof_panel_filter$news_unknown_total + prof_panel_filter$news_other_total

prof_panel_filter$news_intl_other_sources_total_l <- prof_panel_filter$news_local_intl_total_l + prof_panel_filter$news_intl_other_total_l + 
  prof_panel_filter$news_finance_total_l + prof_panel_filter$news_professional_total_l + prof_panel_filter$news_science_total_l +
  prof_panel_filter$news_blog_total_l + prof_panel_filter$news_aggr_total_l + prof_panel_filter$news_unknown_total_l + prof_panel_filter$news_other_total_l
```

And some more online news variables:
```{r}
prof_panel_filter$alt_general_interest_combi_news <- prof_panel_filter$alt_general_interest_news + prof_panel_filter$alt_general_interest_local_news
prof_panel_filter$alt_general_interest_combi_news_l <- prof_panel_filter$alt_general_interest_news_l + prof_panel_filter$alt_general_interest_local_news_l

prof_panel_filter$alt_science_combi_news <- prof_panel_filter$alt_popsci_news + prof_panel_filter$alt_science_news +  prof_panel_filter$alt_medical_news + prof_panel_filter$alt_sci_news_aggregator

prof_panel_filter$alt_science_combi_news_l <- prof_panel_filter$alt_popsci_news_l + prof_panel_filter$alt_science_news_l +  prof_panel_filter$alt_medical_news_l + prof_panel_filter$alt_sci_news_aggregator_l


prof_panel_filter$alt_other_combi_news <- prof_panel_filter$alt_finance_news + prof_panel_filter$alt_online_blog +  prof_panel_filter$alt_news_aggregator + prof_panel_filter$alt_other_news

prof_panel_filter$alt_other_combi_news_l <- prof_panel_filter$alt_finance_news_l + prof_panel_filter$alt_online_blog_l +  prof_panel_filter$alt_news_aggregator_l + prof_panel_filter$alt_other_news_l


prof_panel_filter$alt_general_interest_combi_news_total <- prof_panel_filter$alt_general_interest_news_total + prof_panel_filter$alt_general_interest_local_news_total
prof_panel_filter$alt_general_interest_combi_news_total_l <- prof_panel_filter$alt_general_interest_news_total_l + prof_panel_filter$alt_general_interest_local_news_total_l

prof_panel_filter$alt_science_combi_news_total <- prof_panel_filter$alt_popsci_news_total + prof_panel_filter$alt_science_news_total +  prof_panel_filter$alt_medical_news_total + prof_panel_filter$alt_sci_news_aggregator_total

prof_panel_filter$alt_science_combi_news_total_l <- prof_panel_filter$alt_popsci_news_total_l + prof_panel_filter$alt_science_news_total_l +  prof_panel_filter$alt_medical_news_total_l + prof_panel_filter$alt_sci_news_aggregator_total_l


prof_panel_filter$alt_other_combi_news_total <- prof_panel_filter$alt_finance_news_total + prof_panel_filter$alt_online_blog_total +  prof_panel_filter$alt_news_aggregator_total + prof_panel_filter$alt_other_news_total

prof_panel_filter$alt_other_combi_news_total_l <- prof_panel_filter$alt_finance_news_total_l + prof_panel_filter$alt_online_blog_total_l +  prof_panel_filter$alt_news_aggregator_total_l + prof_panel_filter$alt_other_news_total_l

# with name

prof_panel_filter$alt_fname_general_interest_combi_news <- prof_panel_filter$alt_fname_general_interest_news + prof_panel_filter$alt_fname_general_interest_local_news
prof_panel_filter$alt_fname_general_interest_combi_news_l <- prof_panel_filter$alt_fname_general_interest_news_l + prof_panel_filter$alt_fname_general_interest_local_news_l

prof_panel_filter$alt_fname_science_combi_news <- prof_panel_filter$alt_fname_popsci_news + prof_panel_filter$alt_fname_science_news +  prof_panel_filter$alt_fname_medical_news + prof_panel_filter$alt_fname_sci_news_aggregator

prof_panel_filter$alt_fname_science_combi_news_l <- prof_panel_filter$alt_fname_popsci_news_l + prof_panel_filter$alt_fname_science_news_l +  prof_panel_filter$alt_fname_medical_news_l + prof_panel_filter$alt_fname_sci_news_aggregator_l


prof_panel_filter$alt_fname_other_combi_news <- prof_panel_filter$alt_fname_finance_news + prof_panel_filter$alt_fname_online_blog +  prof_panel_filter$alt_fname_news_aggregator + prof_panel_filter$alt_fname_other_news

prof_panel_filter$alt_fname_other_combi_news_l <- prof_panel_filter$alt_fname_finance_news_l + prof_panel_filter$alt_fname_online_blog_l +  prof_panel_filter$alt_fname_news_aggregator_l + prof_panel_filter$alt_fname_other_news_l



prof_panel_filter$alt_fname_general_interest_combi_news_total <- prof_panel_filter$alt_fname_general_interest_news_total + prof_panel_filter$alt_fname_general_interest_local_news_total
prof_panel_filter$alt_fname_general_interest_combi_news_total_l <- prof_panel_filter$alt_fname_general_interest_news_total_l + prof_panel_filter$alt_fname_general_interest_local_news_total_l

prof_panel_filter$alt_fname_science_combi_news_total <- prof_panel_filter$alt_fname_popsci_news_total + prof_panel_filter$alt_fname_science_news_total +  prof_panel_filter$alt_fname_medical_news_total + prof_panel_filter$alt_fname_sci_news_aggregator_total

prof_panel_filter$alt_fname_science_combi_news_total_l <- prof_panel_filter$alt_fname_popsci_news_total_l + prof_panel_filter$alt_fname_science_news_total_l +  prof_panel_filter$alt_fname_medical_news_total_l + prof_panel_filter$alt_fname_sci_news_aggregator_total_l


prof_panel_filter$alt_fname_other_combi_news_total <- prof_panel_filter$alt_fname_finance_news_total + prof_panel_filter$alt_fname_online_blog +  prof_panel_filter$alt_fname_news_aggregator_total + prof_panel_filter$alt_fname_other_news_total

prof_panel_filter$alt_fname_other_combi_news_total_l <- prof_panel_filter$alt_fname_finance_news_total_l + prof_panel_filter$alt_fname_online_blog_l +  prof_panel_filter$alt_fname_news_aggregator_total_l + prof_panel_filter$alt_fname_other_news_total_l
```


And some additional variables regarding SJR and authorships:
```{r}
prof_panel_filter$avg_sjr <- round(prof_panel_filter$sum_sjr/prof_panel_filter$count_pubs, 5)
prof_panel_filter$avg_sjr_total <- round(prof_panel_filter$sum_sjr_total/prof_panel_filter$count_pubs_total, 5)

prof_panel_filter$share_first_au <- round((prof_panel_filter$n_pubs_first_au + prof_panel_filter$n_pubs_single_au) / prof_panel_filter$n_pubs_all_au, 5)
prof_panel_filter$share_last_au <- round((prof_panel_filter$n_pubs_last_au + prof_panel_filter$n_pubs_single_au ) / prof_panel_filter$n_pubs_all_au, 5)

prof_panel_filter$share_first_au_total <- round((prof_panel_filter$n_pubs_first_au_total + prof_panel_filter$n_pubs_single_au_total) / prof_panel_filter$count_pubs_total, 5)
prof_panel_filter$share_last_au_total <- round((prof_panel_filter$n_pubs_last_au_total + prof_panel_filter$n_pubs_single_au_total ) / prof_panel_filter$count_pubs_total, 5)

prof_panel_filter$pubs_sjr_total <- prof_panel_filter$count_pubs_total * prof_panel_filter$avg_sjr_total 

prof_panel_filter$coa_online_combi_total <- prof_panel_filter$coa_tot_online_all_total + prof_panel_filter$coa_tot_twitter_total
prof_panel_filter$coa_online_combi <- prof_panel_filter$coa_tot_online_all + prof_panel_filter$coa_tot_twitter

prof_panel_filter$coa_online_combi_totalog <- log(prof_panel_filter$coa_online_combi_total+1)

prof_panel_filter$avg_sjr_l <- round(prof_panel_filter$sum_sjr_l/prof_panel_filter$count_pubs_l, 5)
prof_panel_filter$avg_sjr_total_l <- round(prof_panel_filter$sum_sjr_total_l/prof_panel_filter$count_pubs_total_l, 5)

prof_panel_filter$share_first_au_l <- round((prof_panel_filter$n_pubs_first_au_l + prof_panel_filter$n_pubs_single_au_l) / prof_panel_filter$n_pubs_all_au_l, 5)
prof_panel_filter$share_last_au_l <- round((prof_panel_filter$n_pubs_last_au_l + prof_panel_filter$n_pubs_single_au_l ) / prof_panel_filter$n_pubs_all_au_l, 5)

prof_panel_filter$share_first_au_total_l <- round((prof_panel_filter$n_pubs_first_au_total_l + prof_panel_filter$n_pubs_single_au_total_l) / prof_panel_filter$count_pubs_total_l, 5)
prof_panel_filter$share_last_au_total_l <- round((prof_panel_filter$n_pubs_last_au_total_l + prof_panel_filter$n_pubs_single_au_total_l ) / prof_panel_filter$count_pubs_total_l, 5)

prof_panel_filter$pubs_sjr_total_l <- prof_panel_filter$count_pubs_total_l * prof_panel_filter$avg_sjr_total_l 

prof_panel_filter$coa_online_combi_total_l <- prof_panel_filter$coa_tot_online_all_total_l + prof_panel_filter$coa_tot_twitter_total_l
prof_panel_filter$coa_online_combi_l <- prof_panel_filter$coa_tot_online_all_l + prof_panel_filter$coa_tot_twitter_l

prof_panel_filter$coa_online_combi_total_l_log <- log(prof_panel_filter$coa_online_combi_total_l+1)
```

Set some variables to factor as needed:
```{r}
prof_panel_filter$any_grant_l <- as.factor(prof_panel_filter$any_grant_l)
prof_panel_filter$institution_dutch_total_narcis <- as.factor(prof_panel_filter$institution_dutch_total_narcis)
```

Make new variables for top n% of attention:
```{r}
panel_filter_long <- prof_panel_filter %>%
  pivot_longer(c(alt_online_all, news_all, alt_twitter), names_to = "measure", values_to = "value")

top_1_attn <- panel_filter_long %>%
  filter(!is.na(overall_adj_domain) & !is.na(year) & year > 2011)%>%
  group_by(overall_adj_domain, year, measure)%>%
  filter(quantile(value, 0.99, na.rm = TRUE)<=value)%>%
  dplyr::select(profile_id, overall_adj_domain, year, measure, value)

top_1_attn$measure <- paste0(top_1_attn$measure, "_top_1")

top_1_attn <- top_1_attn %>%
  pivot_wider(names_from = "measure")%>%
  mutate(across(contains('top_1'),  ~ifelse(is.na(.), 0, 1)))

prof_panel_filter <- merge(prof_panel_filter,
                           top_1_attn[c("year", "profile_id", "overall_adj_domain", "alt_online_all_top_1", "alt_twitter_top_1", "news_all_top_1")],
                           by = c("profile_id", "year", "overall_adj_domain"),
                           all.x = TRUE,
                           all.y = FALSE)

top_5_attn <- panel_filter_long %>%
  filter(!is.na(overall_adj_domain) & !is.na(year) & year > 2011)%>%
  group_by(overall_adj_domain, year, measure)%>%
  filter(quantile(value, 0.95, na.rm = TRUE)<=value)%>%
  dplyr::select(profile_id, overall_adj_domain, year, measure, value)

top_5_attn$measure <- paste0(top_5_attn$measure, "_top_5")

top_5_attn <- top_5_attn %>%
  pivot_wider(names_from = "measure")%>%
  mutate(across(contains('top_5'),  ~ifelse(is.na(.), 0, 1)))

prof_panel_filter <- merge(prof_panel_filter,
                           top_5_attn[c("year", "profile_id", "overall_adj_domain", "alt_online_all_top_5", "alt_twitter_top_5", "news_all_top_5")],
                           by = c("profile_id", "year", "overall_adj_domain"),
                           all.x = TRUE,
                           all.y = FALSE)

top_10_attn <- panel_filter_long %>%
  filter(!is.na(overall_adj_domain) & !is.na(year) & year > 2011)%>%
  group_by(overall_adj_domain, year, measure)%>%
  filter(quantile(value, 0.90, na.rm = TRUE)<=value)%>%
  dplyr::select(profile_id, overall_adj_domain, year, measure, value)

top_10_attn$measure <- paste0(top_10_attn$measure, "_top_10")


top_10_attn <- top_10_attn %>%
  pivot_wider(names_from = "measure")%>%
  mutate(across(contains('top_10'),  ~ifelse(is.na(.), 0, 1)))

prof_panel_filter <- merge(prof_panel_filter,
                           top_10_attn[c("year", "profile_id", "overall_adj_domain", "alt_online_all_top_10", "alt_twitter_top_10", "news_all_top_10")],
                           by = c("profile_id", "year", "overall_adj_domain"),
                           all.x = TRUE,
                           all.y = FALSE)

top_20_attn <- panel_filter_long %>%
  filter(!is.na(overall_adj_domain) & !is.na(year) & year > 2011)%>%
  group_by(overall_adj_domain, year, measure)%>%
  filter(quantile(value, 0.80, na.rm = TRUE)<=value)%>%
  dplyr::select(profile_id, overall_adj_domain, year, measure, value)

top_20_attn$measure <- paste0(top_20_attn$measure, "_top_20")


top_20_attn <- top_20_attn %>%
  pivot_wider(names_from = "measure")%>%
  mutate(across(contains('top_20'),  ~ifelse(is.na(.), 0, 1)))

prof_panel_filter <- merge(prof_panel_filter,
                           top_20_attn[c("year", "profile_id", "overall_adj_domain", "alt_online_all_top_20", "alt_twitter_top_20", "news_all_top_20")],
                           by = c("profile_id", "year", "overall_adj_domain"),
                           all.x = TRUE,
                           all.y = FALSE)

prof_panel_filter <- filter(prof_panel_filter, !is.na(overall_adj_domain))

# if NA, needs to be 0
prof_panel_filter <- prof_panel_filter %>%
  mutate(across(contains('top_1'),  ~ifelse(is.na(.), 0, .)))%>%
  mutate(across(contains('top_5'),  ~ifelse(is.na(.), 0, .)))%>%
  mutate(across(contains('top_10'),  ~ifelse(is.na(.), 0, .)))%>%
  mutate(across(contains('top_20'),  ~ifelse(is.na(.), 0, .)))
```


Save this:
```{r}
write_csv(prof_panel_filter, "panel_datasets/prof_panel_final_all_vars.csv")
```

Anonymize the dataset for sharing by removing NARCIS IDs. Add new identifiers and
drop any redundant columns.
```{r}
# # generate new ID mapping
# unique_narcis <- unique(prof_panel_filter$profile_id)
# new_ids <- paste("prof", c(1:length(unique_narcis)), sep= "_")
# 
# new_id_mapping <- data.frame(profile_id = unique_narcis,
#                                 prof_id = new_ids)
# 
# dbWriteTable(con, "anonymous_id_mapping", new_id_mapping, row.names=FALSE, append=TRUE)

new_id_mapping <- dbReadTable(con, "anonymous_id_mapping")

# combine the panel with the new ID mapping
prof_panel_filter_anonymous <- merge(prof_panel_filter,
                                     new_id_mapping,
                                     all.x = TRUE)

```


```{r}
# tidy up the variable order again
prof_panel_filter_anonymous <- prof_panel_filter_anonymous %>%
  dplyr::select(prof_id, year, overall_adj_domain , first_pub, years_since_first_pub, entry_batch_2023, institution_dutch_total_narcis, 
                institution_dutch_yearly_strict, institution_dutch_yearly_strict_l,
                inferred_gender, news_all, news_all_l, alt_online_all_l, alt_twitter_l,
                alt_online_all, alt_twitter, 
                count_pubs, count_pubs_l, count_pubs_total, count_pubs_total_l, 
                share_first_au, share_first_au_l, share_first_au_total, share_first_au_total_l,
                share_last_au, share_last_au_l, share_last_au_total, share_last_au_total_l,
                cited_by, cited_by_l, cited_by_total_all, cited_by_total_all_l,
                avg_sjr, avg_sjr_l, avg_sjr_total, avg_sjr_total_l,
                coa_tot_cited_by,  coa_tot_cited_by_l, coa_online_combi, coa_online_combi_l, 
                coa_tot_cited_by_total, coa_tot_cited_by_total_l,
                coa_online_combi_total, coa_online_combi_total_l,
                news_all_total, news_all_total_l,  alt_online_all_total, alt_online_all_total_l,
                alt_twitter_total, alt_twitter_total_l,
                any_grant, any_grant_l, 
                any_news, news_all_top_1, news_all_top_5, news_all_top_10, news_all_top_20, 
                any_online_news, alt_online_all_top_1, alt_online_all_top_5, alt_online_all_top_10, alt_online_all_top_20, 
                any_twitter, alt_twitter_top_1, alt_twitter_top_5, alt_twitter_top_10, alt_twitter_top_20, news_all,
                news_strict_all, news_strict_all_l, 
                news_off_all, news_off_all_l,  news_off_all_total, news_off_all_total_l, 
                news_online_all, news_online_all_l, news_online_all_total, news_online_all_total_l,  
                news_ded_all, news_ded_all_l, news_ded_all_total, news_ded_all_total_l, 
                news_national, news_national_l, news_national_total, news_national_total_l, 
                news_regional, news_regional_l,news_regional_total, news_regional_total_l, 
                news_intl,  news_intl_l,news_intl_total,  news_intl_total_l, 
                news_intl_other_sources, news_intl_other_sources_l, news_intl_other_sources_total, news_intl_other_sources_total_l, 
                alt_online_all, alt_online_all_l, alt_online_all_total, alt_online_all_total_l, 
                alt_online_single_all, alt_online_single_all_l,
                alt_online_name_all, alt_online_name_all_l, alt_online_fname_all, alt_online_fname_all_l, 
                alt_online_fname_all_total, alt_online_fname_all_total_l,
                alt_online_dutch_all, alt_online_dutch_all_l, 
                alt_general_interest_combi_news, alt_general_interest_combi_news_l, 
                alt_general_interest_combi_news_total, alt_general_interest_combi_news_total_l,
                alt_science_combi_news, alt_science_combi_news_l, alt_science_combi_news_total, alt_science_combi_news_total_l, 
                alt_other_combi_news, alt_other_combi_news_l, alt_other_combi_news_total, alt_other_combi_news_total_l,
                 alt_fname_general_interest_combi_news, alt_fname_general_interest_combi_news_l, 
                alt_fname_general_interest_combi_news_total, alt_fname_general_interest_combi_news_total_l,
                alt_fname_science_combi_news, alt_fname_science_combi_news_l, 
                alt_fname_science_combi_news_total, alt_fname_science_combi_news_total_l, 
                alt_fname_other_combi_news, alt_fname_other_combi_news_l, alt_fname_other_combi_news_total, alt_fname_other_combi_news_total_l)


colnames(prof_panel_filter_anonymous)[1] <- "profile_id"

# write it out
write_csv(prof_panel_filter_anonymous, "panel_datasets/prof_panel_anonymised.csv")
```

