---
title: "SJR_comparison"
author: "Ana Macanovic"
date: "2025-04-01"
output: html_document
---

# SJR and CiteScore Rating Comparison

This script compares journal prestige scores from Scimago and Scopus rankings.
We do not distribute the rankings themselves; readers should consult the original
data sources to replicate this analysis.


Load the packages:
```{r message=  F, warning = F, eval = T}
source("helper_functions.R")

packages_to_load <- c("readr", "dplyr", "tidyr")

fpackage_check(packages_to_load)


# For full reproducibility, load the packages with groundhog using the code below instead
# of the fpackage_check function

# library(groundhog)
# groundhog.library(packages_to_load, date = "2025-4-1")
```


```{r}
opts_chunk$set(echo = TRUE)
opts_chunk$set(eval = FALSE)
opts_chunk$set(warning = FALSE)
opts_chunk$set(message = FALSE)
```


Load Scimago and Scopus files for overlapping years we have access to. These are years
between 2011 and 2019:
```{r}
scimago_files <- list.files("resources/scimago_journal_rankings",
                            full.names = TRUE)

scimago_files <- scimago_files[13:21]

scopus_files <- list.files("resources/scopus_source_rankings",
                            full.names = TRUE)

scopus_files <- scopus_files[1:9]
```

For each year, load in both files, merge the scores, and check the correlation:
```{r warning = F, message = F}
years <- c(2011:2019)
correlations <- c()

for (i in 1:length(years)){
  
  scimago <- read_delim(scimago_files[i], delim = ";")
  
  scimago_scores <- scimago %>% 
    dplyr::select(Sourceid, Title, Issn, SJR, `H index`, `SJR Best Quartile`)%>%
    filter(Issn != "-")%>%
    mutate(Issn = strsplit(Issn, ",")) %>%
          unnest(Issn) %>%
          group_by(Title) %>%
          mutate(row = row_number()) %>%
          spread(row, Issn)%>%
    pivot_longer(cols = -c(Sourceid, Title, SJR, `H index`,  `SJR Best Quartile`), values_to = "issn", names_to = "issn_order")%>%
    filter(!is.na(issn))%>%
    dplyr::select(-issn_order)
  
  # remove redundant whitespace
  scimago_scores$issn <- str_remove_all(scimago_scores$issn, " ")
  # replace commas in SJR with dots
  scimago_scores$SJR <- str_replace_all(scimago_scores$SJR, ",", ".")
  
  scopus_scores <- read_csv(scopus_files[i])
  
  scopus_scores <- scopus_scores %>%
    distinct(`Scopus Source ID`, `Print ISSN`, `E-ISSN`, .keep_all = TRUE)%>%
    dplyr::select(CiteScore, SJR, SNIP, `Percent Cited`, Quartile, `Top 10% (CiteScore Percentile)`, `Print ISSN`, `E-ISSN`, Title, `Scopus Source ID`)
  
  scopus_scores <- scopus_scores %>%
    pivot_longer(cols = c(`Print ISSN`, `E-ISSN`), values_to = "issn")%>%
    filter(!is.na(issn))%>%
    dplyr::select(-name)
  
  # pad issn numbers
  scopus_scores$issn <-  str_pad(scopus_scores$issn, 8, pad = "0")
  
  merge_scores <- merge(scimago_scores,
                        scopus_scores,
                        by = "issn")
  
  correlations <- c(correlations,
                    cor(as.numeric(merge_scores$SJR.x), merge_scores$CiteScore, use = "complete.obs"))
  
  print(i)
  
}

```

Prepare the output and write it out:
```{r}
scimago_scopus_correlation <- data.frame(year = years,
                                            correlation = correlations)

scimago_scopus_correlation$correlation <- round(scimago_scopus_correlation$correlation, 2)

write_csv(scimago_scopus_correlation, "Results/supplement_tables/SI_additional_scimago_scopus_correlation.csv")
```

